### 2015-12-16 piezo.tex
Initial commit; stub for paper

%% ****** Start of file rsitemplate.tex ****** %
%%
%%   This file has been edited from the original source file.
%%	 The original file is part of the revtex4-1 package indicated below.
%%   Version 4.1 of 9 October 2009.
%%
%
% This is a template for producing documents for use with 
% the REVTEX 4.1 document class and the RSI substyle.
% 
% Copy this file to another name and then work on that file.
% That way, you always have this original template file to use.

\documentclass[aip,rsi,reprint,graphicx,draft]{revtex4-1} % for checking your page length
%\\documentclass[aip,rsi,preprint,graphicx]{revtex4-1} % for review purposes

\usepackage{siunitx}

\begin{document}

% Use the \preprint command to place your local institutional report number 
% on the title page in preprint mode.
% Multiple \preprint commands are allowed.
%\preprint{}

\title{An ultra-low noise, high-voltage piezo driver}

% repeat the \author .. \affiliation  etc. as needed
% \email, \thanks, \homepage, \altaffiliation all apply to the current author.
% Explanatory text should go in the []'s, 
% actual e-mail address or url should go in the {}'s for \email and \homepage.
% Please use the appropriate macro for the type of information

% \affiliation command applies to all authors since the last \affiliation command. 
% The \affiliation command should follow the other information.

\author{N.C. Pisenti}
\email[]{npisenti@umd.edu}
\author{B.J. Reschovsky}
\author{D.S. Barker}
\author{A. Restelli}
\author{G.K. Campbell}
%\homepage[]{Your web page}
%\thanks{}
%\altaffiliation{}
\affiliation{Joint Quantum Institute, University of Maryland and NIST}

% Collaboration name, if desired (requires use of superscriptaddress option in \documentclass). 
% \noaffiliation is required (may also be used with the \author command).
%\collaboration{}
%\noaffiliation

\date{\today}

\begin{abstract}
We present an ultra-low noise, high voltage driver suited for use with piezoelectric actuators and other low-current applications.
The architecture leverages a commercially available, small-form-factor integrated circuit (IC) for generating high voltage outputs.
The IC uses a flyback configuration switching regulator to generate up to 250V in our design (but up to 1kV or more with small modification), and a high slew-rate op-amp capacitively coupled to the output compensates for the switching noise.
A low-voltage (\SI{\pm 10}{\volt}), high bandwidth modulation input is capable of summing small voltage corrections onto the output, making the driver well suited for use in closed-loop feedback applications.
\end{abstract}

\pacs{}% insert suggested PACS numbers in braces on next line

\maketitle %\maketitle must follow title, authors, abstract and \pacs

% Body of paper goes here. Use proper sectioning commands. 
% References should be done using the \cite and \label commands
\section{Introduction}
\label{Sec:Introduction}
Introduction, why we care, overview of circuit design elements/features.

\section{Circuit Design}
\label{Sec:Circuit}
Discussion of individual circuit components

\section{Results}
\label{Sec:Results}
Noise analysis, bandwidth, (DC) stability, etc.

\section{Conclusion}
\label{Sec:Conclusion}

% If in two-column mode, this environment will change to single-column format so that long equations can be displayed. 
% Use only when necessary.
%\begin{widetext}
%$$\mbox{put long equation here}$$
%\end{widetext}

% Figures should be put into the text as floats. 
% Use the graphics or graphicx packages (distributed with LaTeX2e). EPSFig is no longer fully supported.
% See the LaTeX Graphics Companion by Michel Goosens, Sebastian Rahtz, and Frank Mittelbach for examples. 
%
% Here is an example of the general form of a figure:
% Fill in the caption in the braces of the \caption{} command. 
% Put the label that you will use with \ref{} command in the braces of the \label{} command.
%
% \begin{figure}
% \includegraphics{}% % Important NOTE: Please make certain your figures do not include local directory paths. ex. "c:\file\sub\fig1.eps"
% \caption{\label{}}%
% \end{figure}

% Tables may be be put in the text as floats.
% Here is an example of the general form of a table:
% Fill in the caption in the braces of the \caption{} command. Put the label
% that you will use with \ref{} command in the braces of the \label{} command.
% Insert the column specifiers (l, r, c, d, etc.) in the empty braces of the
% \begin{tabular}{} command.
%
% \begin{table}
% \caption{\label{} }
% \begin{tabular}{}
% \end{tabular}
% \end{table}

% If you have acknowledgments, this puts in the proper section head.
%\begin{acknowledgments}
% Put your acknowledgments here.
%\end{acknowledgments}

% Create the reference section using BibTeX:
%\bibliography{your-bib-file}
% Run this once to generate your BBL file. Then copy the contents of your BBL file into your main latex file, commenting out "\bibliography"

\end{document}
%
% ****** End of file aiptemplate.tex ******

### 2015-12-19 piezo.tex
Sketch of intro done
* HV stabilization schematic figure

@@
 % That way, you always have this original template file to use.
-
-\documentclass[aip,rsi,reprint,graphicx,draft]{revtex4-1} % for checking your page length
+\documentclass[aip,rsi,reprint]{revtex4-1} % for checking your page length
+%\documentclass[aip,rsi,reprint,graphicx,draft]{revtex4-1} % for checking your page length
 %\\documentclass[aip,rsi,preprint,graphicx]{revtex4-1} % for review purposes
@@
 \usepackage{siunitx}
+\usepackage{amsmath}
+
+\usepackage{graphicx}
+%\usepackage{caption}
+%\usepackage{subcaption}
+
+%% Work with illustrator *.ai files...
+\DeclareGraphicsRule{.ai}{pdf}{.ai}{}
 
@@
 %\altaffiliation{}
-\affiliation{Joint Quantum Institute, University of Maryland and NIST}
+\affiliation{Joint Quantum Institute, University of Maryland and National Institute of Standards and Technology}
 
@@
 \label{Sec:Introduction}
-Introduction, why we care, overview of circuit design elements/features.
+
+Many instrumentation applications in the modern laboratory require agile, low-noise voltage sources that can supply hundreds of volts or more.
+Such high-voltage amplifiers are useful for micro-positioning applications, driving piezo-actuated mirrors (e.g., in a scanning Fabry-Per{\`o}t cavity) or diffraction gratings (such as in extended-cavity diode lasers).
+Precision high voltage sources can also be used to bias low-noise, high-bandwidth photodiodes [details?], Other applications...? biophysics? medical devices?
+Often, these applications are operated in a closed feedback loop, where small voltage changes on top of a large DC voltage are necessary to correct for some disturbance to the system.
+
+Traditionally, laboratory electronics capable of supplying high voltages fall under one of two architectural umbrellas: switching converters, and ``linear'' amplifiers.
+DC-DC converters are efficient and can work at very high voltages, but suffer from switching noise and limited control bandwidths.
+Linear-type devices are typically constructed from a high-voltage operational amplifier (op-amp), powered either from a high voltage linear regulator or more typically from a secondary switching converter.
+While the op-amp provides \SI{100}{\decibel} or more of power-supply noise rejection, a high-voltage op-amp require substantially more power than an equivalent switching circuit.
+In either case, the output voltage  $V_{\text{out}}$ is typically given by
+\begin{align}
+  V_{\text{out}} &= G_p(V_{\text{DC}} + V_{\text{mod}})\, \text{,}
+\end{align}
+where $G_p$ is the piezo amplifier gain (typically {$G_p\approx \num{10} - \num{20}$} or more), $V_{\text{DC}}$ is a DC setpoint, and $V_{\text{mod}}$ is a modulation input used for closed-loop control.
+
+It is often the case, however, that in closed-loop feedback applications we do not need and often do not want the modulation control to have a high gain.
+Because the closed loop gain cannot be increased without limit, $G_p V_{\text{mod}} \gg 1$ means the servo gain $G$ must be proportionally smaller to keep the lock stable.
+Because noise added by the servo is suppressed by $1/|G|$ in the large gain limit, if $G$ is limited to achieve a stable lock it is no longer as effective at servoing its own noise.
+
+To avoid this problem, we desire a high voltage amplifier which separates the ``setpoint'' gain $G_p$ from the modulation gain, $G_m$. That is,
+\begin{align}
+  V_{\text{out}} &= G_p V_{\text{DC}} + G_m V_{\text{mod}}\, \text{,}
+  \label{Eq:PiezoTransfer}
+\end{align}
+where now we can make $G_m \approx 1$.
 
@@
 \label{Sec:Circuit}
+
+\begin{figure}[ht]
+\includegraphics[width=\linewidth]{fig/PiezoCircuit.ai}
+%\captionsetup{justification=justified}
+\caption{Schematic of the high voltage stabilization.
+The voltage HV is generated using a Texas Instruments DRV2700 high voltage driver in flyback configuration (see Fig.~\ref{Fig:DRV2700}).
+A fast, very high slew-rate op-amp senses the output voltage across $R_1$ and $R_2$, and servos it by modulating the node at ``HV floating gnd''.
+The $V_{\text{DC}}$ gain is set by $\left(1+R_1/R_2\right)$, while the modulation gain is set by $-R_{\text{mod}}/R_{\text{fb}}$.
+The capacitor linking the floating ground node to the output allows the op-amp to remove residual switching noise and stabilize the DC output according to the transfer function given in Eq.~(\ref{Eq:PiezoTransfer}).
+\label{Fig:PiezoCircuit}}
+\end{figure}
+
 Discussion of individual circuit components

### 2015-12-23 piezo.tex
Added mostly completed schematic; beginning of description of circuit

@@
 \usepackage{amsmath}
+\usepackage{amsfonts}
 
@@
 
-\begin{figure}[ht]
-\includegraphics[width=\linewidth]{fig/PiezoCircuit.ai}
-%\captionsetup{justification=justified}
+The core elements of this circuit revolve around the newly-available Texas Instruments DRV2700 piezo driver.
+\footnote{The identification of commercial products is for information only and does not imply recommendation or endorsement by the National Institute of Standards and Technology.}
+This single-chip integrated circuit can be operated as a boost converter driving an on-chip differential amplifier up to \SI{100}{\volt}, or as a flyback regulator up to \SI{1}{\kilo\volt}. 
+In flyback configuration, the DRV2700 drives a step-up transformer, providing the galvanically isolated voltage $\mathbf{HV}$ at its output; see Fig.~\ref{Fig:DRV2700}.
+
+\begin{figure*}[t]
+\includegraphics[width=\textwidth]{fig/DRV2700.ai}
 \caption{Schematic of the high voltage stabilization.
@@
 \label{Fig:PiezoCircuit}}
-\end{figure}
+\end{figure*}
 
-Discussion of individual circuit components
+In isolation, the DRV2700 is not suited for low-noise laboratory instrumentation. 
+The output ripple, even after heavy filtering, can be as high as a few volts, and standard filter techniques to reduce this noise simultaneously reduce the modulation bandwidth.
+Even if this were not the case, it remains unlikely that the RMS noise could be brought below $\SI{1}{\milli\volt}$, which is the regime we would like to operate in for certain low-noise applications in the laboratory.
+With this in mind, we designed a circuit that leverages the integrated flyback regulator of the DRV2700 but uses a secondary feedback mechanism to both eliminate switching noise and provide a low-gain, DC-coupled feedback path for closed loop applications.
 

### 2015-12-26 piezo.tex
Circuit design intro; sketch of design subsections

--- 2015-12-19 piezo.tex
@@
 
-\begin{figure}[ht]
-\includegraphics[width=\linewidth]{fig/PiezoCircuit.ai}
-%\captionsetup{justification=justified}
+The design is based on the newly-available Texas Instruments DRV2700 piezo driver.
+\footnote{The identification of commercial products is for information only and does not imply recommendation or endorsement by the National Institute of Standards and Technology.}
+This single-chip integrated circuit (IC) can be operated as a boost converter to drive an on-chip differential amplifier up to \SI{100}{\volt}, or as a flyback converter up to \SI{1}{\kilo\volt}.
+In flyback configuration, the internal-boost switch of the DRV2700 drives a step-up transformer.
+When the switch is closed, current flows through the primary coil of the transformer and induces a corresponding voltage across the secondary coil, which charges a capacitor at the output ($\text{C}_{\text{HV}}$ in Fig.~\ref{Fig:PiezoCircuit}).
+When the switch opens, a negative voltage appears across the secondary coil of the transformer, but a diode prevents the capacitor from discharging.
+One key benefit of this topology is the galvanically isolated output.
+By sensing the output voltage across a resistive divider, we servo the floating ground from the flyback converter to remove switching noise and stabilize the high voltage output; see Fig.~\ref{Fig:PiezoCircuit}.
+
+\begin{figure*}[t]
+\includegraphics[width=\textwidth]{fig/DRV2700.ai}
 \caption{Schematic of the high voltage stabilization.
@@
 \label{Fig:PiezoCircuit}}
-\end{figure}
+\end{figure*}
 
-Discussion of individual circuit components
+In isolation, the DRV2700 is not suited for low-noise laboratory instrumentation. 
+The output ripple, even after heavy filtering, can be as high as a few volts, and standard filtering techniques to reduce this noise simultaneously reduces the modulation control bandwidth.
+Even if this were not the case, it remains unlikely that the RMS noise could be brought below $\SI{1}{\milli\volt}$, which is the operating regime we require for certain low-noise applications in the laboratory.
+Despite this drawback, the flyback converter requires very little current to operate and leverages a compact IC to generate very high voltages, making it versatile and easy to deploy in the lab.
+
+The motivation behind our hybrid architecture is twofold.
+First, to make a switching converter useful for low-noise laboratory instrumentation, we need a way to remove the output ripple and residual switching noise.
+Second, we want to take advantage of low-noise op-amps that only work up to tens of volts to provide a unity gain (DC-coupled) feedback path to the high voltage output.
+The architecture shown in Fig.~\ref{Fig:PiezoCircuit} does just this; a low-noise, high-slew rate op-amp ($\mathbf{U2}$) adjusts the floating ground node of the transformer output to cancel switching noise and sum in an offset given by $V_{\text{mod}}$, while the flyback regulator works close to DC to impose the high voltage across the HV - floating ground output.
+We now explain the operation of each sub-block, and draw attention to important design details.
+
+\subsection{DRV2700 flyback regulator}
+\label{Sec:DRV2700}
+
+\subsection{Low-noise stabilization}
+\label{Sec:LowNoiseStabilization}
+%At high frequencies, this modulation appears directly at the HV node through the capacitors.
+%At quasi-DC frequencies, the flyback regulator adjusts the HV node to keep
+
+\subsection{Digital control and auxiliary design features}
+\label{Sec:DigControlAuxDesign}
 

### 2015-12-26 piezo.tex
Initial sketch of DRV2700 description

@@
 
+We based the flyback regulator design off the suggested schematic in the DRV2700 datasheet and evaluation module application note.
+At a basic level, this requires a transformer (ATB3225; 1:10 step-up winding, \SI{7}{\micro\henry} inductance, rated for \SI{0.6}{\ampere}) connected to an output diode and capacitor, and a voltage supplied to the feedback (FB) node.
+Internally, the DRV2700 boost controller tries to drive the FB node to \SI{1.3}{\volt}.
+The op-amp U1 senses the voltage at node \textit{HV} and \textit{GND}${}_\text{HV}$, and adjusts its output such that
+\begin{align}
+\label{Eq:U1Output}
+\text{HV} &= G\cdot V_{\text{dc}} + \text{GND}_{\text{HV}}\,,
+\end{align}
+where the gain $G$ is set by the resistor ratio $R_3/R_4$.
+The capacitors $C_3$ and $C_4$ are chosen such that $C_3 = \SI{22}{\pico\farad}$ and 
+\begin{align}
+\frac{C_4}{C_3} &= \frac{R_3}{R_4~||~R_5}
+\end{align}
+as suggested by the datasheet.
+This pseudo-differential configuration ensures that, in the equilibrium given by Eq.~(\ref{Eq:U1Output}), the output of U1 is driven to \SI{0}{\volt}; the resistive divider $R_9$ and $R_{10}$ is then chosen such that $R_9/(R_9~||~R_{10}) = \SI{1.3}{\volt}/\SI{5}{\volt} \approx \num{0.26}$.
+
+Notes here about expected, measured bandwidth??
+
+The DRV2700 IC, combined with the the feedback provided by U1, regulates the voltage $(\text{HV}-\text{GND}_{\text{HV}}) = G\cdot V_{\text{dc}}$.
+Careful attention was paid to the layout ...
+
 \subsection{Low-noise stabilization}
@@
 %At quasi-DC frequencies, the flyback regulator adjusts the HV node to keep
+
+The choice of component for resistors $R_1$ and $R_2$ is crucial for the low-noise performance of the system. (cite LIGO paper)
 

### 2016-01-01 piezo.tex
reworked the intro, re-arranged the ordering

@@
 
-Many instrumentation applications in the modern laboratory require agile, low-noise voltage sources that can supply hundreds of volts or more.
-Such high-voltage amplifiers are useful for micro-positioning applications, driving piezo-actuated mirrors (e.g., in a scanning Fabry-Per{\`o}t cavity) or diffraction gratings (such as in extended-cavity diode lasers).
-Precision high voltage sources can also be used to bias low-noise, high-bandwidth photodiodes [details?], Other applications...? biophysics? medical devices?
-Often, these applications are operated in a closed feedback loop, where small voltage changes on top of a large DC voltage are necessary to correct for some disturbance to the system.
+Many instrumentation applications in the modern laboratory require agile, low-noise voltage sources capable of supplying hundreds of volts or more.
+For example, piezo-actuated mirrors and diffraction gratings play an important role in many atomic physics experiments (used, e.g., in scanning Fabry-Per{\`o}t cavities and extended-cavity diode lasers).
+Avalanche photodiodes require a low-noise reverse bias of a few hundred volts or more (cite paper Alessandro/Prasoon are using?).
+Other applications...? biophysics? medical devices?
+
+Often, these applications are operated in a closed feedback loop, where small voltage changes on top of a large DC voltage are necessary to stabilize the output of a particular system.
+For example, extended-cavity diode lasers adjust their lasing frequency by changing the angle of a diffraction grating that supplies optical feedback to the diode.
+To stabilize this frequency, a servo controller measures deviations from the desired value and adjusts the voltage controlling the grating angle to correct for any difference.
+Because the servo electronics operate at low voltage, a secondary high-voltage (HV) amplifier is required to drive the piezoelectric actuator.
+This HV gain stage typically accepts an external ``modulation input'', $V_{\text{mod}}$, and produces an amplified voltage $V_{\text{out}}$ according to
+\begin{align}
+V_{\text{out}} = G_p V_{\text{mod}} + V_0
+\end{align}
+where $G_p$ is the amplifier gain and $V_0$ is an optional DC offset.
+Typically, {$G_p\approx \num{10} - \num{20}$} or more such that reasonable voltages $V_{\text{mod}}$ can span the entire output range $V_{\text{out}}$.
+
+It is often the case, however, that in closed-loop feedback applications we do not need and often do not want the modulation control to have a high gain.
+Because the closed loop gain $G \equiv G_s G_p$ cannot be increased without limit, $G_p \gg 1$ means the servo gain $G_s$ must be proportionally smaller to keep the lock stable.
+In locked configuration, any noise introduced by the servo is suppressed by $1/|G_s|$ in the large gain limit.
+If $G_s$ is limited to achieve a stable lock, it is no longer effective at servoing its own noise.
+
+To avoid this problem, we desire a high voltage amplifier which separates the ``setpoint'' gain, $G_{\text{dc}}$, from the modulation gain, $G_{\text{mod}}$. That is,
+\begin{align}
+  V_{\text{out}} &= G_{\text{dc}} V_{\text{dc}} + G_{\text{mod}} V_{\text{mod}}\, \text{,}
+  \label{Eq:PiezoTransfer}
+\end{align}
+where now we can make $G_{\text{mod}} \approx 1$.
 
@@
 \end{align}
-where $G_p$ is the piezo amplifier gain (typically {$G_p\approx \num{10} - \num{20}$} or more), $V_{\text{DC}}$ is a DC setpoint, and $V_{\text{mod}}$ is a modulation input used for closed-loop control.
-
-It is often the case, however, that in closed-loop feedback applications we do not need and often do not want the modulation control to have a high gain.
-Because the closed loop gain cannot be increased without limit, $G_p V_{\text{mod}} \gg 1$ means the servo gain $G$ must be proportionally smaller to keep the lock stable.
-Because noise added by the servo is suppressed by $1/|G|$ in the large gain limit, if $G$ is limited to achieve a stable lock it is no longer as effective at servoing its own noise.
-
-To avoid this problem, we desire a high voltage amplifier which separates the ``setpoint'' gain $G_p$ from the modulation gain, $G_m$. That is,
-\begin{align}
-  V_{\text{out}} &= G_p V_{\text{DC}} + G_m V_{\text{mod}}\, \text{,}
-  \label{Eq:PiezoTransfer}
-\end{align}
-where now we can make $G_m \approx 1$.
+where $G_p$ is the piezo amplifier gain, $V_{\text{DC}}$ is a DC setpoint, and $V_{\text{mod}}$ is a modulation input used for closed-loop control.
 
@@
 One key benefit of this topology is the galvanically isolated output.
-By sensing the output voltage across a resistive divider, we servo the floating ground from the flyback converter to remove switching noise and stabilize the high voltage output; see Fig.~\ref{Fig:PiezoCircuit}.
+By sensing the output voltage across a resistive divider, we feed back to the floating ground from the flyback converter to remove switching noise and stabilize the high voltage output; see Fig.~\ref{Fig:PiezoCircuit}.
 
@@
 \label{Sec:LowNoiseStabilization}
+
+The low-noise stabilization circuitry was added to remove output ripple and residual switching noise, however it serves a dual purpose as a low-gain, high-bandwidth modulation path to the high-voltage output.
+It uses a very high slew-rate (\SI{4100}{\volt\per\micro\second}) op-amp, the LM7171, connected to the filtered ground node of the flyback converter.
+At high frequencies, the output of this op-amp appears directly at the HV node through the capacitor $C_{\text{out}}$.
+Below the corner set by $C_{\text{out}}$, the output of U2 adjusts the floating ground reference of the flyback converter.
+
+After the passive filter ladder connecting the DRV2700 flyback converter the output,
 %At high frequencies, this modulation appears directly at the HV node through the capacitors.
@@
 \label{Sec:DigControlAuxDesign}
+
+\subsection{Noise Analysis}
+\label{Sec:NoiseAnalysis}
 

### 2016-01-02 piezo.tex
Minor sentence tweaks; updated schematic with component names.

@@
 We based the flyback regulator design off the suggested schematic in the DRV2700 datasheet and evaluation module application note.
-At a basic level, this requires a transformer (ATB3225; 1:10 step-up winding, \SI{7}{\micro\henry} inductance, rated for \SI{0.6}{\ampere}) connected to an output diode and capacitor, and a voltage supplied to the feedback (FB) node.
+At a basic level, the DRV2700 flyback circuit requires a transformer (ATB3225; 1:10 step-up winding, \SI{7}{\micro\henry} inductance, rated for \SI{0.6}{\ampere}) connected to an output diode and capacitor, and a ``sense'' voltage supplied to the feedback (FB) node of the IC.
 Internally, the DRV2700 boost controller tries to drive the FB node to \SI{1.3}{\volt}.
@@
 \end{align}
-where the gain $G$ is set by the resistor ratio $R_3/R_4$.
+where the gain $G$ is set by the resistor ratio $R_3/R_4 \equiv R_5/R_6$.
 The capacitors $C_3$ and $C_4$ are chosen such that $C_3 = \SI{22}{\pico\farad}$ and 
 \begin{align}
-\frac{C_4}{C_3} &= \frac{R_3}{R_4~||~R_5}
+\frac{C_4}{C_3} &= \frac{R_3}{R_4~||~R_5}\,,
 \end{align}

### 2016-01-22 piezo.tex
Added rudimentary noise analysis, changes to figures

@@
 \usepackage{siunitx}
+\DeclareSIUnit{\sqrthz}{\ensuremath{\sqrt{\text{\hertz}}}}
+
 \usepackage{amsmath}
@@
 \usepackage{graphicx}
+\usepackage{dcolumn}
+\usepackage{multirow}
 %\usepackage{caption}
@@
 \DeclareGraphicsRule{.ai}{pdf}{.ai}{}
+
+%% useful macros
+\newcommand{\epar}{~||~} % add impedances in parallel
 
@@
 Linear-type devices are typically constructed from a high-voltage operational amplifier (op-amp), powered either from a high voltage linear regulator or more typically from a secondary switching converter.
-While the op-amp provides \SI{100}{\decibel} or more of power-supply noise rejection, a high-voltage op-amp require substantially more power than an equivalent switching circuit.
+While the op-amp provides \SI{100}{\decibel} or more of power-supply noise rejection, a high-voltage op-amp requires substantially more power than an equivalent switching circuit.
 In either case, the output voltage  $V_{\text{out}}$ is typically given by
@@
 In flyback configuration, the internal-boost switch of the DRV2700 drives a step-up transformer.
-When the switch is closed, current flows through the primary coil of the transformer and induces a corresponding voltage across the secondary coil, which charges a capacitor at the output ($\text{C}_{\text{HV}}$ in Fig.~\ref{Fig:PiezoCircuit}).
-When the switch opens, a negative voltage appears across the secondary coil of the transformer, but a diode prevents the capacitor from discharging.
-One key benefit of this topology is the galvanically isolated output.
-By sensing the output voltage across a resistive divider, we feed back to the floating ground from the flyback converter to remove switching noise and stabilize the high voltage output; see Fig.~\ref{Fig:PiezoCircuit}.
+When the switch closes, current begins to flow through the primary coil of the transformer and induces a corresponding voltage across the secondary coil.
+In this state, the output diode is reverse-biased, and the capacitor ($\text{C}_{\text{HV}}$ in Fig.~\ref{Fig:PiezoCircuit}) holds its charge.
+When the switch opens, the voltage across the secondary coil is inverted, putting the diode into conduction and charging the capacitor.
+%One key benefit of this topology is the galvanically isolated output.
+%By sensing the output voltage across a resistive divider, we feed back to the floating ground from the flyback converter to remove switching noise and stabilize the high voltage output; see Fig.~\ref{Fig:PiezoCircuit}.
 
@@
 In isolation, the DRV2700 is not suited for low-noise laboratory instrumentation. 
-The output ripple, even after heavy filtering, can be as high as a few volts, and standard filtering techniques to reduce this noise simultaneously reduces the modulation control bandwidth.
+The output ripple, even after heavy filtering, can be as high as a few volts, and standard filtering techniques to reduce this noise simultaneously reduces the modulation bandwidth of the flyback regulator.
 Even if this were not the case, it remains unlikely that the RMS noise could be brought below $\SI{1}{\milli\volt}$, which is the operating regime we require for certain low-noise applications in the laboratory.
@@
 
+For a detailed noise analysis, see Sec.~\ref{Sec:NoiseAnalysis}.
+
 \subsection{Digital control and auxiliary design features}
@@
 \label{Sec:NoiseAnalysis}
+
+\begin{figure}[t]
+\includegraphics[width=\columnwidth]{fig/NoiseModel.ai}
+\caption{Noise model. \label{Fig:NoiseModel}}
+\end{figure}
+
+We analyze the noise performance of the circuit according to the model shown in Figure~\ref{Fig:NoiseModel}, where noise spectral densities are calculated at the node HV.
+Here, we consider contributions from the intrinsic op-amp noise, the DAC (injected at the node $V_{\text{DC}}$), Johnson-Nyquist noise of the passive components, and any additional noise injected at the modulation input node $V_{\text{mod}}$.
+We also discuss, given our choice of op-amp, the noise rejection ratio from the DRV2700 flyback regulator.
+
+First, the noise gain ($NG$) for this amplifier configuration is given by
+\begin{align}
+\label{Eq:NG}
+%NG(s) &= 1 + \frac{R_1 \epar C_1}{R_2 \epar \left(R_{\text{mod}} \epar C_{\text{mod}}\right)}
+%NG(s) &= 1 + \frac{R_1~||~C_1}{R_2R_{\text{mod}} C_{\text{mod}}}
+NG(s) &= 1 + \frac{Z_1}{R_2 \epar Z_{\text{mod}}}
+\end{align}
+where we've defined the equivalent impedances $Z_1 = R_1/(1+R_1 C_1 s)$ and $Z_{\text{mod}} = R_{\text{mod}}/(1+R_{\text{mod}} C_{\text{mod}} s)$, and $s = i\omega$ is the frequency in the Laplace domain.
+By design, we've chosen $Z_1 \equiv Z_{\text{mod}}$ such that the signal gain from the node $V_{\text{mod}}$ is unity.
+This reduces Eq.~(\ref{Eq:NG}) to
+\begin{align}
+\label{Eq:RedNG}
+NG(s) &= 2 + \frac{Z_1}{R_2}
+\end{align}
+
+The op-amp noise is parametrized by two noise contributions -- $e_n$, the input voltage noise power spectral density (PSD), and $i_n$, the input current noise PSD. 
+For the LM7171, $e_n = \SI[per-mode=symbol]{14}{\nano\volt\per\sqrthz}$ and $i_n = \SI[per-mode=symbol]{1.5}{\pico\ampere\per\sqrthz}$ at $\SI{10}{\kilo\hertz}$.
+The voltage noise is summed in at the non-inverting input, while the current noise is present at both inputs.
+To convert $i_n$ to an equivalent voltage noise $e_n$, we multiply by the impedances $Z_n$, $Z_p$ seen by the inverting and non-inverting nodes, respectively.
+These are calculated as
+\begin{align}
+\begin{split}
+\label{Eq:ZnZp}
+Z_n &= Z_1 \epar Z_{\text{mod}} \epar  R_2   = \frac{Z_1}{2} \epar R_2 \\
+Z_p &= R_{\text{LP}}  \big|\big|\frac{1}{s~C_{\text{LP}}}
+\end{split}
+\end{align}
+The total noise contribution of the op-amp (referenced to the output) is
+\begin{align}
+\label{Eq:OpAmpNoise}
+e_{n,\text{op-amp}} &= NG(s)\sqrt{e_n^2 + (Z_n i_n)^2 + (Z_p i_n)^2}
+\end{align}
+
+We now calculate the noise contribution of the DAC. 
+The noise signal gain from the node $V_{\text{DC}}$ is given by
+\begin{align}
+\begin{split}
+\label{Eq:Gdc}
+G_{\text{DC}} &= \left(\frac{1}{1+sR_{\text{LP}}C_{\text{LP}}}\right)\left(1+\frac{Z_1}{R_2\epar Z_{\text{mod}}}\right) \\
+&= \left(\frac{1}{1+sR_{\text{LP}}C_{\text{LP}}}\right)NG(s)
+\end{split}
+\end{align}
+Thus, the DAC voltage noise contribution is just $e_{n,\text{DAC}} = G_{\text{DC}} v_{n,\text{DAC}}$.
+The AD5663 has a white noise floor of \SI[per-mode=symbol]{100}{\nano\volt\per\sqrthz} (\SI{1}{\kilo\hertz} corner frequency).
+For our circuit, this is the dominant noise contribution.
+Each noise source is shown and tabulated in Table~\ref{Tab:noise}.
+
+\begin{table}
+\caption{Various noise contributions. -- should we just tabulate RMS?}
+\label{Tab:noise}
+\begin{ruledtabular}
+\centering
+\begin{tabular}{lcc}
+ \multirow{2}{*}{Noise source} & \multicolumn{2}{c}{Voltage PSD (\si[per-mode=symbol]{\nano\volt\per\sqrthz})} \\ \cline{2-3}
+\rule{0pt}{3ex} & (input-referred) & (output-referred) \\ 
+\hline
+$e_n$ (op-amp) & \SI{14} (white); \SI{30} ($1/f$)  & \\
+$i_n$ (op-amp) &    & \\
+DAC &    & \\
+Johnson-Nyquist & & \\ \hline
+\textbf{total} & &
+\end{tabular}
+\end{ruledtabular}
+\end{table}
 

### 2016-01-22 piezo.tex
Added text to Digital control/auxiliary design section

@@
 We now explain the operation of each sub-block, and draw attention to important design details. 
+The full schematic, including Gerbers, Bill of Materials, and layout design files, can be found on GitHub~\footnote{\protect\url{https://github.com/JQIamo/piezo-compact-high-voltage-driver}}.
 
@@
 \label{Sec:DigControlAuxDesign}
+
+The DC setpoint is controlled by a low-noise digital-to-analog (DAC) converter.
+This has several advantages: digital control enhances repeatability, and makes it easy to interface with a wide variety of control electronics to, eg, implement a slow infinite integrator [expand on this?].
+A wide array of high-resolution DACs are available with very good noise characteristics.
+We initially chose to use an AD5563R, but found that our performance was ultimately limited by $1/f$ noise in the DAC itself.
+The final design uses an XXX, with XXX external reference, such that the noise contribution from the DAC is comparable to the noise contribution from the LM7171 (see Sec.~\ref{Sec:NoiseAnalysis}).
+
+The DAC is controlled by an integrated microcontroller, which also interfaces with the frontpanel control switches, encoders, and LCD display.
+The microcontroller is also attached via the backplane [talk about eurocard rack somewhere?] to a secondary microcontroller which can be addressed over TCP/IP.
+This vastly expands the conceivable control scenarios; for example, in our lab we implement a slow-feedback lock of two ECDL repumping lasers to a wavemeter. 
+LabView code on the computer attached to the wavemeter computes an error signal and corrective control voltage, which can then be passed over our internal network to the piezo driver to correct for frequency drift in the laser.
+Other similar schemes are possible, enabling complete remote control of the laser electronics.
+
+In addition to the digital setpoint control, a voltage proportional to the high voltage output is connected to a GPIO line on the backplane.
+This is fed to a low-noise current controller (based on the design in~\ref{DurfeeFIX}) to implement feed-forward (cite?).
+An optional analog voltage from the backplane can also be summed with the modulation voltage supplied via BNC on the front panel to generate $V_{\text{mod}}$.
+This may be useful, eg, with servo controllers that reside in the same rack as the other control electronics.
 

### 2016-01-22 piezo.tex
Added additional info about frontpanel control

@@
 
+Control via the frontpanel is provided by a rotary encoder/push button, and a single on/off switch.
+The rotary encoder/push button switch allows interaction with a user-definable menu system.
+For example, this allows the user to quickly switch the piezo driver into ``ramp'' mode to scan a laser over some resonance feature.
+
 In addition to the digital setpoint control, a voltage proportional to the high voltage output is connected to a GPIO line on the backplane.
@@
 This may be useful, eg, with servo controllers that reside in the same rack as the other control electronics.
+
+Finally, the high voltage output is interlocked with a signal on the back plane (which can optionally be over-ridden by placing a jumper onboard); this allows easy integration into existing laboratory interlock schemes.
 

### 2016-01-25 piezo.tex
changes up through flyback circuit; notes on what to measure

@@
 
-The design is based on the newly-available Texas Instruments DRV2700 piezo driver.
-\footnote{The identification of commercial products is for information only and does not imply recommendation or endorsement by the National Institute of Standards and Technology.}
-This single-chip integrated circuit (IC) can be operated as a boost converter to drive an on-chip differential amplifier up to \SI{100}{\volt}, or as a flyback converter up to \SI{1}{\kilo\volt}.
-In flyback configuration, the internal-boost switch of the DRV2700 drives a step-up transformer.
-When the switch closes, current begins to flow through the primary coil of the transformer and induces a corresponding voltage across the secondary coil.
-In this state, the output diode is reverse-biased, and the capacitor ($\text{C}_{\text{HV}}$ in Fig.~\ref{Fig:PiezoCircuit}) holds its charge.
-When the switch opens, the voltage across the secondary coil is inverted, putting the diode into conduction and charging the capacitor.
-%One key benefit of this topology is the galvanically isolated output.
-%By sensing the output voltage across a resistive divider, we feed back to the floating ground from the flyback converter to remove switching noise and stabilize the high voltage output; see Fig.~\ref{Fig:PiezoCircuit}.
-
 \begin{figure*}[t]
@@
 
+The design is based on the newly-available Texas Instruments DRV2700 piezo driver.
+\footnote{The identification of commercial products is for information only and does not imply recommendation or endorsement by the National Institute of Standards and Technology.}
+This single-chip integrated circuit (IC) can be operated as a boost converter to drive an on-chip differential amplifier up to \SI{100}{\volt}, or as a flyback converter up to \SI{1}{\kilo\volt}.
+In flyback configuration, the internal-boost switch of the DRV2700 drives a step-up transformer.
+When the switch closes, current begins to flow through the primary coil of the transformer and induces a corresponding voltage across the secondary coil.
+In this state, the output diode is reverse-biased, and the capacitor ($\text{C}_{\text{HV}}$ in Fig.~\ref{Fig:PiezoCircuit}) holds its charge.
+When the switch opens, the voltage across the secondary coil is inverted, putting the diode into conduction and charging the capacitor.
+By changing the rate at which the switch is engaged, the DRV2700 is able to regulate a particular voltage at the output.
+
 In isolation, the DRV2700 is not suited for low-noise laboratory instrumentation. 
-The output ripple, even after heavy filtering, can be as high as a few volts, and standard filtering techniques to reduce this noise simultaneously reduces the modulation bandwidth of the flyback regulator.
+The output ripple, even after heavy filtering, can be as high as a few volts, and standard filtering techniques to reduce this noise simultaneously reduce the modulation bandwidth of the flyback regulator.
 Even if this were not the case, it remains unlikely that the RMS noise could be brought below $\SI{1}{\milli\volt}$, which is the operating regime we require for certain low-noise applications in the laboratory.
-Despite this drawback, the flyback converter requires very little current to operate and leverages a compact IC to generate very high voltages, making it versatile and easy to deploy in the lab.
+Despite this drawback, the flyback converter requires very little current to operate and leverages a compact IC to generate high voltages without the need of an auxiliary supply.
 
-The motivation behind our hybrid architecture is twofold.
-First, to make a switching converter useful for low-noise laboratory instrumentation, we need a way to remove the output ripple and residual switching noise.
-Second, we want to take advantage of low-noise op-amps that only work up to tens of volts to provide a unity gain (DC-coupled) feedback path to the high voltage output.
-The architecture shown in Fig.~\ref{Fig:PiezoCircuit} does just this; a low-noise, high-slew rate op-amp ($\mathbf{U2}$) adjusts the floating ground node of the transformer output to cancel switching noise and sum in an offset given by $V_{\text{mod}}$, while the flyback regulator works close to DC to impose the high voltage across the HV - floating ground output.
-We now explain the operation of each sub-block, and draw attention to important design details. 
-The full schematic, including Gerbers, Bill of Materials, and layout design files, can be found on GitHub~\footnote{\protect\url{https://github.com/JQIamo/piezo-compact-high-voltage-driver}}.
+The architecture presented in this paper uses an active feedback element (U2, described in Sec.~\ref{Sec:LowNoiseStabilization}) to remove switching noise and residual ripple at the high-voltage output of the flyback regulator.
+Additionally, U2 provides a DC-coupled, unity-gain feedback path to the high voltage node, which can be used for closed-loop servo applications and high-bandwidth modulation.
+This design shows how researchers might leverage the versatility of galvanically isolated switching regulators (such as the DRV2700) in a low-noise laboratory environment.
+[versatile and easy to deploy in the lab.]
+
+In the next few sections, we provide details on each sub-block of the circuit and draw attention to important design details.
+The full schematic, including Gerbers, bill of materials, and layout design files, can be found on GitHub~\footnote{\protect\url{https://github.com/JQIamo/piezo-compact-high-voltage-driver}}.
 
@@
 Internally, the DRV2700 boost controller tries to drive the FB node to \SI{1.3}{\volt}.
-The op-amp U1 senses the voltage at node \textit{HV} and \textit{GND}${}_\text{HV}$, and adjusts its output such that
+The op-amp U1 senses the voltage at node HV and $\text{GND}_\text{HV}$, and adjusts its output such that
 \begin{align}
@@
 
+The galvanically isolated output of the flyback regulator is passed through a four-pole, low-pass RC filter (corner frequency $f_c \approx \SI{3}{\kilo\hertz}$). 
+Additional capacitors on both the HV and $\text{GND}_{\text{HV}}$ resistor networks shunt high frequency noise to ground. 
+The DRV2700 IC, combined with the feedback provided by U1, regulates the voltage difference $(\text{HV}-\text{GND}_{\text{HV}}) = G\cdot V_{\text{dc}}$.
+The gain $G = 50$ for the design implemented in our lab, allowing a \SI{5}{\volt} DAC to span \SI{0}{\volt} -- \SI{250}{\volt}.
+
+Careful attention was paid to the layout...
+
 Notes here about expected, measured bandwidth??
-
-The DRV2700 IC, combined with the the feedback provided by U1, regulates the voltage $(\text{HV}-\text{GND}_{\text{HV}}) = G\cdot V_{\text{dc}}$.
-Careful attention was paid to the layout ...
 
@@
 
+We characterized the performance of the high-voltage piezo driver with a few different metrics.
+In Fig.~XX, you can see the noise power spectral density.
+This trace was taken on an SRSXXX spectrum analyzer, AC coupled to the high-voltage output with a \SI{0.5}{\hertz} high-pass filter circuit shown in Fig.~XX(b).
+
+\begin{itemize}
+\item $1/f \rightarrow$ white noise corner frequency
+\item white noise spectral density
+\item RMS noise (0.1 - 10 Hz; 10 Hz - 10 kHz, or something similar) -- use SRS voltage preamp?
+\item How effective is the LM7171 at reducing switching noise? look at FFT power before final filter resistor, and at output of op amp (dBc spec)
+\item compare noise to predicted values
+\item longterm trace on kiethly -- across voltage divider at output? Monitor vs temperature? -- need to find low Tc resistors, at least.
+\item see what dependence is on power source -- eg, JQI power supply vs lab supply vs very quiet voltage regulator?
+\item current draw -- display in some ``bottom line'' specs table?
+\item bandwidth measurements -- full scale triangle ramp, small signal bandwidth -- discuss limitations on this (eg, also versus different piezo loads)
+\item Lock a laser, show RMS noise fluct vs. old piezo?
+\end{itemize}
+
 \section{Conclusion}

### 2016-01-25 piezo.tex
Added details to low-noise stabilization section
Discussion of resistor 1/f noise

@@
 A fast, very high slew-rate op-amp senses the output voltage across $R_1$ and $R_2$, and servos it by modulating the node at ``HV floating gnd''.
-The $V_{\text{DC}}$ gain is set by $\left(1+R_1/R_2\right)$, while the modulation gain is set by $-R_{\text{mod}}/R_{\text{fb}}$.
+The $V_{\text{DC}}$ gain is set by $\left(1+R_1/R_2\right)$, while the modulation gain is set by $-R_{\text{mod}}/R_1$.
 The capacitor linking the floating ground node to the output allows the op-amp to remove residual switching noise and stabilize the DC output according to the transfer function given in Eq.~(\ref{Eq:PiezoTransfer}).
-\label{Fig:PiezoCircuit}}
+-- Add back in second set of shunt caps!\label{Fig:PiezoCircuit}}
 \end{figure*}
@@
 
-The low-noise stabilization circuitry was added to remove output ripple and residual switching noise, however it serves a dual purpose as a low-gain, high-bandwidth modulation path to the high-voltage output.
-It uses a very high slew-rate (\SI{4100}{\volt\per\micro\second}) op-amp, the LM7171, connected to the filtered ground node of the flyback converter.
-At high frequencies, the output of this op-amp appears directly at the HV node through the capacitor $C_{\text{out}}$.
-Below the corner set by $C_{\text{out}}$, the output of U2 adjusts the floating ground reference of the flyback converter.
+The low-noise stabilization circuit is crucial to the performance of the design, as it is responsible for removing noise at the output of the flyback converter.
+To accomplish this task, a high slew-rate op-amp (Texas Instruments LM7171, \SI{4100}{\volt\per\micro\second}) drives the galvanically isolated ground node of the flyback converter (see U2 in Fig.~\ref{Fig:PiezoCircuit}).
+This op-amp enforces the HV output voltage
+\begin{align}
+\text{V}_\text{HV} &= \left(1 + \frac{R_1}{R_2~||~R_\text{mod}}\right) \text{V}_\text{DC} -
+\left(\frac{R_\text{mod}}{R_1}\right) \text{V}_\text{mod}
+\end{align}
+We choose $R_1, R_\text{mod} = \SI{1}{\mega\ohm}$, $R_2 = \SI{20.5}{\kilo\ohm}$ such that the DC gain is $\approx 50$ and the modulation gain is unity.
+Depending on the application, however, other gain configurations would work equally well provided the non-inverting gain of U2 closely matches the gain of the flyback regulator since they derive from the same control voltage.
+Ultimately, the op-amp U2 sets the operating voltage of the output, while the flyback converter regulates the high voltage difference between $\text{GND}_\text{HV}$ and the output.
+Because the output of the flyback regulator is galvanically isolated, U2 is free to control the $\text{GND}_\text{HV}$ node at ``low'' voltages, which are transferred directly to the high voltage output.
 
-After the passive filter ladder connecting the DRV2700 flyback converter the output,
+%The low-noise stabilization circuitry was added to remove output ripple and residual switching noise, however it serves a dual purpose as a low-gain, high-bandwidth modulation path to the high-voltage output.
+%It uses a very high slew-rate (\SI{4100}{\volt\per\micro\second}) op-amp, the LM7171, connected to the filtered ground node of the flyback converter.
+%At high frequencies, the output of this op-amp appears directly at the HV node through the capacitor $C_{\text{out}}$.
+%Below the corner set by $C_{\text{out}}$, the output of U2 adjusts the floating ground reference of the flyback converter.
+
+%After the passive filter ladder connecting the DRV2700 flyback converter the output,
 %At high frequencies, this modulation appears directly at the HV node through the capacitors.
@@
 
-The choice of component for resistors $R_1$ and $R_2$ is crucial for the low-noise performance of the system. (cite LIGO paper)
+The choice of component for resistors $R_1$ and $R_2$ is crucial for the low-noise performance of the system, because this resistive divider is responsible for accurately sensing the high voltage output and noise contributions thus appear directly at the output.
+Resistors are fundamentally limited by Johnson noise, in which thermal fluctuations contribute to a white noise power spectrum given by $\sqrt{k_B T R}$.
+However, resistors also exhibit $1/f$ current noise caused by equilibrium fluctuations of the resistance~\cite{Clarke1974a,Voss1976a}.
+The magnitude of this ``excess noise'' is highly dependent on the resistor composition, and varies from manufacturer to manufacturer.
+Reference~\cite{Seifert2009a} characterized $1/f$ noise in a variety of resistors, and found that the Vishay TNPW \SI{0.1}{\percent}-series resistors showed a noise spectrum almost consistent with Johnson noise down to \SI{1}{\hertz}.
+A previous iteration of this design used Panasonic ERJ-8ENF resistors (1206, \SI{1}{\percent}), and we noticed substantial low-frequency noise correlated with varying strain on the PCB.
+This is consistent with the findings in~\cite{Seifert2009a}, which showed this Panasonic series to exhibit voltage noise two orders of magnitude larger than the TNPW series at \SI{1}{\hertz}.
 

### 2016-01-26 piezo.tex
modified introduction

@@
 Often, these applications are operated in a closed feedback loop, where small voltage changes on top of a large DC voltage are necessary to stabilize the output of a particular system.
-For example, extended-cavity diode lasers adjust their lasing frequency by changing the angle of a diffraction grating that supplies optical feedback to the diode.
-To stabilize this frequency, a servo controller measures deviations from the desired value and adjusts the voltage controlling the grating angle to correct for any difference.
-Because the servo electronics operate at low voltage, a secondary high-voltage (HV) amplifier is required to drive the piezoelectric actuator.
-This HV gain stage typically accepts an external ``modulation input'', $V_{\text{mod}}$, and produces an amplified voltage $V_{\text{out}}$ according to
-\begin{align}
-V_{\text{out}} = G_p V_{\text{mod}} + V_0
-\end{align}
-where $G_p$ is the amplifier gain and $V_0$ is an optional DC offset.
-Typically, {$G_p\approx \num{10} - \num{20}$} or more such that reasonable voltages $V_{\text{mod}}$ can span the entire output range $V_{\text{out}}$.
-
-It is often the case, however, that in closed-loop feedback applications we do not need and often do not want the modulation control to have a high gain.
-Because the closed loop gain $G \equiv G_s G_p$ cannot be increased without limit, $G_p \gg 1$ means the servo gain $G_s$ must be proportionally smaller to keep the lock stable.
-In locked configuration, any noise introduced by the servo is suppressed by $1/|G_s|$ in the large gain limit.
-If $G_s$ is limited to achieve a stable lock, it is no longer effective at servoing its own noise.
-
-To avoid this problem, we desire a high voltage amplifier which separates the ``setpoint'' gain, $G_{\text{dc}}$, from the modulation gain, $G_{\text{mod}}$. That is,
-\begin{align}
-  V_{\text{out}} &= G_{\text{dc}} V_{\text{dc}} + G_{\text{mod}} V_{\text{mod}}\, \text{,}
-  \label{Eq:PiezoTransfer}
-\end{align}
-where now we can make $G_{\text{mod}} \approx 1$.
+For example, extended-cavity diode lasers adjust their lasing frequency by changing the angle of a piezo-actuated diffraction grating that supplies optical feedback to the diode.
+High-voltage piezoelectric drivers typically provide a ``modulation input'' for  such closed-loop applications, where the input voltage is either DC coupled and gained such that the input range spans the entire output range of the driver, or AC coupled directly to the output.
+While this may have certain advantages, many applications would benefit from an architecture that provides a unity gain, DC-coupled feedback path to the high voltage output -- such a device would make closed-loop piezoelectric systems less susceptible to noise contributions from the servo controller.
+Indeed, in our laboratory, we often find this to be the limiting factor in the stability of our laser frequency locks.
 
@@
 Linear-type devices are typically constructed from a high-voltage operational amplifier (op-amp), powered either from a high voltage linear regulator or more typically from a secondary switching converter.
-While the op-amp provides \SI{100}{\decibel} or more of power-supply noise rejection, a high-voltage op-amp requires substantially more power than an equivalent switching circuit.
-In either case, the output voltage  $V_{\text{out}}$ is typically given by
-\begin{align}
-  V_{\text{out}} &= G_p(V_{\text{DC}} + V_{\text{mod}})\, \text{,}
-\end{align}
-where $G_p$ is the piezo amplifier gain, $V_{\text{DC}}$ is a DC setpoint, and $V_{\text{mod}}$ is a modulation input used for closed-loop control.
+While the op-amp provides \SI{100}{\decibel} or more of power-supply noise rejection, a high-voltage op-amp requires substantially more power than an equivalent switching circuit and is thus more cumbersome to deploy in the laboratory.
+
+Here, we present an architecture which combines the best of both worlds: a high-voltage piezoelectric driver with excellent noise characteristics that can be powered from a standard low-current, low-voltage supply.
+The DC operating point is controlled digitally, and an analog input provides a DC-coupled, unity-gain feedback path ($\pm\SI{10}{\volt}$) to the output.
+The following design is versatile and easy to deploy throughout the lab in a variety of high-voltage applications.
 
@@
 
-The design is based on the newly-available Texas Instruments DRV2700 piezo driver.
-\footnote{The identification of commercial products is for information only and does not imply recommendation or endorsement by the National Institute of Standards and Technology.}
+The design is based on the newly-available Texas Instruments DRV2700 piezo driver\footnote{The identification of commercial products is for information only and does not imply recommendation or endorsement by the National Institute of Standards and Technology.}, however it is easily modified to work with any galvanically isolated DC-DC converter.
 This single-chip integrated circuit (IC) can be operated as a boost converter to drive an on-chip differential amplifier up to \SI{100}{\volt}, or as a flyback converter up to \SI{1}{\kilo\volt}.
@@
 \item Lock a laser, show RMS noise fluct vs. old piezo?
+\item compare to SC100 toptica controller? even if just internally.
 \end{itemize}

### 2016-01-26 piezo.tex
Reworked intro to circuit description
* Repartitioned "intro" and flyback regulator section; other mods

@@
 
-Traditionally, laboratory electronics capable of supplying high voltages fall under one of two architectural umbrellas: switching converters, and ``linear'' amplifiers.
-DC-DC converters are efficient and can work at very high voltages, but suffer from switching noise and limited control bandwidths.
-Linear-type devices are typically constructed from a high-voltage operational amplifier (op-amp), powered either from a high voltage linear regulator or more typically from a secondary switching converter.
-While the op-amp provides \SI{100}{\decibel} or more of power-supply noise rejection, a high-voltage op-amp requires substantially more power than an equivalent switching circuit and is thus more cumbersome to deploy in the laboratory.
-
-Here, we present an architecture which combines the best of both worlds: a high-voltage piezoelectric driver with excellent noise characteristics that can be powered from a standard low-current, low-voltage supply.
-The DC operating point is controlled digitally, and an analog input provides a DC-coupled, unity-gain feedback path ($\pm\SI{10}{\volt}$) to the output.
-The following design is versatile and easy to deploy throughout the lab in a variety of high-voltage applications.
+%Here, we present an architecture which combines the best of both worlds: a high-voltage piezoelectric driver with excellent noise characteristics that can be powered from a standard low-current, low-voltage supply.
+%The DC operating point is controlled digitally, and an analog input provides a DC-coupled, unity-gain feedback path ($\pm\SI{10}{\volt}$) to the output.
+%The following design is versatile and easy to deploy throughout the lab in a variety of high-voltage applications.
 
@@
 \caption{Schematic of the high voltage stabilization.
-The voltage HV is generated using a Texas Instruments DRV2700 high voltage driver in flyback configuration (see Fig.~\ref{Fig:DRV2700}).
+The voltage HV is generated using a Texas Instruments DRV2700 high voltage driver in flyback configuration.
 A fast, very high slew-rate op-amp senses the output voltage across $R_1$ and $R_2$, and servos it by modulating the node at ``HV floating gnd''.
@@
 
-The design is based on the newly-available Texas Instruments DRV2700 piezo driver\footnote{The identification of commercial products is for information only and does not imply recommendation or endorsement by the National Institute of Standards and Technology.}, however it is easily modified to work with any galvanically isolated DC-DC converter.
+Traditionally, laboratory electronics capable of supplying high voltages fall under one of two architectural umbrellas: DC-DC switching converters, and ``linear'' amplifiers.
+DC-DC converters are efficient and can work at very high voltages, but suffer from switching noise and limited control bandwidths.
+Linear-type devices are typically constructed from a high-voltage operational amplifier (op-amp), powered either from a high voltage linear regulator or more typically from a secondary switching converter.
+While the op-amp provides \SI{100}{\decibel} or more of power-supply noise rejection, high-voltage op-amps requires substantially more power than an equivalent switching circuit and are more cumbersome to deploy in the laboratory.
+
+Here, we present a hybrid architecture (see Fig.~\ref{Fig:PiezoCircuit} for details).
+The high voltage is generated by a galvanically isolated switching converter (described in Sec.~\ref{Sec:DRV2700}), while a low-noise, high slew-rate op-amp removes the switching noise by modulating the \textbf{OUT--} node of the DC-DC converter (Sec.~\ref{Sec:LowNoiseStabilization}).
+This op-amp additionally provides a low-gain, high-bandwidth modulation input for closed-loop feedback applications.
+
+The design principles discussed below show how researchers might leverage the versatility of galvanically isolated switching regulators in a low-noise laboratory environment; straightforward modifications to the schematic make it possible to tailor the high voltage driver to a specific application.
+The entire electronics package fits comfortably into a 12HP eurocard rack module, and draws less than \SI{50}{\milli\ampere} at \SI{15}{\volt} [get real numbers].
+The full schematic, including Gerbers, a bill of materials, and layout design files, can be found on GitHub~\footnote{\protect\url{https://github.com/JQIamo/piezo-compact-high-voltage-driver}}.
+
+\subsection{Flyback regulator}
+\label{Sec:DRV2700}
+
+The high voltage DC-DC converter used here is based on the newly-available Texas Instruments DRV2700 piezo driver\footnote{The identification of commercial products is for information only and does not imply recommendation or endorsement by the National Institute of Standards and Technology.}.
 This single-chip integrated circuit (IC) can be operated as a boost converter to drive an on-chip differential amplifier up to \SI{100}{\volt}, or as a flyback converter up to \SI{1}{\kilo\volt}.
@@
 When the switch opens, the voltage across the secondary coil is inverted, putting the diode into conduction and charging the capacitor.
-By changing the rate at which the switch is engaged, the DRV2700 is able to regulate a particular voltage at the output.
+By changing the rate at which the switch is engaged, the DRV2700 is able to regulate a particular voltage across the galvanically isolated output (nodes $\text{GND}_\text{HV}$ and HV in Fig.~\ref{Fig:PiezoCircuit}).
 
-In isolation, the DRV2700 is not suited for low-noise laboratory instrumentation. 
-The output ripple, even after heavy filtering, can be as high as a few volts, and standard filtering techniques to reduce this noise simultaneously reduce the modulation bandwidth of the flyback regulator.
-Even if this were not the case, it remains unlikely that the RMS noise could be brought below $\SI{1}{\milli\volt}$, which is the operating regime we require for certain low-noise applications in the laboratory.
-Despite this drawback, the flyback converter requires very little current to operate and leverages a compact IC to generate high voltages without the need of an auxiliary supply.
-
-The architecture presented in this paper uses an active feedback element (U2, described in Sec.~\ref{Sec:LowNoiseStabilization}) to remove switching noise and residual ripple at the high-voltage output of the flyback regulator.
-Additionally, U2 provides a DC-coupled, unity-gain feedback path to the high voltage node, which can be used for closed-loop servo applications and high-bandwidth modulation.
-This design shows how researchers might leverage the versatility of galvanically isolated switching regulators (such as the DRV2700) in a low-noise laboratory environment.
-[versatile and easy to deploy in the lab.]
-
-In the next few sections, we provide details on each sub-block of the circuit and draw attention to important design details.
-The full schematic, including Gerbers, bill of materials, and layout design files, can be found on GitHub~\footnote{\protect\url{https://github.com/JQIamo/piezo-compact-high-voltage-driver}}.
-
-\subsection{DRV2700 flyback regulator}
-\label{Sec:DRV2700}
-
-We based the flyback regulator design off the suggested schematic in the DRV2700 datasheet and evaluation module application note.
-At a basic level, the DRV2700 flyback circuit requires a transformer (ATB3225; 1:10 step-up winding, \SI{7}{\micro\henry} inductance, rated for \SI{0.6}{\ampere}) connected to an output diode and capacitor, and a ``sense'' voltage supplied to the feedback (FB) node of the IC.
+The transformer (ATB3225, 1:10 step-up winding), diode, and RC feedback network are based on values suggested in the DRV2700 datasheet~\cite{DRV2700Datasheet,DRV2700EVMUserGuide}.
 Internally, the DRV2700 boost controller tries to drive the FB node to \SI{1.3}{\volt}.
@@
 \label{Eq:U1Output}
-\text{HV} &= G\cdot V_{\text{dc}} + \text{GND}_{\text{HV}}\,,
+\text{HV} - \text{GND}_{\text{HV}} &= G\cdot V_{\text{dc}}\,,
 \end{align}
@@
 \end{align}
-as suggested by the datasheet.
-This pseudo-differential configuration ensures that, in the equilibrium given by Eq.~(\ref{Eq:U1Output}), the output of U1 is driven to \SI{0}{\volt}; the resistive divider $R_9$ and $R_{10}$ is then chosen such that $R_9/(R_9~||~R_{10}) = \SI{1.3}{\volt}/\SI{5}{\volt} \approx \num{0.26}$.
+as suggested by the datasheet, and $R_6 = R_7 = R_8$.
+In our lab, we implement a gain $G\approx 50$ ($R_3 = R_5 = \SI{499}{\kilo\ohm}$; $R_4 = R_{6-8} = \SI{10}{\kilo\ohm}$) such that a \SI{5}{\volt} digital-to-analog (DAC) converter at $V_\text{DC}$ can span \SI{0}{\volt} -- \SI{250}{\volt}.
 
-The galvanically isolated output of the flyback regulator is passed through a four-pole, low-pass RC filter (corner frequency $f_c \approx \SI{3}{\kilo\hertz}$). 
+This pseudo-differential configuration ensures that, in the equilibrium given by Eq.~(\ref{Eq:U1Output}), the output of U1 is driven to \SI{0}{\volt}; the resistive divider $R_9$ and $R_{10}$ is then chosen such that $R_{10}/(R_9~||~R_{10}) = \SI{1.3}{\volt}/\SI{5}{\volt} \approx \num{0.26}$.
+
+The output of the flyback regulator is passed through a four-pole, low-pass RC filter.
+The corner frequency $f_c \approx \SI{3}{\kilo\hertz}$ is chosen to be high enough that a slow ($\approx \SI{10}{\hertz}$) rail-to-rail triangle ramp can be applied at $V_\text{DC}$ (for, e.g., sweeping over a spectroscopy resonance), but low enough that the $\approx \SI{100}{\kilo\hertz}$ switching noise is attenuated.
 Additional capacitors on both the HV and $\text{GND}_{\text{HV}}$ resistor networks shunt high frequency noise to ground.
-The DRV2700 IC, combined with the feedback provided by U1, regulates the voltage difference $(\text{HV}-\text{GND}_{\text{HV}}) = G\cdot V_{\text{dc}}$.
-The gain $G = 50$ for the design implemented in our lab, allowing a \SI{5}{\volt} DAC to span \SI{0}{\volt} -- \SI{250}{\volt}.
 
@@
 Depending on the application, however, other gain configurations would work equally well provided the non-inverting gain of U2 closely matches the gain of the flyback regulator since they derive from the same control voltage.
-Ultimately, the op-amp U2 sets the operating voltage of the output, while the flyback converter regulates the high voltage difference between $\text{GND}_\text{HV}$ and the output.
+Ultimately, the op-amp U2 sets the operating voltage of the output referenced to true circuit ground, while the flyback converter regulates the high voltage relative to the pseudoground node $\text{GND}_\text{HV}$.
 Because the output of the flyback regulator is galvanically isolated, U2 is free to control the $\text{GND}_\text{HV}$ node at ``low'' voltages, which are transferred directly to the high voltage output.
@@
 The DC setpoint is controlled by a low-noise digital-to-analog (DAC) converter.
-This has several advantages: digital control enhances repeatability, and makes it easy to interface with a wide variety of control electronics to, eg, implement a slow infinite integrator [expand on this?].
+This has several advantages: digital control enhances setpoint repeatability, and makes it easy to interface with a wide variety of control electronics to, eg, implement a slow infinite integrator [expand on this?].
 A wide array of high-resolution DACs are available with very good noise characteristics.

### 2016-05-31 piezo.tex
Formatting changes; added LP filter switch to schematic

@@
 The low-noise stabilization circuit is crucial to the performance of the design, as it is responsible for removing noise at the output of the flyback converter.
-To accomplish this task, a high slew-rate op-amp (Texas Instruments LM7171, \SI{4100}{\volt\per\micro\second}) drives the galvanically isolated ground node of the flyback converter (see U2 in Fig.~\ref{Fig:PiezoCircuit}).
+To accomplish this task, a high slew-rate op-amp (Texas Instruments LM7171, \SI[per-mode=symbol]{4100}{\volt\per\micro\second}) drives the galvanically isolated ground node of the flyback converter (see U2 in Fig.~\ref{Fig:PiezoCircuit}).
 This op-amp enforces the HV output voltage
@@
 \end{figure}
+\begin{figure}[t]
+\includegraphics[width=\columnwidth]{calc/NoiseContrib.pdf}
+\caption{Noise Contributions (color online).
+Plotted are the noise contributions from each source in our model -- op-amp current noise (dashed orange) and voltage noise (dotted blue); Johnson noise (dash-dotted green), DAC noise (long dashed red), and total noise (solid purple).
+Power spectral density is referred to the high voltage output.\label{Fig:NoisePlot}}
+\end{figure}
 
-We analyze the noise performance of the circuit according to the model shown in Figure~\ref{Fig:NoiseModel}, where noise spectral densities are calculated at the node HV.
-Here, we consider contributions from the intrinsic op-amp noise, the DAC (injected at the node $V_{\text{DC}}$), Johnson-Nyquist noise of the passive components, and any additional noise injected at the modulation input node $V_{\text{mod}}$.
-We also discuss, given our choice of op-amp, the noise rejection ratio from the DRV2700 flyback regulator.
+We analyze the noise performance of the circuit according to the model shown in Fig.~\ref{Fig:NoiseModel}, where noise spectral densities are calculated at the node HV.
+A summary of each noise contribution (op-amp, DAC, Johnson-Nyquist, external modulation input) is shown in Table~\ref{Tab:noise}, along with the cumulative root-mean-square (RMS) nose estimates in different frequency bands.
+% We also discuss, given our choice of op-amp, the noise rejection ratio from the DRV2700 flyback regulator.
+% -- not sure about how to do this... could just report the measured value:
 
-First, the noise gain ($NG$) for this amplifier configuration is given by
+To treat the intrinsic op-amp noise contributions, we first compute the noise gain ($NG$) for this amplifier configuration according to
 \begin{align}
 \label{Eq:NG}
-%NG(s) &= 1 + \frac{R_1 \epar C_1}{R_2 \epar \left(R_{\text{mod}} \epar C_{\text{mod}}\right)}
-%NG(s) &= 1 + \frac{R_1~||~C_1}{R_2R_{\text{mod}} C_{\text{mod}}}
-NG(s) &= 1 + \frac{Z_1}{R_2 \epar Z_{\text{mod}}}
+NG(s) &= 1 + \frac{Z_1}{R_2 \epar Z_{\text{mod}}}\,,
 \end{align}
@@
 \label{Eq:RedNG}
-NG(s) &= 2 + \frac{Z_1}{R_2}
+NG(s) &= 2 + \frac{Z_1}{R_2}\,.
 \end{align}
@@
 The op-amp noise is parametrized by two noise contributions -- $e_n$, the input voltage noise power spectral density (PSD), and $i_n$, the input current noise PSD.
-For the LM7171, $e_n = \SI[per-mode=symbol]{14}{\nano\volt\per\sqrthz}$ and $i_n = \SI[per-mode=symbol]{1.5}{\pico\ampere\per\sqrthz}$ at $\SI{10}{\kilo\hertz}$.
+For the LM7171, $e_n = \SI[per-mode=symbol]{14}{\nano\volt\per\sqrthz}$ and $i_n = \SI[per-mode=symbol]{1.5}{\pico\ampere\per\sqrthz}$ at $\SI{10}{\kilo\hertz}$, with a $1/f$ noise character below this frequency~\cite{LM7171Datasheet}.
 The voltage noise is summed in at the non-inverting input, while the current noise is present at both inputs.

### 2016-06-04 piezo.tex
Mostly done, going through edits

@@
 % That way, you always have this original template file to use.
-\documentclass[aip,rsi,reprint]{revtex4-1} % for checking your page length
+%\documentclass[aip,rsi,reprint]{revtex4-1} % for checking your page length
 %\documentclass[aip,rsi,reprint,graphicx,draft]{revtex4-1} % for checking your page length
-%\\documentclass[aip,rsi,preprint,graphicx]{revtex4-1} % for review purposes
+\documentclass[aip,rsi,preprint,graphicx]{revtex4-1} % for review purposes
 
@@
 \usepackage{graphicx}
+\usepackage[caption=false]{subfig}
 \usepackage{dcolumn}
@@
 
-The high voltage DC-DC converter used here is based on the newly-available Texas Instruments DRV2700 piezo driver\footnote{The identification of commercial products is for information only and does not imply recommendation or endorsement by the National Institute of Standards and Technology.}.
-This single-chip integrated circuit (IC) can be operated as a boost converter to drive an on-chip differential amplifier up to \SI{100}{\volt}, or as a flyback converter up to \SI{1}{\kilo\volt}.
+The high voltage DC-DC converter used here is based on the Texas Instruments DRV2700 piezo driver\footnote{The identification of commercial products is for information only and does not imply recommendation or endorsement by the National Institute of Standards and Technology.}.
+This single-chip integrated circuit (IC) can be operated as a boost converter to drive an on-chip differential amplifier up to \SI{100}{\volt}, or as a flyback converter up to \SI{1}{\kilo\volt} or more.
 In flyback configuration, the internal-boost switch of the DRV2700 drives a step-up transformer.
@@
 where the gain $G$ is set by the resistor ratio $R_3/R_4 \equiv R_5/R_6$.
+This pseudo-differential feedback configuration ensures that, in the equilibrium given by Eq.~(\ref{Eq:U1Output}), the output of U1 is driven to \SI{0}{\volt}; the resistive divider $R_9$ and $R_{10}$ is then chosen such that $R_{10}/(R_9~||~R_{10}) = \SI{1.3}{\volt}/\SI{5}{\volt} \approx \num{0.26}$.
 The capacitors $C_3$ and $C_4$ are chosen such that $C_3 = \SI{22}{\pico\farad}$ and
 \begin{align}
-\frac{C_4}{C_3} &= \frac{R_3}{R_4~||~R_5}\,,
+\frac{C_4}{C_3} &= \frac{R_3}{R_4~||~R_5}
 \end{align}
 as suggested by the datasheet, and $R_6 = R_7 = R_8$.
-In our lab, we implement a gain $G\approx 50$ ($R_3 = R_5 = \SI{499}{\kilo\ohm}$; $R_4 = R_{6-8} = \SI{10}{\kilo\ohm}$) such that a \SI{5}{\volt} digital-to-analog (DAC) converter at $V_\text{DC}$ can span \SI{0}{\volt} -- \SI{250}{\volt}.
-
-This pseudo-differential configuration ensures that, in the equilibrium given by Eq.~(\ref{Eq:U1Output}), the output of U1 is driven to \SI{0}{\volt}; the resistive divider $R_9$ and $R_{10}$ is then chosen such that $R_{10}/(R_9~||~R_{10}) = \SI{1.3}{\volt}/\SI{5}{\volt} \approx \num{0.26}$.
+In our lab, we implement a gain $G\approx 50$ ($R_3 = R_5 = \SI{499}{\kilo\ohm}$; $R_4 = R_{6-8} = \SI{10}{\kilo\ohm}$) such that a \SI{5}{\volt} digital-to-analog converter (DAC) controlling the node $V_\text{DC}$ can span \SI{250}{\volt} at the output.
 
 The output of the flyback regulator is passed through a four-pole, low-pass RC filter.
-The corner frequency $f_c \approx \SI{3}{\kilo\hertz}$ is chosen to be high enough that a slow ($\approx \SI{10}{\hertz}$) rail-to-rail triangle ramp can be applied at $V_\text{DC}$ (for, e.g., sweeping over a spectroscopy resonance), but low enough that the $\approx \SI{100}{\kilo\hertz}$ switching noise is attenuated.
+The corner frequency $f_c \approx \SI{3}{\kilo\hertz}$ is chosen to be high enough that a slow ($\approx \SI{10}{\hertz}$) rail-to-rail triangle ramp can be applied by the DAC at $V_\text{DC}$ (for, e.g., sweeping over a spectroscopy resonance), but low enough that the $\approx \SI{100}{\kilo\hertz}$ switching noise is substantially attenuated.
 Additional capacitors on both the HV and $\text{GND}_{\text{HV}}$ resistor networks shunt high frequency noise to ground.
-
-Careful attention was paid to the layout...
-
-Notes here about expected, measured bandwidth??
 
@@
 The low-noise stabilization circuit is crucial to the performance of the design, as it is responsible for removing noise at the output of the flyback converter.
-To accomplish this task, a high slew-rate op-amp (Texas Instruments LM7171, \SI[per-mode=symbol]{4100}{\volt\per\micro\second}) drives the galvanically isolated ground node of the flyback converter (see U2 in Fig.~\ref{Fig:PiezoCircuit}).
+To accomplish this, a high slew-rate op-amp (Texas Instruments LM7171, \SI[per-mode=symbol]{4100}{\volt\per\micro\second}) drives the galvanically isolated ground node of the flyback converter (see U2 in Fig.~\ref{Fig:PiezoCircuit}).
 This op-amp enforces the HV output voltage
@@
 \text{V}_\text{HV} &= \left(1 + \frac{R_1}{R_2~||~R_\text{mod}}\right) \text{V}_\text{DC} -
-\left(\frac{R_\text{mod}}{R_1}\right) \text{V}_\text{mod}
+\left(\frac{R_\text{mod}}{R_1}\right) \text{V}_\text{mod}\,.
+\label{Eq:FullTransferFunc}
 \end{align}
-We choose $R_1, R_\text{mod} = \SI{1}{\mega\ohm}$, $R_2 = \SI{20.5}{\kilo\ohm}$ such that the DC gain is $\approx 50$ and the modulation gain is unity.
-Depending on the application, however, other gain configurations would work equally well provided the non-inverting gain of U2 closely matches the gain of the flyback regulator since they derive from the same control voltage.
+We choose $R_1,\,R_\text{mod} = \SI{1}{\mega\ohm}$, $R_2 = \SI{20.5}{\kilo\ohm}$ such that the DC gain is $\approx 50$ and the modulation gain $\text{V}_\text{HV}/\text{V}_\text{mod}$ is unity.
+Depending on the application, other gain configurations would work equally well provided the non-inverting gain of U2 closely matches the gain of the flyback regulator (since they derive from the same control voltage).
 Ultimately, the op-amp U2 sets the operating voltage of the output referenced to true circuit ground, while the flyback converter regulates the high voltage relative to the pseudoground node $\text{GND}_\text{HV}$.
-Because the output of the flyback regulator is galvanically isolated, U2 is free to control the $\text{GND}_\text{HV}$ node at ``low'' voltages, which are transferred directly to the high voltage output.
+Because the output of the flyback regulator is galvanically isolated, U2 is free to control the pseudo-ground node $\text{GND}_\text{HV}$. 
+At low frequencies, this amounts to changing the \SI{0}{\volt} reference for the flyback regulator, while at high frequencies the capacitor $\text{C}_\text{HV}$ provides a low-impedance pathway to directly modulate the HV output.
+Thus, U2 simultaneously acts to servo residual switching noise while providing a DC-coupled, high-bandwidth modulation pathway to the output.
 
-%The low-noise stabilization circuitry was added to remove output ripple and residual switching noise, however it serves a dual purpose as a low-gain, high-bandwidth modulation path to the high-voltage output.
-%It uses a very high slew-rate (\SI{4100}{\volt\per\micro\second}) op-amp, the LM7171, connected to the filtered ground node of the flyback converter.
-%At high frequencies, the output of this op-amp appears directly at the HV node through the capacitor $C_{\text{out}}$.
-%Below the corner set by $C_{\text{out}}$, the output of U2 adjusts the floating ground reference of the flyback converter.
-
-%After the passive filter ladder connecting the DRV2700 flyback converter the output,
-%At high frequencies, this modulation appears directly at the HV node through the capacitors.
-%At quasi-DC frequencies, the flyback regulator adjusts the HV node to keep
-
-The choice of component for resistors $R_1$ and $R_2$ is crucial for the low-noise performance of the system, because this resistive divider is responsible for accurately sensing the high voltage output and noise contributions thus appear directly at the output.
+As a final note, it is worth mentioning that the choice of component for resistors $R_1$ and $R_2$ is crucial for the low-noise performance of the system, because this resistive divider is responsible for accurately sensing the high voltage output and noise contributions thus appear directly at the output.
 Resistors are fundamentally limited by Johnson noise, in which thermal fluctuations contribute to a white noise power spectrum given by $\sqrt{k_B T R}$.
@@
 
-For a detailed noise analysis, see Sec.~\ref{Sec:NoiseAnalysis}.
-
 \subsection{Digital control and auxiliary design features}
@@
 
-The DC setpoint is controlled by a low-noise digital-to-analog (DAC) converter.
-This has several advantages: digital control enhances setpoint repeatability, and makes it easy to interface with a wide variety of control electronics to, eg, implement a slow infinite integrator [expand on this?].
-A wide array of high-resolution DACs are available with very good noise characteristics.
-We initially chose to use an AD5563R, but found that our performance was ultimately limited by $1/f$ noise in the DAC itself.
-The final design uses an XXX, with XXX external reference, such that the noise contribution from the DAC is comparable to the noise contribution from the LM7171 (see Sec.~\ref{Sec:NoiseAnalysis}).
-
-The DAC is controlled by an integrated microcontroller, which also interfaces with the frontpanel control switches, encoders, and LCD display.
-The microcontroller is also attached via the backplane [talk about eurocard rack somewhere?] to a secondary microcontroller which can be addressed over TCP/IP.
-This vastly expands the conceivable control scenarios; for example, in our lab we implement a slow-feedback lock of two ECDL repumping lasers to a wavemeter.
-LabView code on the computer attached to the wavemeter computes an error signal and corrective control voltage, which can then be passed over our internal network to the piezo driver to correct for frequency drift in the laser.
+The DC setpoint is controlled by a low-noise digital-to-analog converter (DAC).
+This has several advantages: digital control enhances setpoint repeatability, and makes it easy to integrate with a wide variety of computerized control electronics.
+The DAC itself is controlled by an onboard microcontroller, which also interacts with the frontpanel control switches, encoders, and LCD display.
+The entire circuit is designed to fit in a standard Eurocard rack, which supplies power at $\pm\SI{15}{\volt}$ and contains a backplane with analog lines to communicate with other modules in the rack (e.g., to implement a current feed-forward for laser diodes, see description below).
+The backplane also contains a secondary microcontroller, which can be addressed over TCP/IP.
+This vastly expands the conceivable control scenarios. For example, in our lab we implement a slow-feedback lock of two ECDL repumping lasers to a wavemeter.
+LabView code on the computer attached to the wavemeter computes an error signal and corrective control voltage, which can then be passed over our internal network to the piezo driver to correct for frequency drifts in the laser.
 Other similar schemes are possible, enabling complete remote control of the laser electronics.
 
-Control via the frontpanel is provided by a rotary encoder/push button, and a single on/off switch.
-The rotary encoder/push button switch allows interaction with a user-definable menu system.
-For example, this allows the user to quickly switch the piezo driver into ``ramp'' mode to scan a laser over some resonance feature.
+In addition to software-defined control via the backplane, frontpanel control is provided by a rotary encoder/push button, and a single SPDT switch.
+The encoder/push button provides menu navigation, and the switch toggles between DC and scanning operation.
+However, other user interfaces can easily be designed to work with the existing hardware.
 
-In addition to the digital setpoint control, a voltage proportional to the high voltage output is connected to a GPIO line on the backplane.
-This is fed to a low-noise current controller (based on the design in~\ref{DurfeeFIX}) to implement feed-forward (cite?).
+A voltage proportional to the output (sensed at node XX) is buffered and connected to a monitor BNC on the frontpanel and a GPIO line on the backplane.
+The GPIO line is fed to a low-noise current controller (based on the design in~\ref{DurfeeFIX}) to implement feed-forward.
 An optional analog voltage from the backplane can also be summed with the modulation voltage supplied via BNC on the front panel to generate $V_{\text{mod}}$.
 This may be useful, eg, with servo controllers that reside in the same rack as the other control electronics.
+For a detailed description of the wiring, see GITHUB.
 
-Finally, the high voltage output is interlocked with a signal on the back plane (which can optionally be over-ridden by placing a jumper onboard); this allows easy integration into existing laboratory interlock schemes.
+Finally, the high voltage output is interlocked with a signal on the back plane (which can optionally be over-ridden by placing a jumper); this allows easy integration into existing laboratory interlock schemes, if desired.
 
@@
 \end{figure}
+
 \begin{figure}[t]
+\subfloat{
 \includegraphics[width=\columnwidth]{calc/NoiseContrib.pdf}
+}
+
+\subfloat{
+%\begin{table}
+\centering
+\begin{tabular*}{0.9\columnwidth}{@{\extracolsep{\fill}} lc}
+\hline\hline
+\rule{0pt}{2.5ex}\multirow{2}{*}{Noise source} & RMS Voltage                        \\
+& (\SI{1}{\hertz}~--~\SI{100}{\kilo\hertz})\rule[-1ex]{0pt}{1ex} \\
+\hline
+\rule{0pt}{2ex}$e_n$ (op-amp)  & \SI{52}{\micro\volt}      \\
+$i_n$ (op-amp)  & \SI{32}{\micro\volt}      \\
+DAC             & \SI{75}{\micro\volt}       \\
+Johnson-Nyquist & \SI{31}{\micro\volt}        \\ 
+\hline
+\rule{0pt}{2ex}\textbf{total (calculated)} & \SI{101}{\micro\volt}  \\
+\hline\hline
+\end{tabular*}
+%\end{table}
+}
 \caption{Noise Contributions (color online).
 Plotted are the noise contributions from each source in our model -- op-amp current noise (dashed orange) and voltage noise (dotted blue); Johnson noise (dash-dotted green), DAC noise (long dashed red), and total noise (solid purple).
-Power spectral density is referred to the high voltage output.\label{Fig:NoisePlot}}
+Power spectral density is referred to the high voltage output.
+The table shows the integrated RMS noise from \SI{1}{\hertz}~--~\SI{100}{\kilo\hertz} due to each noise source.
+The total noise is summed in quadrature.\label{Fig:NoisePlot}}
 \end{figure}
@@
 We analyze the noise performance of the circuit according to the model shown in Fig.~\ref{Fig:NoiseModel}, where noise spectral densities are calculated at the node HV.
-A summary of each noise contribution (op-amp, DAC, Johnson-Nyquist, external modulation input) is shown in Table~\ref{Tab:noise}, along with the cumulative root-mean-square (RMS) nose estimates in different frequency bands.
+A summary of each noise contribution (op-amp, DAC, Johnson-Nyquist, external modulation input) is shown in Fig.~\ref{Fig:NoisePlot}, along with the cumulative root-mean-square (RMS) nose estimates in different frequency bands.
 % We also discuss, given our choice of op-amp, the noise rejection ratio from the DRV2700 flyback regulator.
@@
 
-The op-amp noise is parametrized by two noise contributions -- $e_n$, the input voltage noise power spectral density (PSD), and $i_n$, the input current noise PSD.
+The op-amp noise is parametrized by two noise contributions: $e_n$, the input voltage noise power spectral density (PSD), and $i_n$, the input current noise PSD.
 For the LM7171, $e_n = \SI[per-mode=symbol]{14}{\nano\volt\per\sqrthz}$ and $i_n = \SI[per-mode=symbol]{1.5}{\pico\ampere\per\sqrthz}$ at $\SI{10}{\kilo\hertz}$, with a $1/f$ noise character below this frequency~\cite{LM7171Datasheet}.
@@
 For our circuit, this is the dominant noise contribution.
-Each noise source is shown and tabulated in Table~\ref{Tab:noise}.
+Each noise source is shown and tabulated in Fig.~\ref{Fig:NoisePlot}.
 
-\begin{table}
-\caption{Various noise contributions. -- should we just tabulate RMS?}
-\label{Tab:noise}
-\begin{ruledtabular}
-\centering
-\begin{tabular}{lcc}
- \multirow{2}{*}{Noise source} & \multicolumn{2}{c}{Voltage PSD (\si[per-mode=symbol]{\nano\volt\per\sqrthz})} \\ \cline{2-3}
-\rule{0pt}{3ex} & (input-referred) & (output-referred) \\
-\hline
-$e_n$ (op-amp) & \SI{14} (white); \SI{30} ($1/f$)  & \\
-$i_n$ (op-amp) &    & \\
-DAC &    & \\
-Johnson-Nyquist & & \\ \hline
-\textbf{total} & &
-\end{tabular}
-\end{ruledtabular}
-\end{table}
+\begin{figure}[h]
+\subfloat{
+%\includegraphics[clip,width=\columnwidth]{fig/TimeDomain.pdf}
+}
+
+\subfloat{
+\includegraphics[clip,width=\columnwidth]{fig/LongTimeDomain.pdf}
+}
+\caption{Time-domain traces of the high voltage output (\SI{100}{\volt}).
+\textit{Top:} short-time scatterplot  (AC coupled).
+Points are colored based on the Gaussian spread in acquired voltages, thus indicating the RMS width of the trace.
+\textit{Bottom:} long-term trace, measured on a Keithly~2000 digital multimeter.
+A~\SI{100}{\volt} DC offset is subtracted from the plotted values.
+The top trace shows the lab temperature during the same time period.\label{Fig:TimeDomain}}
+\end{figure}
 
@@
 \label{Sec:Results}
-Noise analysis, bandwidth, (DC) stability, etc.
+Here, we show the performance of the high-voltage piezo driver.
+In Fig.~\ref{Fig:PSD}, you can see the noise power spectral density at several different output voltages.
+This trace was taken on an SR780 spectrum analyzer, with the piezo output coupled through a \SI{0.5}{\hertz} high-pass filter. 
+The RMS noise ($\SI{1}{\hertz} - \SI{100}{\kilo\hertz}$) is \SI{80}{\micro\volt} at \SI{100}{\volt}.
+\begin{figure}[h]
+\includegraphics[width=\columnwidth]{fig/VoltagePSD.pdf}
+\caption{Voltage power spectral density at various output voltages.
+The integrated RMS voltage noise ($\SI{1}{\hertz} - \SI{100}{\kilo\hertz}$) is \SI{80}{\micro\volt} for the \SI{100}{\volt} output.\label{Fig:PSD}}
+\end{figure}
 
-We characterized the performance of the high-voltage piezo driver with a few different metrics.
-In Fig.~XX, you can see the noise power spectral density.
-This trace was taken on an SRSXXX spectrum analyzer, AC coupled to the high-voltage output with a \SI{0.5}{\hertz} high-pass filter circuit shown in Fig.~XX(b).
+\begin{figure}[h]
+\includegraphics[width=\columnwidth]{fig/PiezoModulationTransfer.pdf}
+\caption{Modulation input transfer function.
+Green trace shows the response with a ThorLabs piezoelectric actuator {(PN~AE0505D08F)}; the mechanical resonances above $\approx\SI{50}{\kilo\hertz}$ are clearly visible.
+The red trace shows the response under a \SI{1}{\micro\farad} purely capacitive load.
+Loaded response bandwidth is $\approx\SI{100}{\kilo\hertz}$, while unloaded the bandwidth is $\approx\SI{1}{\mega\hertz}$.\label{Fig:TransferFunc}}
+\end{figure}
 

### 2016-06-13 piezo.tex
first draft done

@@
 % That way, you always have this original template file to use.
-%\documentclass[aip,rsi,reprint]{revtex4-1} % for checking your page length
+\documentclass[aip,rsi,reprint]{revtex4-1} % for checking your page length
 %\documentclass[aip,rsi,reprint,graphicx,draft]{revtex4-1} % for checking your page length
-\documentclass[aip,rsi,preprint,graphicx]{revtex4-1} % for review purposes
+%\documentclass[aip,rsi,preprint,graphicx]{revtex4-1} % for review purposes
+%\documentclass{aastex}
+
+%\usepackage[warnundef]{jabbrv}
 
@@
 
+% \usepackage{aastex}
+%\usepackage{natbib}
+\usepackage{hyperref}
+
 %% Work with illustrator *.ai files...
@@
 \newcommand{\epar}{~||~} % add impedances in parallel
+\newcommand{\CC}{{C\nolinebreak[4]\hspace{-.05em}\raisebox{.4ex}{\tiny\bf ++}}~}
+
+%% ugh, should find better solution to this. ADS returns \prb, not recognized by revtex style...
+\newcommand{\prb}{Phys. Rev. B}
 
@@
 Many instrumentation applications in the modern laboratory require agile, low-noise voltage sources capable of supplying hundreds of volts or more.
-For example, piezo-actuated mirrors and diffraction gratings play an important role in many atomic physics experiments (used, e.g., in scanning Fabry-Per{\`o}t cavities and extended-cavity diode lasers).
-Avalanche photodiodes require a low-noise reverse bias of a few hundred volts or more (cite paper Alessandro/Prasoon are using?).
-Other applications...? biophysics? medical devices?
+For example, piezo-actuated mirrors and diffraction gratings play an important role in atomic physics experiments (used, e.g., in scanning Fabry-Per{\`o}t cavities and extended-cavity diode lasers), while avalanche photodiodes and photomultiplier tubes require large bias voltages for proper operation.
+In the realm of biophysics, electrokinetic separation methods such as free-flow or capillary electrophoresis require large electric field gradients, and the recent push to develop lab-on-a-chip devices could benefit from miniaturized high voltage sources~\cite{Kohlheyer2008a}.
+(ion traps?
+charge multiplier tubes?)
 
-Often, these applications are operated in a closed feedback loop, where small voltage changes on top of a large DC voltage are necessary to stabilize the output of a particular system.
-For example, extended-cavity diode lasers adjust their lasing frequency by changing the angle of a piezo-actuated diffraction grating that supplies optical feedback to the diode.
-High-voltage piezoelectric drivers typically provide a ``modulation input'' for  such closed-loop applications, where the input voltage is either DC coupled and gained such that the input range spans the entire output range of the driver, or AC coupled directly to the output.
-While this may have certain advantages, many applications would benefit from an architecture that provides a unity gain, DC-coupled feedback path to the high voltage output -- such a device would make closed-loop piezoelectric systems less susceptible to noise contributions from the servo controller.
-Indeed, in our laboratory, we often find this to be the limiting factor in the stability of our laser frequency locks.
+Often, laboratory devices are operated in a closed feedback loop, where small voltage changes on top of a large DC voltage are necessary to stabilize the output of a particular system.
+For example, extended-cavity diode lasers can adjust their lasing frequency by changing the angle of a piezo-actuated diffraction grating that supplies optical feedback to the diode.
+Commercially available piezoelectric drivers typically provide a modulation input for  such closed-loop applications, but the input voltage is either AC coupled to the output or gained such that it spans the entire voltage range of the device.
+While this has certain advantages, many applications would benefit from an architecture that provides a unity gain, DC-coupled feedback path to the high voltage output. 
+Such a device could make closed-loop systems less susceptible to noise contributions from the servo controller, which we often find in our laboratory to be the limiting factor in laser lock stability.
 
-%Here, we present an architecture which combines the best of both worlds: a high-voltage piezoelectric driver with excellent noise characteristics that can be powered from a standard low-current, low-voltage supply.
-%The DC operating point is controlled digitally, and an analog input provides a DC-coupled, unity-gain feedback path ($\pm\SI{10}{\volt}$) to the output.
-%The following design is versatile and easy to deploy throughout the lab in a variety of high-voltage applications.
+Traditionally, instrumentation electronics capable of supplying high voltages fall under one of two architectural umbrellas: DC-DC switching converters, and linear-type amplifiers.
+While DC-DC converters are efficient and can work at very high voltages, they suffer from switching noise and limited control bandwidths.
+Linear-type devices are typically constructed from a high-voltage operational amplifier (op-amp), powered either from a high voltage linear regulator or more typically from a secondary switching converter.
+While the op-amp provides \SI{100}{\decibel} or more of power-supply noise rejection, high-voltage op-amps require substantially more power than an equivalent switching circuit and are more cumbersome to deploy in the laboratory.
+
+Here, we present a hybrid architecture: the high voltage is generated by a galvanically isolated DC-DC converter (described in Sec.~\ref{Sec:DRV2700}), while a low-noise, high slew-rate op-amp removes noise at the output by modulating the {OUT--} node of the switching converter (see Sec.~\ref{Sec:LowNoiseStabilization}).
+The op-amp additionally provides a low-gain, high-bandwidth modulation input for closed-loop feedback applications.
+This architecture is able to achieve extremely low noise performance, draws very little current, and fits comfortably onto a small-footprint PCB.
+Complete design files, including the schematic, bill of materials, and board layout, can be found on Github.~\footnote{\protect\url{https://github.com/JQIamo/hv-piezo-driver}}
+% Mention other features?
+
+%The high voltage setpoint is digitally controlled, and can be swept over \SI{200}{\volt} at \approx\SI{10}{\hertz}.
 
@@
 A fast, very high slew-rate op-amp senses the output voltage across $R_1$ and $R_2$, and servos it by modulating the node at ``HV floating gnd''.
-The $V_{\text{DC}}$ gain is set by $\left(1+R_1/R_2\right)$, while the modulation gain is set by $-R_{\text{mod}}/R_1$.
-The capacitor linking the floating ground node to the output allows the op-amp to remove residual switching noise and stabilize the DC output according to the transfer function given in Eq.~(\ref{Eq:PiezoTransfer}).
--- Add back in second set of shunt caps!\label{Fig:PiezoCircuit}}
+The DC control signal for this op-amp is supplied by a digital-to-analog (DAC) converter, which is passed through a switchable low-pass filter.
+This allows for very heavy filtering of the DAC $1/f$ noise during steady-state operation, but the corner frequency can be increased if the output needs to be scanned more quickly.
+The $\text{V}_{\text{DC}}$ gain is set by $\left(1+R_1/R_2\right)$, while the modulation gain is set by $-R_{\text{mod}}/R_1$.
+The capacitor linking the floating ground node to the output allows the op-amp to remove residual switching noise and stabilize the DC output according to the transfer function given in Eq.~(\ref{Eq:FullTransferFunc}).
+\label{Fig:PiezoCircuit}}
 \end{figure*}
 
-Traditionally, laboratory electronics capable of supplying high voltages fall under one of two architectural umbrellas: DC-DC switching converters, and ``linear'' amplifiers.
-DC-DC converters are efficient and can work at very high voltages, but suffer from switching noise and limited control bandwidths.
-Linear-type devices are typically constructed from a high-voltage operational amplifier (op-amp), powered either from a high voltage linear regulator or more typically from a secondary switching converter.
-While the op-amp provides \SI{100}{\decibel} or more of power-supply noise rejection, high-voltage op-amps requires substantially more power than an equivalent switching circuit and are more cumbersome to deploy in the laboratory.
-
-Here, we present a hybrid architecture (see Fig.~\ref{Fig:PiezoCircuit} for details).
-The high voltage is generated by a galvanically isolated switching converter (described in Sec.~\ref{Sec:DRV2700}), while a low-noise, high slew-rate op-amp removes the switching noise by modulating the \textbf{OUT--} node of the DC-DC converter (Sec.~\ref{Sec:LowNoiseStabilization}).
-This op-amp additionally provides a low-gain, high-bandwidth modulation input for closed-loop feedback applications.
-
-The design principles discussed below show how researchers might leverage the versatility of galvanically isolated switching regulators in a low-noise laboratory environment; straightforward modifications to the schematic make it possible to tailor the high voltage driver to a specific application.
-The entire electronics package fits comfortably into a 12HP eurocard rack module, and draws less than \SI{50}{\milli\ampere} at \SI{15}{\volt} [get real numbers].
-The full schematic, including Gerbers, a bill of materials, and layout design files, can be found on GitHub~\footnote{\protect\url{https://github.com/JQIamo/piezo-compact-high-voltage-driver}}.
+The design principles discussed below show how researchers might leverage the versatility of galvanically isolated switching regulators in a low-noise laboratory environment. 
+Our design targets a \SI{250}{\volt} output, but straightforward modifications to the schematic make it possible to tailor the gain and output range to a specific application.
+The entire electronics package fits comfortably into a 12HP eurocard rack module (with the high voltage section taking only a fraction of the PCB), and draws less than \SI{150}{\milli\ampere} at \SI{15}{\volt}.
+%The full schematic, including Gerbers, a bill of materials, and layout design files, can be found on GitHub.~\footnote{\protect\url{https://github.com/JQIamo/hv-piezo-driver}}
 
@@
 Internally, the DRV2700 boost controller tries to drive the FB node to \SI{1.3}{\volt}.
-The op-amp U1 senses the voltage at node HV and $\text{GND}_\text{HV}$, and adjusts its output such that
+The op-amp U1 senses the voltage at nodes HV and $\text{GND}_\text{HV}$, and adjusts its output such that
 \begin{align}
@@
 \begin{align}
-\frac{C_4}{C_3} &= \frac{R_3}{R_4~||~R_5}
+\frac{C_4}{C_3} &= \frac{R_3}{R_4~||~R_7}
 \end{align}
 as suggested by the datasheet, and $R_6 = R_7 = R_8$.
-In our lab, we implement a gain $G\approx 50$ ($R_3 = R_5 = \SI{499}{\kilo\ohm}$; $R_4 = R_{6-8} = \SI{10}{\kilo\ohm}$) such that a \SI{5}{\volt} digital-to-analog converter (DAC) controlling the node $V_\text{DC}$ can span \SI{250}{\volt} at the output.
+In our lab, we implement a gain $G\approx 50$ ($R_3 = R_5 = \SI{499}{\kilo\ohm}$; $R_4 = R_{6-8} = \SI{10}{\kilo\ohm}$) such that a \SI{5}{\volt} digital-to-analog converter (DAC) controlling the node $\text{V}_\text{DC}$ can span \SI{250}{\volt} at the output.
 
 The output of the flyback regulator is passed through a four-pole, low-pass RC filter.
-The corner frequency $f_c \approx \SI{3}{\kilo\hertz}$ is chosen to be high enough that a slow ($\approx \SI{10}{\hertz}$) rail-to-rail triangle ramp can be applied by the DAC at $V_\text{DC}$ (for, e.g., sweeping over a spectroscopy resonance), but low enough that the $\approx \SI{100}{\kilo\hertz}$ switching noise is substantially attenuated.
+The corner frequency $f_c \approx \SI{3}{\kilo\hertz}$ is chosen to be high enough that a slow ($\approx \SI{10}{\hertz}$) rail-to-rail triangle ramp can be applied by the DAC at $\text{V}_\text{DC}$ (for, e.g., sweeping over a spectroscopy resonance), but low enough that the $\approx \SI{100}{\kilo\hertz}$ switching noise is substantially attenuated.
 Additional capacitors on both the HV and $\text{GND}_{\text{HV}}$ resistor networks shunt high frequency noise to ground.
@@
 Depending on the application, other gain configurations would work equally well provided the non-inverting gain of U2 closely matches the gain of the flyback regulator (since they derive from the same control voltage).
-Ultimately, the op-amp U2 sets the operating voltage of the output referenced to true circuit ground, while the flyback converter regulates the high voltage relative to the pseudoground node $\text{GND}_\text{HV}$.
-Because the output of the flyback regulator is galvanically isolated, U2 is free to control the pseudo-ground node $\text{GND}_\text{HV}$. 
-At low frequencies, this amounts to changing the \SI{0}{\volt} reference for the flyback regulator, while at high frequencies the capacitor $\text{C}_\text{HV}$ provides a low-impedance pathway to directly modulate the HV output.
-Thus, U2 simultaneously acts to servo residual switching noise while providing a DC-coupled, high-bandwidth modulation pathway to the output.
+Ultimately, the op-amp U2 sets the operating voltage of the output (referenced to true circuit ground) while the flyback converter regulates the high voltage relative to the pseudoground node $\text{GND}_\text{HV}$.
+Because the output of the flyback regulator is galvanically isolated, U2 is free to control $\text{GND}_\text{HV}$. 
+At low frequencies, this amounts to changing the ``zero-volt'' reference for the flyback regulator, while at high frequencies the capacitor $\text{C}_\text{HV}$ provides a low-impedance pathway to the HV output.
+In this manner, U2 is simultaneously able to servo residual switching noise and provide a DC-coupled, high-bandwidth modulation of the output.
 
-As a final note, it is worth mentioning that the choice of component for resistors $R_1$ and $R_2$ is crucial for the low-noise performance of the system, because this resistive divider is responsible for accurately sensing the high voltage output and noise contributions thus appear directly at the output.
-Resistors are fundamentally limited by Johnson noise, in which thermal fluctuations contribute to a white noise power spectrum given by $\sqrt{k_B T R}$.
+As a final note, it is worth mentioning that the choice of component for resistors $R_1$ and $R_2$ is crucial for the low-noise performance of the system, because this resistive divider is responsible for accurately sensing the voltage $\text{V}_\text{HV}$; noise introduced by these resistors cannot be corrected by the op-amp, and thus appears directly at the output.
+Resistors are fundamentally limited by Johnson noise, in which thermal fluctuations contribute to a white noise power spectrum given by $\sqrt{k_B T R}$.(Cite art of electronics?)\cite{Horowitz1989a}
 However, resistors also exhibit $1/f$ current noise caused by equilibrium fluctuations of the resistance~\cite{Clarke1974a,Voss1976a}.
 The magnitude of this ``excess noise'' is highly dependent on the resistor composition, and varies from manufacturer to manufacturer.
-Reference~\cite{Seifert2009a} characterized $1/f$ noise in a variety of resistors, and found that the Vishay TNPW \SI{0.1}{\percent}-series resistors showed a noise spectrum almost consistent with Johnson noise down to \SI{1}{\hertz}.
+Seifert, et.
+al.~\cite{Seifert2009a} characterized $1/f$ noise in a variety of resistors, and found that the Vishay TNPW \SI{0.1}{\percent}-series resistors showed a noise spectrum almost consistent with Johnson noise down to \SI{1}{\hertz}.
 A previous iteration of this design used Panasonic ERJ-8ENF resistors (1206, \SI{1}{\percent}), and we noticed substantial low-frequency noise correlated with varying strain on the PCB.
 This is consistent with the findings in~\cite{Seifert2009a}, which showed this Panasonic series to exhibit voltage noise two orders of magnitude larger than the TNPW series at \SI{1}{\hertz}.
+The final board design utilizes three TNPW \SI{0.1}{\percent} 0603 resistors in series for both R1 and R2.
 
@@
 The DAC itself is controlled by an onboard microcontroller, which also interacts with the frontpanel control switches, encoders, and LCD display.
-The entire circuit is designed to fit in a standard Eurocard rack, which supplies power at $\pm\SI{15}{\volt}$ and contains a backplane with analog lines to communicate with other modules in the rack (e.g., to implement a current feed-forward for laser diodes, see description below).
+The entire circuit is designed to fit in a standard Eurocard rack, which supplies power at $\pm\SI{15}{\volt}$ and contains a backplane with analog lines to communicate with other modules (e.g., to implement a current feed-forward for laser diodes, see description below).
 The backplane also contains a secondary microcontroller, which can be addressed over TCP/IP.
@@
 In addition to software-defined control via the backplane, frontpanel control is provided by a rotary encoder/push button, and a single SPDT switch.
-The encoder/push button provides menu navigation, and the switch toggles between DC and scanning operation.
+The encoder/push button provide menu navigation, and the switch toggles between DC and scanning operation.
 However, other user interfaces can easily be designed to work with the existing hardware.
+Arduino-based code written in \CC defines the entire software interaction, and can be modified depending on the needs of the researcher.
 
-A voltage proportional to the output (sensed at node XX) is buffered and connected to a monitor BNC on the frontpanel and a GPIO line on the backplane.
-The GPIO line is fed to a low-noise current controller (based on the design in~\ref{DurfeeFIX}) to implement feed-forward.
-An optional analog voltage from the backplane can also be summed with the modulation voltage supplied via BNC on the front panel to generate $V_{\text{mod}}$.
-This may be useful, eg, with servo controllers that reside in the same rack as the other control electronics.
-For a detailed description of the wiring, see GITHUB.
+A voltage proportional to the output (sensed at the inverting node of U2) is buffered and connected to a monitor BNC on the frontpanel and a GPIO line on the backplane.
+In our lab, this GPIO line is fed to a low-noise current controller (based on the design in~\cite{Erickson2008a}) to implement a current feed-forward.
+An optional analog voltage from the backplane can also be summed with the modulation voltage supplied via BNC on the frontpanel to generate $\text{V}_{\text{mod}}$.
+This may be useful, e.g., with servo controllers that reside in the same rack as the other control electronics.
 
 Finally, the high voltage output is interlocked with a signal on the back plane (which can optionally be over-ridden by placing a jumper); this allows easy integration into existing laboratory interlock schemes, if desired.
+For more details, see the design files and documentation on Github~\cite{DesignFiles}.
 
@@
 \includegraphics[width=\columnwidth]{fig/NoiseModel.ai}
-\caption{Noise model. \label{Fig:NoiseModel}}
+\caption{Noise model (see text).
+In reality, the capacitor labeled $Z_\text{LP}$ is comprised of a \SI{47}{\nano\farad} capacitor in parallel with a switchable \SI{10}{\micro\farad} capacitor, such that the corner frequency of the filter can be changed depending on the mode of operation.
+The $\text{R}_\text{on}$ resistance of the switch introduces a zero in the transfer function at $\approx\SI{23}{\kilo\hertz}$, which has negligible effect on the computed RMS noise.
+\label{Fig:NoiseModel}}
 \end{figure}
@@
 \subfloat{
-\includegraphics[width=\columnwidth]{calc/NoiseContrib.pdf}
+\includegraphics[width=\columnwidth]{fig/NoiseContrib.pdf}
 }
@@
 \subfloat{
-%\begin{table}
 \centering
-\begin{tabular*}{0.9\columnwidth}{@{\extracolsep{\fill}} lc}
+\begin{tabular*}{0.95\columnwidth}{@{\extracolsep{\fill}} lcc}
 \hline\hline
-\rule{0pt}{2.5ex}\multirow{2}{*}{Noise source} & RMS Voltage                        \\
-& (\SI{1}{\hertz}~--~\SI{100}{\kilo\hertz})\rule[-1ex]{0pt}{1ex} \\
+\rule{0pt}{2.5ex}\multirow{2}{*}{Noise source} & RMS Voltage & RMS Voltage \\
+& (\SI{1}{\hertz}~--~\SI{10}{\hertz})\rule[-1ex]{0pt}{1ex} & (\SI{10}{\hertz}~--~\SI{100}{\kilo\hertz})\rule[-1ex]{0pt}{1ex} \\
 \hline
-\rule{0pt}{2ex}$e_n$ (op-amp)  & \SI{52}{\micro\volt}      \\
-$i_n$ (op-amp)  & \SI{32}{\micro\volt}      \\
-DAC             & \SI{75}{\micro\volt}       \\
-Johnson-Nyquist & \SI{31}{\micro\volt}        \\ 
+\rule{0pt}{2ex}$e_n$ (op-amp)  & \SI{26}{\micro\volt} & \SI{27}{\micro\volt}      \\
+$i_n$ (op-amp)  &            \SI{49}{\micro\volt}     & \SI{59}{\micro\volt}      \\
+DAC             &             \SI{22}{\micro\volt}    & \SI{7}{\micro\volt}       \\
+Johnson-Nyquist &             \SI{3}{\micro\volt}    & \SI{31}{\micro\volt}        \\ 
 \hline
-\rule{0pt}{2ex}\textbf{total (calculated)} & \SI{101}{\micro\volt}  \\
+\rule{0pt}{2ex}\textbf{total (calculated)} & \SI{60}{\micro\volt} & \SI{73}{\micro\volt}  \\
 \hline\hline
 \end{tabular*}
-%\end{table}
 }
 \caption{Noise Contributions (color online).
-Plotted are the noise contributions from each source in our model -- op-amp current noise (dashed orange) and voltage noise (dotted blue); Johnson noise (dash-dotted green), DAC noise (long dashed red), and total noise (solid purple).
-Power spectral density is referred to the high voltage output.
-The table shows the integrated RMS noise from \SI{1}{\hertz}~--~\SI{100}{\kilo\hertz} due to each noise source.
-The total noise is summed in quadrature.\label{Fig:NoisePlot}}
+Plotted are the noise contributions from each source in our model, along with the total calculated noise.
+Power spectral density is referred to the high voltage output, and the table shows the integrated RMS noise due to each noise source in different frequency bands.
+The total RMS noise (summed in quadrature) over the entire \SI{1}{\hertz}~--~\SI{100}{\kilo\hertz} range is calculated to be \SI{94}{\micro\volt}.
+\label{Fig:NoisePlot}}
 \end{figure}
 
-We analyze the noise performance of the circuit according to the model shown in Fig.~\ref{Fig:NoiseModel}, where noise spectral densities are calculated at the node HV.
+We analyze the noise performance of the circuit according to the model shown in Fig.~\ref{Fig:NoiseModel}, where noise spectral densities are calculated at the node $\text{V}_\text{HV}$.
 A summary of each noise contribution (op-amp, DAC, Johnson-Nyquist, external modulation input) is shown in Fig.~\ref{Fig:NoisePlot}, along with the cumulative root-mean-square (RMS) nose estimates in different frequency bands.
 % We also discuss, given our choice of op-amp, the noise rejection ratio from the DRV2700 flyback regulator.
-% -- not sure about how to do this... could just report the measured value:
+% -- not sure about how to do this... could just report the measured value.
 
@@
 where we've defined the equivalent impedances $Z_1 = R_1/(1+R_1 C_1 s)$ and $Z_{\text{mod}} = R_{\text{mod}}/(1+R_{\text{mod}} C_{\text{mod}} s)$, and $s = i\omega$ is the frequency in the Laplace domain.
-By design, we've chosen $Z_1 \equiv Z_{\text{mod}}$ such that the signal gain from the node $V_{\text{mod}}$ is unity.
+By design, we've chosen $Z_1 \equiv Z_{\text{mod}}$ such that the signal gain from the node $\text{V}_{\text{mod}}$ is unity.
 This reduces Eq.~(\ref{Eq:NG}) to
@@
 We now calculate the noise contribution of the DAC.
-The noise signal gain from the node $V_{\text{DC}}$ is given by
+The noise signal gain from the node $\text{V}_{\text{DC}}$ is given by
 \begin{align}
@@
 \label{Eq:Gdc}
-G_{\text{DC}} &= \left(\frac{1}{1+sR_{\text{LP}}C_{\text{LP}}}\right)\left(1+\frac{Z_1}{R_2\epar Z_{\text{mod}}}\right) \\
-&= \left(\frac{1}{1+sR_{\text{LP}}C_{\text{LP}}}\right)NG(s)
+G_{\text{DC}} &= \left(\frac{Z_\text{LP}}{R_\text{LP} + Z_\text{LP}}\right)\left(1+\frac{Z_1}{R_2\epar Z_{\text{mod}}}\right) \\
+&= \left(\frac{Z_\text{LP}}{R_\text{LP} + Z_\text{LP}}\right)NG(s)\,,
 \end{split}
 \end{align}
-Thus, the DAC voltage noise contribution is just $e_{n,\text{DAC}} = G_{\text{DC}} v_{n,\text{DAC}}$.
-The AD5663 has a white noise floor of \SI[per-mode=symbol]{100}{\nano\volt\per\sqrthz} (\SI{1}{\kilo\hertz} corner frequency).
-For our circuit, this is the dominant noise contribution.
-Each noise source is shown and tabulated in Fig.~\ref{Fig:NoisePlot}.
+where the first term represents the contribution to the transfer function from the switchable low-pass filter (discussed above).
+The DAC voltage noise contribution is then simply $e_{n,\text{DAC}} = G_{\text{DC}} v_{n,\text{DAC}}$. 
+The DAC used in our design (Analog devices, AD5663R) has a white noise floor of \SI[per-mode=symbol]{100}{\nano\volt\per\sqrthz} with an $\approx\SI{1}{\kilo\hertz}$ corner frequency.
+Without the addition of the low-pass filter after $\text{V}_\text{DC}$, this DAC would dominate both the low- and high-frequency noise performance of the circuit.
+However, we are instead dominated by Johnson noise at intermediate to high frequencies, and the op-amp's intrinsic current noise at lower frequencies.
+Both of these contributions could potentially be suppressed by using lower resistances $R_1, R_\text{mod}$, however one must be careful about power and current limitations when dealing with such high voltages.
+Each noise source is tabulated and plotted in Fig.~\ref{Fig:NoisePlot}.
+
+\section{Results}
+\label{Sec:Results}
+Here, we show the measured performance of the high-voltage piezo driver.
+In Fig.~\ref{Fig:PSD}, we plot the noise power spectral density measured at several different output voltages.
+These traces were taken on an SR780 spectrum analyzer, with the piezo output coupled through a \SI{0.5}{\hertz} high-pass filter. 
+At \SI{100}{\volt}, the integrated noise ($\SI{1}{\hertz} - \SI{100}{\kilo\hertz}$) was measured to be $\SI{80}{\micro\volt}_\text{RMS}$ ($\SI{138}{\micro\volt}_\text{RMS}$, $\SI{101}{\micro\volt}_\text{RMS}$ for \SI{50}{\volt}, \SI{200}{\volt} outputs).
+This matches well with the expected total RMS noise calculated in Section~\ref{Sec:NoiseAnalysis}.
+
+\begin{figure}[hb]
+\includegraphics[width=\columnwidth]{fig/VoltagePSD.pdf}
+\caption{Voltage power spectral density at various output voltages.
+The integrated RMS voltage noise ($\SI{1}{\hertz} - \SI{100}{\kilo\hertz}$) is $\{138, 80, 101\}~\si{\micro\volt}$ measured at  $\{50, 100, 200\}~\si{\volt}$.
+\label{Fig:PSD}}
+\end{figure}
+
+Figure~\ref{Fig:TimeDomain} shows the performance at both short- and long-time scales.
+At long times, voltage fluctuations on the order of a few \si{\milli\volt} can be observed.
+This is due generically to $1/f$ noise, but also correlates with the external temperature.
+A cross-correlation between measured temperature and output voltage fluctuation yields an effective temperature coefficient of \SI[per-mode=symbol]{-24}{ppm\per\celsius} at \SI{100}{\volt}.
+The short-term trace was taken on a PicoScope~5442B (ac-coupled, \SI{100}{\volt} output).
+Points are colored based on their normally distributed statistical probability, and thus give a visual estimation of the RMS width.
 
 \begin{figure}[h]
-\subfloat{
-%\includegraphics[clip,width=\columnwidth]{fig/TimeDomain.pdf}
-}
-
-\subfloat{
-\includegraphics[clip,width=\columnwidth]{fig/LongTimeDomain.pdf}
-}
+\includegraphics[width=\columnwidth]{fig/TimeDomain.pdf}
 \caption{Time-domain traces of the high voltage output (\SI{100}{\volt}).
-\textit{Top:} short-time scatterplot  (AC coupled).
+Top: short-time scatterplot  (AC coupled).
 Points are colored based on the Gaussian spread in acquired voltages, thus indicating the RMS width of the trace.
-\textit{Bottom:} long-term trace, measured on a Keithly~2000 digital multimeter.
+Bottom: long-term trace, measured on a Keithly~2010 digital multimeter.
 A~\SI{100}{\volt} DC offset is subtracted from the plotted values.
@@
 
-\section{Results}
-\label{Sec:Results}
-Here, we show the performance of the high-voltage piezo driver.
-In Fig.~\ref{Fig:PSD}, you can see the noise power spectral density at several different output voltages.
-This trace was taken on an SR780 spectrum analyzer, with the piezo output coupled through a \SI{0.5}{\hertz} high-pass filter. 
-The RMS noise ($\SI{1}{\hertz} - \SI{100}{\kilo\hertz}$) is \SI{80}{\micro\volt} at \SI{100}{\volt}.
-\begin{figure}[h]
-\includegraphics[width=\columnwidth]{fig/VoltagePSD.pdf}
-\caption{Voltage power spectral density at various output voltages.
-The integrated RMS voltage noise ($\SI{1}{\hertz} - \SI{100}{\kilo\hertz}$) is \SI{80}{\micro\volt} for the \SI{100}{\volt} output.\label{Fig:PSD}}
-\end{figure}
-
+Finally, Figure~\ref{Fig:TransferFunc} shows the measured frequency response under different load conditions.
+The unloaded bandwidth is as high as a few megahertz, while a \SI{1}{\micro\farad} capacitive load can still be driven at $\approx\SI{100}{\kilo\hertz}$.
+Several mechanical resonances can be seen with a \SI{700}{\nano\farad} piezoelectric load, as might be expected.
+In a laboratory setting, these resonances can be mitigated by using a digital feedback controller with notch filters tuned to match the exact resonance frequencies observed in the system\cite{Ryou2016a}, thereby extending the usable bandwidth out to $\approx\SI{100}{\kilo\hertz}$.
 \begin{figure}[h]
@@
 
-\begin{itemize}
-\item $1/f \rightarrow$ white noise corner frequency
-\item white noise spectral density
-\item RMS noise (0.1 - 10 Hz; 10 Hz - 10 kHz, or something similar) -- use SRS voltage preamp?
-\item How effective is the LM7171 at reducing switching noise? look at FFT power before final filter resistor, and at output of op amp (dBc spec)
-\item compare noise to predicted values
-\item longterm trace on kiethly -- across voltage divider at output? Monitor vs temperature? -- need to find low Tc resistors, at least.
-\item see what dependence is on power source -- eg, JQI power supply vs lab supply vs very quiet voltage regulator?
-\item current draw -- display in some ``bottom line'' specs table?
-\item bandwidth measurements -- full scale triangle ramp, small signal bandwidth -- discuss limitations on this (eg, also versus different piezo loads)
-\item Lock a laser, show RMS noise fluct vs. old piezo?
-\item compare to SC100 toptica controller? even if just internally.
-\end{itemize}
-
 \section{Conclusion}
 \label{Sec:Conclusion}
+
+We have designed, built, and characterized a high-voltage piezoelectric circuit optimized for use in a modern atomic physics laboratory.
+It is based on a flyback configuration switching regulator, but is able to achieve very low noise performance by active stabilization from a high slew-rate op-amp.
+This hybrid architecture makes it small and easy to deploy in a variety of situations, without requiring an external, bulky high-voltage power supply.
+The design principles discussed here can be adapted to fit the exact application, and all design files are freely available on GitHub for others to use and modify.
+
+The authors would like to thank Z. Smith for useful discussions.
+
+This work was partially supported by ONR, and the NSF through the PFC at the JQI.
+
+%
+%\section{Other...}
+%\begin{itemize}
+%\item $1/f \rightarrow$ white noise corner frequency
+%\item white noise spectral density
+%\item RMS noise (0.1 - 10 Hz; 10 Hz - 10 kHz, or something similar) -- use SRS voltage preamp?
+%\item How effective is the LM7171 at reducing switching noise? look at FFT power before final filter resistor, and at output of op amp (dBc spec)
+%\item compare noise to predicted values
+%\item longterm trace on kiethly -- across voltage divider at output? Monitor vs temperature? -- need to find low Tc resistors, at least.
+%\item see what dependence is on power source -- eg, JQI power supply vs lab supply vs very quiet voltage regulator?
+%\item current draw -- display in some ``bottom line'' specs table?
+%\item bandwidth measurements -- full scale triangle ramp, small signal bandwidth -- discuss limitations on this (eg, also versus different piezo loads)
+%\item Lock a laser, show RMS noise fluct vs. old piezo?
+%\item compare to SC100 toptica controller? even if just internally.
+%\end{itemize}
 
@@
 % Create the reference section using BibTeX:
-%\bibliography{your-bib-file}
+%\bibliographystyle{jabbrv_abbr}
+\bibliography{piezobib}
 % Run this once to generate your BBL file. Then copy the contents of your BBL file into your main latex file, commenting out "\bibliography"

### 2016-06-19 piezo.tex
first round of paper torture

@@
 \email[]{npisenti@umd.edu}
+\author{A. Restelli}
 \author{B.J. Reschovsky}
 \author{D.S. Barker}
-\author{A. Restelli}
 \author{G.K. Campbell}
@@
 We present an ultra-low noise, high voltage driver suited for use with piezoelectric actuators and other low-current applications. 
-The architecture leverages a commercially available, small-form-factor integrated circuit (IC) for generating high voltage outputs.
-The IC uses a flyback configuration switching regulator to generate up to 250V in our design (but up to 1kV or more with small modification), and a high slew-rate op-amp capacitively coupled to the output compensates for the switching noise.
-A low-voltage (\SI{\pm 10}{\volt}), high bandwidth modulation input is capable of summing small voltage corrections onto the output, making the driver well suited for use in closed-loop feedback applications.
+The architecture uses a flyback switching regulator to generate up to 250V in our current design, with an output of \SI{1}{\kilo\volt} or more possible with small modifications. 
+A high slew-rate op-amp suppresses the switching noise by XX dB (MEASURE), yielding a total RMS noise of $\approx\SI{100}{\micro\volt}$ (\SI{1}{\hertz}--\SI{100}{\kilo\hertz}).
+A low-voltage (\SI{\pm 10}{\volt}), high bandwidth signal can be summed directly onto the output, making the driver well-suited for closed-loop feedback applications.
+Digital control allows for repeatable setpoints, and the circuit consumes less than \SI{150}{\milli\ampere} at $\pm\SI{15}{\volt}$.
 \end{abstract}
@@
 Many instrumentation applications in the modern laboratory require agile, low-noise voltage sources capable of supplying hundreds of volts or more.
-For example, piezo-actuated mirrors and diffraction gratings play an important role in atomic physics experiments (used, e.g., in scanning Fabry-Per{\`o}t cavities and extended-cavity diode lasers), while avalanche photodiodes and photomultiplier tubes require large bias voltages for proper operation.
-In the realm of biophysics, electrokinetic separation methods such as free-flow or capillary electrophoresis require large electric field gradients, and the recent push to develop lab-on-a-chip devices could benefit from miniaturized high voltage sources~\cite{Kohlheyer2008a}.
-(ion traps?
-charge multiplier tubes?)
+For example, piezo-actuated mirrors and diffraction gratings play an important role in atomic physics experiments (used, e.g., in scanning Fabry-Per{\`o}t cavities\cite{REF} and extended-cavity diode lasers\cite{REF, also LIGO?}), while avalanche photodiodes and photomultiplier tubes require large bias voltages for proper operation.
+In the realm of biophysics, electrokinetic separation methods such as free-flow or capillary electrophoresis\cite{Kohlheyer2008a} require large electric field gradients, and the recent push to develop lab-on-a-chip devices could benefit from miniaturized high voltage sources\cite{REF}.
+(Jun Ye phase stabilziation paper, piezo actuated mirrors - optical tweezer experiments).
 
-Often, laboratory devices are operated in a closed feedback loop, where small voltage changes on top of a large DC voltage are necessary to stabilize the output of a particular system.
-For example, extended-cavity diode lasers can adjust their lasing frequency by changing the angle of a piezo-actuated diffraction grating that supplies optical feedback to the diode.
-Commercially available piezoelectric drivers typically provide a modulation input for  such closed-loop applications, but the input voltage is either AC coupled to the output or gained such that it spans the entire voltage range of the device.
+Laboratory devices are often operated in a closed feedback loop, where small voltage changes on top of a large DC voltage are necessary to stabilize the output of a particular system.
+For example, the frequency of an extended-cavity diode laser can be locked by feeding back to a piezo-actuated diffraction grating or mirror, which in turn supplies optical feedback to the diode.
+Commercially available piezoelectric drivers typically provide a modulation input for  such closed-loop applications, but the input voltage is gained such that it spans the entire output range of the device.
 While this has certain advantages, many applications would benefit from an architecture that provides a unity gain, DC-coupled feedback path to the high voltage output. 
@@
 
-Traditionally, instrumentation electronics capable of supplying high voltages fall under one of two architectural umbrellas: DC-DC switching converters, and linear-type amplifiers.
+Instrumentation electronics capable of supplying high voltages traditionally fall under one of two architectural umbrellas: DC-DC switching converters, and linear-type amplifiers.
 While DC-DC converters are efficient and can work at very high voltages, they suffer from switching noise and limited control bandwidths.
@@
 
-Here, we present a hybrid architecture: the high voltage is generated by a galvanically isolated DC-DC converter (described in Sec.~\ref{Sec:DRV2700}), while a low-noise, high slew-rate op-amp removes noise at the output by modulating the {OUT--} node of the switching converter (see Sec.~\ref{Sec:LowNoiseStabilization}).
+We present a circuit with a hybrid architecture.
+The high voltage is generated by a galvanically isolated DC-DC converter (described in Sec.~\ref{Sec:DRV2700}), while a low-noise, high slew-rate op-amp removes noise at the output  (see Sec.~\ref{Sec:LowNoiseStabilization}).
 The op-amp additionally provides a low-gain, high-bandwidth modulation input for closed-loop feedback applications.
-This architecture is able to achieve extremely low noise performance, draws very little current, and fits comfortably onto a small-footprint PCB.
+This architecture is able to achieve extremely low noise performance ($\approx\SI{100}{\micro\volt}_{\text{RMS}}$) over the entire output range, draws very little current, and fits comfortably onto a small-footprint PCB.
 Complete design files, including the schematic, bill of materials, and board layout, can be found on Github.~\footnote{\protect\url{https://github.com/JQIamo/hv-piezo-driver}}
+(TOTAL COST, etc.)
 % Mention other features?
@@
 \includegraphics[width=\textwidth]{fig/DRV2700.ai}
-\caption{Schematic of the high voltage stabilization.
+\caption{Schematic of the high voltage supply and stabilization.
 The voltage HV is generated using a Texas Instruments DRV2700 high voltage driver in flyback configuration.
-A fast, very high slew-rate op-amp senses the output voltage across $R_1$ and $R_2$, and servos it by modulating the node at ``HV floating gnd''.
-The DC control signal for this op-amp is supplied by a digital-to-analog (DAC) converter, which is passed through a switchable low-pass filter.
+A high slew-rate op-amp senses the output voltage across $R_1$ and $R_2$, and servos it by modulating the node at ``HV floating gnd''.
+The DC control signal for this op-amp,  $\text{V}_{\text{ctl}}$, is supplied by a digital-to-analog (DAC) converter, which is passed through a switchable low-pass filter.
 This allows for very heavy filtering of the DAC $1/f$ noise during steady-state operation, but the corner frequency can be increased if the output needs to be scanned more quickly.
-The $\text{V}_{\text{DC}}$ gain is set by $\left(1+R_1/R_2\right)$, while the modulation gain is set by $-R_{\text{mod}}/R_1$.
+The $\text{V}_{\text{ctl}}$ gain is set by $\left(1+R_1/R_2\right)$, while the modulation gain is set by $-R_{\text{mod}}/R_1$.
 The capacitor linking the floating ground node to the output allows the op-amp to remove residual switching noise and stabilize the DC output according to the transfer function given in Eq.~(\ref{Eq:FullTransferFunc}).
+Op-amps U1 and U2 are powered at $\pm\SI{15}{\volt}$ (not shown).
 \label{Fig:PiezoCircuit}}
@@
 %The full schematic, including Gerbers, a bill of materials, and layout design files, can be found on GitHub.~\footnote{\protect\url{https://github.com/JQIamo/hv-piezo-driver}}
+
+As shown in Figure~\ref{Fig:PiezoCircuit}, the circuit contains three key sections: the high voltage converter, the low-noise stabilization, ...
+(overview of key block elements);  existence of DAC, modulation input, etc.
+
+Add in additional section for slow ramp, including MOS circuit and switchable low-pass filter.
 
@@
 When the switch opens, the voltage across the secondary coil is inverted, putting the diode into conduction and charging the capacitor.
-By changing the rate at which the switch is engaged, the DRV2700 is able to regulate a particular voltage across the galvanically isolated output (nodes $\text{GND}_\text{HV}$ and HV in Fig.~\ref{Fig:PiezoCircuit}).
+By changing the switching duty cycle, the DRV2700 is able to regulate the voltage across the galvanically isolated output (nodes $\text{GND}_\text{HV}$ and HV in Fig.~\ref{Fig:PiezoCircuit}).
 
-The transformer (ATB3225, 1:10 step-up winding), diode, and RC feedback network are based on values suggested in the DRV2700 datasheet~\cite{DRV2700Datasheet,DRV2700EVMUserGuide}.
-Internally, the DRV2700 boost controller tries to drive the FB node to \SI{1.3}{\volt}.
-The op-amp U1 senses the voltage at nodes HV and $\text{GND}_\text{HV}$, and adjusts its output such that
+The DRV2700 implements output voltage control by comparing the feedback input pin, FB, with an internal \SI{1.3}{\volt} reference.
+The resistors $R_9$ and $R_{10}$ are chosen such that pin FB is at \SI{1.3}{\volt} when the output of U1 is at ground: $R_{10}/(R_9+R_{10}) = \SI{1.3}{\volt}/\SI{5}{\volt} \approx \num{0.26}$.
+The op-amp U1 subtracts $\text{GND}_{\text{HV}}$ and $G\cdot \text{V}_\text{ctl}$ from the voltage at node HV, ensuring the DRV2700 regulates the output voltage such that
 \begin{align}
 \label{Eq:U1Output}
-\text{HV} - \text{GND}_{\text{HV}} &= G\cdot V_{\text{dc}}\,,
+\text{V}_\text{HV} - \text{V}_{\text{FG}} &= G\cdot \text{V}_{\text{ctl}}\,,
 \end{align}
-where the gain $G$ is set by the resistor ratio $R_3/R_4 \equiv R_5/R_6$.
-This pseudo-differential feedback configuration ensures that, in the equilibrium given by Eq.~(\ref{Eq:U1Output}), the output of U1 is driven to \SI{0}{\volt}; the resistive divider $R_9$ and $R_{10}$ is then chosen such that $R_{10}/(R_9~||~R_{10}) = \SI{1.3}{\volt}/\SI{5}{\volt} \approx \num{0.26}$.
+where the gain $G$ is set by the resistor ratio $R_3/R_4 \equiv R_5/R_6$, and $\text{V}_\text{ctl}$ is the control voltage set by the DAC.
 The capacitors $C_3$ and $C_4$ are chosen such that $C_3 = \SI{22}{\pico\farad}$ and
 \begin{align}
-\frac{C_4}{C_3} &= \frac{R_3}{R_4~||~R_7}
+\frac{C_4}{C_3} &= \frac{R_3}{R_4~||~R_7}\,,
 \end{align}
-as suggested by the datasheet, and $R_6 = R_7 = R_8$.
-In our lab, we implement a gain $G\approx 50$ ($R_3 = R_5 = \SI{499}{\kilo\ohm}$; $R_4 = R_{6-8} = \SI{10}{\kilo\ohm}$) such that a \SI{5}{\volt} digital-to-analog converter (DAC) controlling the node $\text{V}_\text{DC}$ can span \SI{250}{\volt} at the output.
+as suggested by the DRV2700 datasheet\cite{DRV2700Datasheet}, $R_6 = R_7 = R_8$, and $R_i||R_j \equiv R_i R_j/(R_i + R_j)$.
+In our lab, we implement a gain $G\approx 50$ ($R_3 = R_5 = \SI{499}{\kilo\ohm}$; $R_4 = R_{6,7,8} = \SI{10}{\kilo\ohm}$), allowing our \SI{5}{\volt} control signal $\text{V}_\text{ctl}$ to span \SI{250}{\volt} at the output.
+A different DAC and/or a different gain factor could be chosen to adjust the maximum output voltage\footnote{Note that the passive components must be rated for the chosen output voltage.}.
+The transformer (ATB3225, 1:10 step-up winding), diode, and RC feedback network are all based on values suggested in the DRV2700 datasheet~\cite{DRV2700Datasheet,DRV2700EVMUserGuide}.
 
 The output of the flyback regulator is passed through a four-pole, low-pass RC filter.
-The corner frequency $f_c \approx \SI{3}{\kilo\hertz}$ is chosen to be high enough that a slow ($\approx \SI{10}{\hertz}$) rail-to-rail triangle ramp can be applied by the DAC at $\text{V}_\text{DC}$ (for, e.g., sweeping over a spectroscopy resonance), but low enough that the $\approx \SI{100}{\kilo\hertz}$ switching noise is substantially attenuated.
+The corner frequency $f_c \approx \SI{3}{\kilo\hertz}$ is chosen to be high enough that a slow ($\approx \SI{10}{\hertz}$) rail-to-rail triangle ramp can be applied by the DAC at $\text{V}_\text{ctl}$ (for, e.g., sweeping over a spectroscopy resonance), but low enough that the $\approx \SI{100}{\kilo\hertz}$ switching noise is substantially attenuated.
 Additional capacitors on both the HV and $\text{GND}_{\text{HV}}$ resistor networks shunt high frequency noise to ground.
+This filter topology, modeled on a lossy transmission line, is sufficient for our application, but other corner frequencies or topologies could also be used.
 
-\subsection{Low-noise stabilization}
+\subsection{Low-noise stabilization and fast modulation}
 \label{Sec:LowNoiseStabilization}
@@
 \begin{align}
-\text{V}_\text{HV} &= \left(1 + \frac{R_1}{R_2~||~R_\text{mod}}\right) \text{V}_\text{DC} -
+\text{V}_\text{out} &= \left(1 + \frac{R_1}{R_2~||~R_\text{mod}}\right) \text{V}_\text{ctl} -
 \left(\frac{R_\text{mod}}{R_1}\right) \text{V}_\text{mod}\,.
@@
 \end{align}
-We choose $R_1,\,R_\text{mod} = \SI{1}{\mega\ohm}$, $R_2 = \SI{20.5}{\kilo\ohm}$ such that the DC gain is $\approx 50$ and the modulation gain $\text{V}_\text{HV}/\text{V}_\text{mod}$ is unity.
-Depending on the application, other gain configurations would work equally well provided the non-inverting gain of U2 closely matches the gain of the flyback regulator (since they derive from the same control voltage).
-Ultimately, the op-amp U2 sets the operating voltage of the output (referenced to true circuit ground) while the flyback converter regulates the high voltage relative to the pseudoground node $\text{GND}_\text{HV}$.
-Because the output of the flyback regulator is galvanically isolated, U2 is free to control $\text{GND}_\text{HV}$. 
+Here, $\text{V}_\text{mod}$ is the applied modulation, which can vary between $\pm\SI{10}{\volt}$.
+We choose $R_1 = R_\text{mod} = \SI{1}{\mega\ohm}$ and $R_2 = \SI{20.5}{\kilo\ohm}$ such that the DC gain is $\approx 50$ and the modulation gain $\Delta\text{V}_\text{out}/\Delta\text{V}_\text{mod}$ is unity.
+Depending on the application, other gain configurations could work equally well provided the non-inverting gain of U2 closely matches the gain of the flyback regulator (since they both derive from $\text{V}_\text{ctl}$).
+Ultimately, the op-amp U2 sets the operating voltage of the output (referenced to true circuit ground) while the flyback converter regulates the high voltage relative to $\text{V}_\text{FG}$.
+Because the output of the flyback regulator is galvanically isolated, U2 is able to control $\text{V}_\text{FG}$. 
 At low frequencies, this amounts to changing the ``zero-volt'' reference for the flyback regulator, while at high frequencies the capacitor $\text{C}_\text{HV}$ provides a low-impedance pathway to the HV output.
-In this manner, U2 is simultaneously able to servo residual switching noise and provide a DC-coupled, high-bandwidth modulation of the output.
+Thus, U2 is simultaneously able to servo residual switching noise and provide a DC-coupled, high-bandwidth modulation of the output.
 
-As a final note, it is worth mentioning that the choice of component for resistors $R_1$ and $R_2$ is crucial for the low-noise performance of the system, because this resistive divider is responsible for accurately sensing the voltage $\text{V}_\text{HV}$; noise introduced by these resistors cannot be corrected by the op-amp, and thus appears directly at the output.
-Resistors are fundamentally limited by Johnson noise, in which thermal fluctuations contribute to a white noise power spectrum given by $\sqrt{k_B T R}$.(Cite art of electronics?)\cite{Horowitz1989a}
+The choice of component for resistors $R_1$ and $R_2$ is crucial for the low-noise performance of the system. 
+Because this resistive divider is responsible for accurately sensing the voltage $\text{V}_\text{out}$, noise introduced by these resistors cannot be corrected by the op-amp.
+In general, resistors are fundamentally limited by Johnson noise, in which thermal fluctuations contribute to a white noise power spectrum given by $\sqrt{4 k_B T R}$, where $T$ is the temperature and $k_B$ is Boltzmann's constant\cite{Horowitz1989aCITECHAPTER}.
 However, resistors also exhibit $1/f$ current noise caused by equilibrium fluctuations of the resistance~\cite{Clarke1974a,Voss1976a}.
-The magnitude of this ``excess noise'' is highly dependent on the resistor composition, and varies from manufacturer to manufacturer.
+This excess noise depends on the applied voltage, and therefore is an important consideration in a high-voltage circuit.
+It is also highly dependent on the resistor composition and varies from manufacturer to manufacturer.
 Seifert, et.
 al.~\cite{Seifert2009a} characterized $1/f$ noise in a variety of resistors, and found that the Vishay TNPW \SI{0.1}{\percent}-series resistors showed a noise spectrum almost consistent with Johnson noise down to \SI{1}{\hertz}.
-A previous iteration of this design used Panasonic ERJ-8ENF resistors (1206, \SI{1}{\percent}), and we noticed substantial low-frequency noise correlated with varying strain on the PCB.
-This is consistent with the findings in~\cite{Seifert2009a}, which showed this Panasonic series to exhibit voltage noise two orders of magnitude larger than the TNPW series at \SI{1}{\hertz}.
-The final board design utilizes three TNPW \SI{0.1}{\percent} 0603 resistors in series for both R1 and R2.
+Our current design uses this series in a 1206 package, but we noticed substantial low-frequency noise correlated with varying strain on the PCB, potentially due to the relatively large footprint of this device.
+Future boards will instead use three TNPW \SI{0.1}{\percent} 0603 resistors in series for both R1 and R2 to minimize strain-induced output noise.
+%A previous iteration of this design used Panasonic ERJ-8ENF resistors (1206, \SI{1}{\percent}), and we noticed substantial low-frequency noise correlated with varying strain on the PCB.
+%This is consistent with the findings in Seifert, which showed this Panasonic series to exhibit voltage noise two orders of magnitude larger than the TNPW series at \SI{1}{\hertz}.
+
+\subsection{Digital control and slow modulation}
+
+DAC sets control point, ucontroller can do a rail to rail slow ramp;
+Talk about MOS circuit, switchable lowpass filter (more in next section on noise);
 
@@
 
-A voltage proportional to the output (sensed at the inverting node of U2) is buffered and connected to a monitor BNC on the frontpanel and a GPIO line on the backplane.
+A voltage proportional to the output (sensed at the inverting node of U2, not shown on Figure~\ref{Fig:PiezoCircuit}) is buffered and connected to a monitor BNC on the frontpanel and a GPIO line on the backplane.
 In our lab, this GPIO line is fed to a low-noise current controller (based on the design in~\cite{Erickson2008a}) to implement a current feed-forward.
@@
 
-\subsection{Noise Analysis}
+\section{Noise Analysis}
 \label{Sec:NoiseAnalysis}
@@
 We now calculate the noise contribution of the DAC.
-The noise signal gain from the node $\text{V}_{\text{DC}}$ is given by
+The noise signal gain from the node $\text{V}_{\text{ctl}}$ is given by
 \begin{align}
@@
 \label{Eq:Gdc}
-G_{\text{DC}} &= \left(\frac{Z_\text{LP}}{R_\text{LP} + Z_\text{LP}}\right)\left(1+\frac{Z_1}{R_2\epar Z_{\text{mod}}}\right) \\
+G_{\text{ctl}} &= \left(\frac{Z_\text{LP}}{R_\text{LP} + Z_\text{LP}}\right)\left(1+\frac{Z_1}{R_2\epar Z_{\text{mod}}}\right) \\
 &= \left(\frac{Z_\text{LP}}{R_\text{LP} + Z_\text{LP}}\right)NG(s)\,,
@@
 where the first term represents the contribution to the transfer function from the switchable low-pass filter (discussed above).
-The DAC voltage noise contribution is then simply $e_{n,\text{DAC}} = G_{\text{DC}} v_{n,\text{DAC}}$. 
+The DAC voltage noise contribution is then simply $e_{n,\text{DAC}} = G_{\text{ctl}} v_{n,\text{DAC}}$. 
 The DAC used in our design (Analog devices, AD5663R) has a white noise floor of \SI[per-mode=symbol]{100}{\nano\volt\per\sqrthz} with an $\approx\SI{1}{\kilo\hertz}$ corner frequency.
-Without the addition of the low-pass filter after $\text{V}_\text{DC}$, this DAC would dominate both the low- and high-frequency noise performance of the circuit.
+Without the addition of the low-pass filter after $\text{V}_\text{ctl}$, this DAC would dominate both the low- and high-frequency noise performance of the circuit.
 However, we are instead dominated by Johnson noise at intermediate to high frequencies, and the op-amp's intrinsic current noise at lower frequencies.

### 2016-06-22 piezo.tex
Round two edits pre second paper torture
* better overview
* section about MOS quench and slow ramps

** Need to ammend section on voltage monitor

@@
 A low-voltage (\SI{\pm 10}{\volt}), high bandwidth signal can be summed directly onto the output, making the driver well-suited for closed-loop feedback applications.
-Digital control allows for repeatable setpoints, and the circuit consumes less than \SI{150}{\milli\ampere} at $\pm\SI{15}{\volt}$.
+Digital control enables repeatable setpoints or sophisticated control logic, and the circuit consumes less than \SI{150}{\milli\ampere} at $\pm\SI{15}{\volt}$.
 \end{abstract}
@@
 Many instrumentation applications in the modern laboratory require agile, low-noise voltage sources capable of supplying hundreds of volts or more.
-For example, piezo-actuated mirrors and diffraction gratings play an important role in atomic physics experiments (used, e.g., in scanning Fabry-Per{\`o}t cavities\cite{REF} and extended-cavity diode lasers\cite{REF, also LIGO?}), while avalanche photodiodes and photomultiplier tubes require large bias voltages for proper operation.
-In the realm of biophysics, electrokinetic separation methods such as free-flow or capillary electrophoresis\cite{Kohlheyer2008a} require large electric field gradients, and the recent push to develop lab-on-a-chip devices could benefit from miniaturized high voltage sources\cite{REF}.
-(Jun Ye phase stabilziation paper, piezo actuated mirrors - optical tweezer experiments).
+For example, piezo-actuated mirrors and diffraction gratings play an important role in atomic physics experiments (used, e.g., in Fabry-Per{\`o}t cavities\cite{Riedle1994a,Bohlouli-Zanjani2006a} and extended-cavity diode lasers\cite{Wieman1991a}), while avalanche photodiodes and photomultiplier tubes require large bias voltages for proper operation.
+% Huber2014a -- Ba+ paper with micro-positioning mirror??
+In the realm of biophysics, electrokinetic separation methods such as free-flow or capillary electrophoresis\cite{Kohlheyer2008a} require large electric field gradients, and the recent push to develop lab-on-a-chip devices could benefit from miniaturized high voltage sources\cite{Temiz2015a}.
 
@@
 This architecture is able to achieve extremely low noise performance ($\approx\SI{100}{\micro\volt}_{\text{RMS}}$) over the entire output range, draws very little current, and fits comfortably onto a small-footprint PCB.
-Complete design files, including the schematic, bill of materials, and board layout, can be found on Github.~\footnote{\protect\url{https://github.com/JQIamo/hv-piezo-driver}}
-(TOTAL COST, etc.)
+Complete design files, including the schematic, bill of materials, and board layout, can be found on Github\cite{DesignFiles}.
+The board manufacture and component cost is less than \SI{200}[\$]{}, making it a cost-effective alternative to commercial options. 
 % Mention other features?
@@
 
-The design principles discussed below show how researchers might leverage the versatility of galvanically isolated switching regulators in a low-noise laboratory environment. 
+The design principles discussed below show how we leverage the versatility of galvanically isolated switching regulators in a low-noise laboratory environment. 
 Our design targets a \SI{250}{\volt} output, but straightforward modifications to the schematic make it possible to tailor the gain and output range to a specific application.
@@
 
-As shown in Figure~\ref{Fig:PiezoCircuit}, the circuit contains three key sections: the high voltage converter, the low-noise stabilization, ...
-(overview of key block elements);  existence of DAC, modulation input, etc.
-
-Add in additional section for slow ramp, including MOS circuit and switchable low-pass filter.
+Figure~\ref{Fig:PiezoCircuit} shows the schematic overview. 
+A digital-to-analog converter (DAC) generates a voltage setpoint, which is sent to the high-voltage flyback regulator and to the low-noise stabilization circuit.
+The flyback regulator (Sec.~\ref{Sec:DRV2700}) controls the potential between circuit nodes $\text{V}_\text{HV}$ and $\text{V}_\text{FG}$, while the low-noise stabilization circuitry (Sec.~\ref{Sec:LowNoiseStabilization}) servos the output node $\text{V}_\text{out}$ relative to the true circuit ground.
+The DAC is controlled by an integrated microcontroller, and can be programmed to output slow ($\approx\SI{10}{\hertz}$) rail-to-rail voltage ramps in addition to setting the DC operating point.
+Because $1/f$ voltage noise in the DAC contributes heavily to the output noise, a low-pass filter can be engaged during DC operation to mitigate this effect (see Sec.~\ref{Sec:NoiseAnalysis}).
+To improve the large-voltage slew rate, a MOSFET ``quench'' circuit is included to shorten the $RC$ time constant of the high voltage node $\text{V}_\text{HV}$ when needed (Figure~\ref{Fig:MOS}, described in Sec.~\ref{Sec:SlowModulationMOS}).
+Fast output modulation over $\pm\SI{10}{\volt}$ can be achieved through the input node $\text{V}_\text{mod}$.
+This node is DC-coupled to the high voltage output, and is useful for closed-loop feedback control.
+The bandwidth under various loads is shown in Figure~\ref{Fig:TransferFunc}.
 
@@
 
-The high voltage DC-DC converter used here is based on the Texas Instruments DRV2700 piezo driver\footnote{The identification of commercial products is for information only and does not imply recommendation or endorsement by the National Institute of Standards and Technology.}.
+The high voltage DC-DC converter used here is based on the Texas Instruments DRV2700 piezo driver\footnote{The identification of commercial products in this paper is for information only and does not imply recommendation or endorsement by the National Institute of Standards and Technology.}.
 This single-chip integrated circuit (IC) can be operated as a boost converter to drive an on-chip differential amplifier up to \SI{100}{\volt}, or as a flyback converter up to \SI{1}{\kilo\volt} or more.
-In flyback configuration, the internal-boost switch of the DRV2700 drives a step-up transformer.
+In flyback configuration, the internal-boost switch of the DRV2700 (pin SW in Fig.~\ref{Fig:PiezoCircuit}) drives a step-up transformer.
 When the switch closes, current begins to flow through the primary coil of the transformer and induces a corresponding voltage across the secondary coil.
@@
 When the switch opens, the voltage across the secondary coil is inverted, putting the diode into conduction and charging the capacitor.
-By changing the switching duty cycle, the DRV2700 is able to regulate the voltage across the galvanically isolated output (nodes $\text{GND}_\text{HV}$ and HV in Fig.~\ref{Fig:PiezoCircuit}).
+By changing the switching duty cycle, the DRV2700 is able to regulate the voltage across the galvanically isolated output (nodes $\text{V}_\text{FG}$ and $\text{V}_\text{HV}$ in Fig.~\ref{Fig:PiezoCircuit}).
 
-The DRV2700 implements output voltage control by comparing the feedback input pin, FB, with an internal \SI{1.3}{\volt} reference.
+The DRV2700 implements output voltage control by comparing the feedback input pin at node $\text{V}_\text{FB}$ with an internal \SI{1.3}{\volt} reference.
 The resistors $R_9$ and $R_{10}$ are chosen such that pin FB is at \SI{1.3}{\volt} when the output of U1 is at ground: $R_{10}/(R_9+R_{10}) = \SI{1.3}{\volt}/\SI{5}{\volt} \approx \num{0.26}$.
-The op-amp U1 subtracts $\text{GND}_{\text{HV}}$ and $G\cdot \text{V}_\text{ctl}$ from the voltage at node HV, ensuring the DRV2700 regulates the output voltage such that
+The op-amp U1 subtracts $\text{V}_\text{FG}$ and $G\cdot \text{V}_\text{ctl}$ from the voltage at node $\text{V}_\text{HV}$, ensuring the DRV2700 regulates the output voltage such that
 \begin{align}
@@
 \end{align}
-as suggested by the DRV2700 datasheet\cite{DRV2700Datasheet}, $R_6 = R_7 = R_8$, and $R_i||R_j \equiv R_i R_j/(R_i + R_j)$.
-In our lab, we implement a gain $G\approx 50$ ($R_3 = R_5 = \SI{499}{\kilo\ohm}$; $R_4 = R_{6,7,8} = \SI{10}{\kilo\ohm}$), allowing our \SI{5}{\volt} control signal $\text{V}_\text{ctl}$ to span \SI{250}{\volt} at the output.
+as suggested by the DRV2700 datasheet\cite{DRV2700Datasheet}, where $R_6 = R_7 = R_8$, and $R_i||R_j \equiv R_i R_j/(R_i + R_j)$.
+In our lab, we implement a gain $G\approx 50$ ($R_3 = R_5 = \SI{499}{\kilo\ohm}$; $R_4 = R_{6,7,8} = \SI{10}{\kilo\ohm}$), allowing a \SI{5}{\volt} control signal $\text{V}_\text{ctl}$ to span \SI{250}{\volt} at the output.
 A different DAC and/or a different gain factor could be chosen to adjust the maximum output voltage\footnote{Note that the passive components must be rated for the chosen output voltage.}.
@@
 The corner frequency $f_c \approx \SI{3}{\kilo\hertz}$ is chosen to be high enough that a slow ($\approx \SI{10}{\hertz}$) rail-to-rail triangle ramp can be applied by the DAC at $\text{V}_\text{ctl}$ (for, e.g., sweeping over a spectroscopy resonance), but low enough that the $\approx \SI{100}{\kilo\hertz}$ switching noise is substantially attenuated.
-Additional capacitors on both the HV and $\text{GND}_{\text{HV}}$ resistor networks shunt high frequency noise to ground.
+Additional capacitors on both the $\text{V}_\text{HV}$ and $\text{V}_\text{FG}$ resistor networks shunt high frequency noise to ground.
 This filter topology, modeled on a lossy transmission line, is sufficient for our application, but other corner frequencies or topologies could also be used.
@@
 At low frequencies, this amounts to changing the ``zero-volt'' reference for the flyback regulator, while at high frequencies the capacitor $\text{C}_\text{HV}$ provides a low-impedance pathway to the HV output.
-Thus, U2 is simultaneously able to servo residual switching noise and provide a DC-coupled, high-bandwidth modulation of the output.
+Thus, U2 simultaneously servos residual switching noise from the flyback converter and provides a DC-coupled, high-bandwidth modulation of the output.
 
@@
 Because this resistive divider is responsible for accurately sensing the voltage $\text{V}_\text{out}$, noise introduced by these resistors cannot be corrected by the op-amp.
-In general, resistors are fundamentally limited by Johnson noise, in which thermal fluctuations contribute to a white noise power spectrum given by $\sqrt{4 k_B T R}$, where $T$ is the temperature and $k_B$ is Boltzmann's constant\cite{Horowitz1989aCITECHAPTER}.
+In general, resistors are fundamentally limited by Johnson noise, in which thermal fluctuations contribute to a white noise power spectrum given by $\sqrt{4 k_B T R}$, where $T$ is the temperature and $k_B$ is Boltzmann's constant\cite{Horowitz1989a}.
 However, resistors also exhibit $1/f$ current noise caused by equilibrium fluctuations of the resistance~\cite{Clarke1974a,Voss1976a}.
@@
 al.~\cite{Seifert2009a} characterized $1/f$ noise in a variety of resistors, and found that the Vishay TNPW \SI{0.1}{\percent}-series resistors showed a noise spectrum almost consistent with Johnson noise down to \SI{1}{\hertz}.
-Our current design uses this series in a 1206 package, but we noticed substantial low-frequency noise correlated with varying strain on the PCB, potentially due to the relatively large footprint of this device.
+Our current design uses this series in a 1206 package, but we noticed substantial low-frequency noise correlated with varying strain on the PCB, potentially due to the relatively large footprint of this package.
 Future boards will instead use three TNPW \SI{0.1}{\percent} 0603 resistors in series for both R1 and R2 to minimize strain-induced output noise.
@@
 
+The value of capacitor $\text{C}_1$ is a tradeoff between two competing design considerations.
+On the one hand, larger $\text{C}_1$ extends the bandwidth where the suppression of switching noise from the DRV2700 is maximal.
+However, large values of $\text{C}_1$ limit the bandwith of $\text{V}_\text{ctl}$ and increase the reverse transfer function from the load to the control, thereby limiting the directivity.
+We empirically settled on $\text{C}_1 = \SI{1}{\nano\farad}$.
+This value is large enough to saturate the feedback gain in the \SI{40}{\kilo\hertz}--\SI{100}{\kilo\hertz} range where switching noise dominates, but not so large that we limit the bandwidth of $\text{V}_\text{ctl}$.
+Once this value was chosen, capacitor $\text{C}_\text{mod}$ was calculated to match the impedances $R_1||\text{C}_1=R_\text{mod}||\text{C}_\text{mod}$.
+For our circuit, this means $\text{C}_\text{mod} = \text{C}_1$.
+
+%
+%The LM7171 has an open-loop gain of \SI{85}{\decibel}, with a dominant pole at $\approx\SI{10}{\kilo\hertz}$.
+%We thus model the open loop gain, $A_\text{OL}$, as
+%\begin{align}
+%A_\text{OL} &= \frac{10^{85/20}}{1+s/(2\pi\cdot\SI{10}{\kilo\hertz})}
+%\end{align}
+%Thus, noise appearing at $\text{V}_\text{out}$ is attenuated by a factor
+%\begin{align}
+%\frac{1}{1+A_\text{OL}\left(\frac{R_2||Z_\text{mod}}{Z_1 + R_2||Z_\text{mod}}\right)}
+%\end{align}
+%where $Z_1, Z_\text{mod}$ are the equivalent impedances of $R_1||\text{C}_1$ and $R_\text{mod}||\text{C}_\text{mod}$, respectively.
+%For $R_1=\SI{1}{\mega\ohm}$, choosing $\text{C}_1 = \SI{1}{\nano\farad}$ 
+%
+% such that the closed-loop gain for noise contributed by the flyback regulator at node $\text{V}_\text{out}$ is minimized in the \SIrange{40}{100}{\kilo\hertz} switching noise band.
+%For $R_1=\SI{1}{\mega\ohm}$, we choose $\text{C}_1=\SI{1}{\nano\farad}$.
+%The noise gain
+
 \subsection{Digital control and slow modulation}
+\label{Sec:SlowModulationMOS}
 
-DAC sets control point, ucontroller can do a rail to rail slow ramp;
-Talk about MOS circuit, switchable lowpass filter (more in next section on noise);
+\begin{figure}[b!]
+\includegraphics[width=\columnwidth]{fig/MOS.ai}
+\caption{MOSFET ``quench'' circuit.
+When the mid-ground node $\text{V}_\text{MG}$ (see Fig.~\ref{Fig:PiezoCircuit}) goes below the threshold value set at $\text{V}_\text{th}$, the op-amp puts the HV MOSFET Q1 into conduction.
+Now, the time constant for capacitor $\text{C}_\text{out}$ in Fig.~\ref{Fig:PiezoCircuit} is given by $R_\text{MOS} C_\text{out}$, which for our circuit is set to \SI{1}{\milli\second}.
+\label{Fig:MOS}}
+\end{figure}
 
-\subsection{Digital control and auxiliary design features}
-\label{Sec:DigControlAuxDesign}
+The high-voltage setpoint (absent voltages summed in at $\text{V}_\text{mod}$) is controlled by a low-noise DAC.
+This has two advantages: digital control enhances setpoint repeatability, and makes it easy to integrate with a wide variety of computerized control electronics or implement more sophisticated servo loops.
+So while the modulation input $\text{V}_\text{mod}$ has a limited range of $\pm\SI{10}{\volt}$, larger voltage swings can be achieved by reprogramming the DAC.
 
-The DC setpoint is controlled by a low-noise digital-to-analog converter (DAC).
-This has several advantages: digital control enhances setpoint repeatability, and makes it easy to integrate with a wide variety of computerized control electronics.
-The DAC itself is controlled by an onboard microcontroller, which also interacts with the frontpanel control switches, encoders, and LCD display.
-The entire circuit is designed to fit in a standard Eurocard rack, which supplies power at $\pm\SI{15}{\volt}$ and contains a backplane with analog lines to communicate with other modules (e.g., to implement a current feed-forward for laser diodes, see description below).
-The backplane also contains a secondary microcontroller, which can be addressed over TCP/IP.
-This vastly expands the conceivable control scenarios. For example, in our lab we implement a slow-feedback lock of two ECDL repumping lasers to a wavemeter.
-LabView code on the computer attached to the wavemeter computes an error signal and corrective control voltage, which can then be passed over our internal network to the piezo driver to correct for frequency drifts in the laser.
-Other similar schemes are possible, enabling complete remote control of the laser electronics.
+One downside of the flyback regulator presented above is that while the switched transformer is very efficient at charging the capacitor $\text{C}_\text{HV}$, discharge of the high-voltage line is limited by the $RC$ time constant of the circuit.
+To get around this limitation, we have added an auxiliary MOSFET ``quench'' circuit, as suggested in the DRV2700 datasheet, to quickly shunt $\text{V}_\text{out}$ to ground (see Figure~\ref{Fig:MOS}).
+This works by monitoring the voltage at $\text{V}_\text{MG}$, the mid-ground node controlled by op-amp U2.
+If that voltage drops below the threshold set by $\text{V}_\text{th}$, the comparator op-amp in Fig.~\ref{Fig:MOS} changes the gate voltage of the MOSFET to put it into conduction.
+Now, the time constant is given by $\tau \approx R_\text{MOS}\text{C}_\text{out}$.
+For our circuit, this is about \SI{1}{\milli\second} and the threshold $\text{V}_\text{th} \approx \SI{-10}{\volt}$ but other values could be chosen depending on the design requirements.
 
-In addition to software-defined control via the backplane, frontpanel control is provided by a rotary encoder/push button, and a single SPDT switch.
+\subsection{Auxiliary design features}
+\label{Sec:AuxDesign}
+
+Here, we discuss some additional features of our circuit that are independent of the high-voltage design but make it nicer to work with in the laboratory.
+The onboard microcontroller responsible for setting the DAC control voltage, $\text{V}_\text{ctl}$, also interfaces with frontpanel controls including a switch, LCD, and rotary encoder with an integrated push button.
 The encoder/push button provide menu navigation, and the switch toggles between DC and scanning operation.
@@
 
-A voltage proportional to the output (sensed at the inverting node of U2, not shown on Figure~\ref{Fig:PiezoCircuit}) is buffered and connected to a monitor BNC on the frontpanel and a GPIO line on the backplane.
-In our lab, this GPIO line is fed to a low-noise current controller (based on the design in~\cite{Erickson2008a}) to implement a current feed-forward.
-An optional analog voltage from the backplane can also be summed with the modulation voltage supplied via BNC on the frontpanel to generate $\text{V}_{\text{mod}}$.
+The entire circuit fits into a standard Eurocard rack, which supplies power at $\pm\SI{15}{\volt}$.
+While not required, the rack provides a backplane with analog lines to communicate with other modules (e.g., to implement a current feed-forward for laser diodes, see description below).
+We are presently designing a backplane with a secondary microcontroller that can be addressed over TCP/IP.
+This vastly expands the conceivable control scenarios. 
+For example, in our lab we implement a slow-feedback lock of two external-cavity diode lasers to a wavemeter for repumping strontium.
+LabView code on the computer attached to the wavemeter computes an error signal and corrective control voltage, which will be passed over our internal network to the piezo driver to correct for frequency drifts in the laser.
+Other similar schemes are possible, enabling complete remote control of the laser electronics.
+
+The modulation voltage $\text{V}_\text{mod}$ can be supplied either from a BNC on the frontpanel, or from the backplane.
 This may be useful, e.g., with servo controllers that reside in the same rack as the other control electronics.
+In either case, this voltage is differentially buffered to break ground loops.
+An output voltage monitor (sensed at the inverting node of U2 in Figure~\ref{Fig:PiezoCircuit}) is buffered and connected to a BNC on the frontpanel, a GPIO line on the backplane, and to the microcontroller.
+This enables the microcontroller to digitally implement an infinite integrator, driving $\text{V}_\text{mod}$ to \SI{0}{\volt} in closed-loop operation and preventing the servo controller from railing.
+In our lab, the GPIO voltage monitor is fed to a low-noise current controller (based on the design in~\cite{Erickson2008a}) to implement a laser diode current feed-forward.
+The high voltage output is interlocked with a signal on the backplane (which can optionally be bypassed by placing an onboard jumper), permitting easy integration with existing laboratory interlock schemes if desired.
 
-Finally, the high voltage output is interlocked with a signal on the back plane (which can optionally be over-ridden by placing a jumper); this allows easy integration into existing laboratory interlock schemes, if desired.
+%While the integrated Eurocard rack and backplane are convenient, they are not necessary to use the circuit design we provide -- one can equally supply $\pm\SI{15}{\volt}$ and program the microcontroller to fit whichever enclosure is at hand.
 For more details, see the design files and documentation on Github~\cite{DesignFiles}.
@@
 \caption{Noise model (see text).
-In reality, the capacitor labeled $Z_\text{LP}$ is comprised of a \SI{47}{\nano\farad} capacitor in parallel with a switchable \SI{10}{\micro\farad} capacitor, such that the corner frequency of the filter can be changed depending on the mode of operation.
-The $\text{R}_\text{on}$ resistance of the switch introduces a zero in the transfer function at $\approx\SI{23}{\kilo\hertz}$, which has negligible effect on the computed RMS noise.
+The element labeled $Z_\text{LP}$ is comprised of a \SI{47}{\nano\farad} capacitor in parallel with a \SI{10}{\micro\farad} capacitor connected to ground through a switch, such that the corner frequency of the filter can be changed depending on the mode of operation.
+The on-resistance of the switch introduces a zero in the transfer function at $\approx\SI{23}{\kilo\hertz}$, which has negligible effect on the computed RMS noise.
 \label{Fig:NoiseModel}}
@@
 \hline
-\rule{0pt}{2ex}$e_n$ (op-amp)  & \SI{26}{\micro\volt} & \SI{27}{\micro\volt}      \\
-$i_n$ (op-amp)  &            \SI{49}{\micro\volt}     & \SI{59}{\micro\volt}      \\
-DAC             &             \SI{22}{\micro\volt}    & \SI{7}{\micro\volt}       \\
+\rule{0pt}{2ex}$e_n$ (op-amp)  & \SI{26}{\micro\volt} & \SI{31}{\micro\volt}      \\
+$i_n$ (op-amp)  &            \SI{51}{\micro\volt}     & \SI{73}{\micro\volt}      \\
+DAC             &             \SI{28}{\micro\volt}    & \SI{8}{\micro\volt}       \\
 Johnson-Nyquist &             \SI{3}{\micro\volt}    & \SI{31}{\micro\volt}        \\ 
 \hline
-\rule{0pt}{2ex}\textbf{total (calculated)} & \SI{60}{\micro\volt} & \SI{73}{\micro\volt}  \\
+\rule{0pt}{2ex}\textbf{total (calculated)} & \SI{64}{\micro\volt} & \SI{86}{\micro\volt}  \\
 \hline\hline
@@
 Plotted are the noise contributions from each source in our model, along with the total calculated noise.
-Power spectral density is referred to the high voltage output, and the table shows the integrated RMS noise due to each noise source in different frequency bands.
-The total RMS noise (summed in quadrature) over the entire \SI{1}{\hertz}~--~\SI{100}{\kilo\hertz} range is calculated to be \SI{94}{\micro\volt}.
+Power spectral density (PSD) is referred to the high voltage output, and the table shows the integrated RMS noise due to each noise source in different frequency bands.
+The total RMS noise (summed in quadrature) over the entire \SI{1}{\hertz}~--~\SI{100}{\kilo\hertz} range is calculated to be \SI{107}{\micro\volt}.
 \label{Fig:NoisePlot}}
@@
 
-We analyze the noise performance of the circuit according to the model shown in Fig.~\ref{Fig:NoiseModel}, where noise spectral densities are calculated at the node $\text{V}_\text{HV}$.
-A summary of each noise contribution (op-amp, DAC, Johnson-Nyquist, external modulation input) is shown in Fig.~\ref{Fig:NoisePlot}, along with the cumulative root-mean-square (RMS) nose estimates in different frequency bands.
+We analyze the noise performance of the circuit according to the model shown in Fig.~\ref{Fig:NoiseModel}, where noise spectral densities are calculated at the node $\text{V}_\text{out}$.
+A summary of each noise contribution (op-amp, DAC, Johnson-Nyquist) is shown in Fig.~\ref{Fig:NoisePlot}, along with the cumulative root-mean-square (RMS) nose estimates in different frequency bands.
 % We also discuss, given our choice of op-amp, the noise rejection ratio from the DRV2700 flyback regulator.
@@
 \label{Eq:NG}
-NG(s) &= 1 + \frac{Z_1}{R_2 \epar Z_{\text{mod}}}\,,
+NG(s) &= 1 + Z_1\left(\frac{1}{R_2} + \frac{1}{Z_\text{mod}}\right)\,,
 \end{align}
@@
 \label{Eq:ZnZp}
-Z_n &= Z_1 \epar Z_{\text{mod}} \epar  R_2   = \frac{Z_1}{2} \epar R_2 \\
-Z_p &= R_{\text{LP}}  \big|\big|\frac{1}{s~C_{\text{LP}}}
+Z_n &\equiv \left(\frac{1}{Z_1} + \frac{1}{Z_\text{mod}} +  \frac{1}{R_2}\right)^{-1}   = \frac{Z_1 R_2}{2R_2 + Z_1} \\
+Z_p &\equiv \left(\frac{1}{R_\text{LP}} + \frac{1}{Z_\text{LP}}\right)^{-1}\,.
 \end{split}
 \end{align}
+The impedance $Z_\text{LP}$ is determined by the corner frequency of a switchable low-pass filter between the DAC and the non-inverting node of U2 (discussed below).
+
 The total noise contribution of the op-amp (referenced to the output) is
@@
 \begin{align}
-\begin{split}
 \label{Eq:Gdc}
-G_{\text{ctl}} &= \left(\frac{Z_\text{LP}}{R_\text{LP} + Z_\text{LP}}\right)\left(1+\frac{Z_1}{R_2\epar Z_{\text{mod}}}\right) \\
-&= \left(\frac{Z_\text{LP}}{R_\text{LP} + Z_\text{LP}}\right)NG(s)\,,
-\end{split}
+G_{\text{ctl}} &= \left(\frac{Z_\text{LP}}{R_\text{LP} + Z_\text{LP}}\right)NG(s)\,,
 \end{align}
-where the first term represents the contribution to the transfer function from the switchable low-pass filter (discussed above).
-The DAC voltage noise contribution is then simply $e_{n,\text{DAC}} = G_{\text{ctl}} v_{n,\text{DAC}}$. 
-The DAC used in our design (Analog devices, AD5663R) has a white noise floor of \SI[per-mode=symbol]{100}{\nano\volt\per\sqrthz} with an $\approx\SI{1}{\kilo\hertz}$ corner frequency.
-Without the addition of the low-pass filter after $\text{V}_\text{ctl}$, this DAC would dominate both the low- and high-frequency noise performance of the circuit.
-However, we are instead dominated by Johnson noise at intermediate to high frequencies, and the op-amp's intrinsic current noise at lower frequencies.
-Both of these contributions could potentially be suppressed by using lower resistances $R_1, R_\text{mod}$, however one must be careful about power and current limitations when dealing with such high voltages.
-Each noise source is tabulated and plotted in Fig.~\ref{Fig:NoisePlot}.
+where the first term represents the contribution to the transfer function from the switchable low-pass filter.
+Without the addition of this low-pass filter, the voltage noise of the DAC would dominate both the low- and high-frequency noise performance of the circuit.
+But if we were to simply place a fixed-corner filter at this node, we would severely restrict the AC performance of $\text{V}_\text{ctl}$.
+Thus, the switchable low-pass filter is necessary to achieve low-noise performance during ``DC'' operation, while still permitting the DAC to modulate $\text{V}_\text{ctl}$ more quickly when needed.
+In our circuit, the high-corner filter is comprised of a \SI{20.5}{\kilo\ohm} resistor and \SI{47}{\nano\farad} capacitor, with $f_c \approx \SI{165}{\hertz}$.
+In ``DC'' mode, a secondary \SI{10}{\micro\farad} capacitor in parallel with the \SI{47}{\nano\farad} capacitor mentioned above can be shorted to ground through a low resistance digital switch.
+This changes the corner frequency to \SI{0.8}{\hertz}.
+The non-zero resistance of the digital switch contributes a zero to the transfer function at high frequencies, but has negligible effect on the performance.
+The DAC voltage noise contribution can now be calculated as $e_{n,\text{DAC}} = G_{\text{ctl}} v_{n,\text{DAC}}$, where $v_{n,\text{DAC}}$ is the frequency dependent output voltage noise of the DAC. 
+In subsequent calculations, we take the ``DC mode'' operation for the switchable low-pass filter.
+%The DAC used in our design (Analog devices, AD5663R) has a white noise floor of \SI[per-mode=symbol]{100}{\nano\volt\per\sqrthz} with an $\approx\SI{1}{\kilo\hertz}$ corner frequency.
+
+The low-noise stabilization circuit is limited in its ability to reject residual switching noise $v_{n,\text{DRV}}$ from the DRV2700 regulator by the total loop gain analyzed from node $\text{V}_\text{out}$.
+The LM7171 has an open-loop gain of \SI{85}{\decibel}, with a dominant pole at $\approx\SI{10}{\kilo\hertz}$.
+We model the open loop gain, $A_\text{OL}$, as
+\begin{align}
+A_\text{OL} &= \frac{10^{85/20}}{1+s/(2\pi\cdot\SI{10}{\kilo\hertz})}
+\end{align}
+Thus, noise appearing at $\text{V}_\text{out}$ is attenuated by a factor
+\begin{align}
+\frac{1}{1+A_\text{OL}\left(\frac{R_2||Z_\text{mod}}{Z_1 + R_2||Z_\text{mod}}\right)}
+\end{align}
+For $R_1=\SI{1}{\mega\ohm}$ and $\text{C}_1 = \SI{1}{\nano\farad}$, $v_{n,\text{DRV}}$ is attenuated by as much as \SI{76}{\decibel} at \SI{6.3}{\kilo\hertz}, with a rolloff of \SI[per-mode=symbol]{10}{\decibel\per\text{decade}} at higher frequencies.
+(INCLUDE DRV NOISE MODEL IN CALCULATION??)
+
+% such that the closed-loop gain for noise contributed by the flyback regulator at node $\text{V}_\text{out}$ is minimized in the \SIrange{40}{100}{\kilo\hertz} switching noise band.
+%For $R_1=\SI{1}{\mega\ohm}$, we choose $\text{C}_1=\SI{1}{\nano\farad}$.
+%The noise gain
+
+Given the noise model discussed above, our circuit is dominated by Johnson noise at intermediate to high frequencies, and the op-amp's intrinsic current noise at lower frequencies.
+Both of these contributions could be suppressed by using lower resistances $R_1, R_\text{mod}$, however one must be careful about power and current limitations when dealing with such high voltages.
+Each noise source is tabulated and plotted in Fig.~\ref{Fig:NoisePlot}, and the total voltage noise  is calculated to be $\SI{107}{\micro\volt}$ ($\SI{1}{\hertz} - \SI{100}{\kilo\hertz}$).
 
@@
 \label{Sec:Results}
-Here, we show the measured performance of the high-voltage piezo driver.
-In Fig.~\ref{Fig:PSD}, we plot the noise power spectral density measured at several different output voltages.
-These traces were taken on an SR780 spectrum analyzer, with the piezo output coupled through a \SI{0.5}{\hertz} high-pass filter. 
-At \SI{100}{\volt}, the integrated noise ($\SI{1}{\hertz} - \SI{100}{\kilo\hertz}$) was measured to be $\SI{80}{\micro\volt}_\text{RMS}$ ($\SI{138}{\micro\volt}_\text{RMS}$, $\SI{101}{\micro\volt}_\text{RMS}$ for \SI{50}{\volt}, \SI{200}{\volt} outputs).
-This matches well with the expected total RMS noise calculated in Section~\ref{Sec:NoiseAnalysis}.
-
-\begin{figure}[hb]
+\begin{figure}[t]
 \includegraphics[width=\columnwidth]{fig/VoltagePSD.pdf}
@@
 
+In this section, we show the measured performance of the high-voltage piezo driver.
+In Fig.~\ref{Fig:PSD}, we plot the noise power spectral density measured at several different output voltages.
+These traces were taken on a Stanford Research Systems SR780 spectrum analyzer, with the piezo output coupled through a \SI{0.5}{\hertz} high-pass filter. 
+At \SI{100}{\volt}, the integrated noise ($\SI{1}{\hertz} - \SI{100}{\kilo\hertz}$) was measured to be $\SI{80}{\micro\volt}_\text{RMS}$ ($\SI{138}{\micro\volt}_\text{RMS}$, $\SI{101}{\micro\volt}_\text{RMS}$ for \SI{50}{\volt}, \SI{200}{\volt} outputs).
+This matches well with the expected total RMS noise calculated in Section~\ref{Sec:NoiseAnalysis}.
+
 Figure~\ref{Fig:TimeDomain} shows the performance at both short- and long-time scales.
@@
 This is due generically to $1/f$ noise, but also correlates with the external temperature.
-A cross-correlation between measured temperature and output voltage fluctuation yields an effective temperature coefficient of \SI[per-mode=symbol]{-24}{ppm\per\celsius} at \SI{100}{\volt}.
+A cross-correlation between measured temperature and output voltage (trace not shown) yields an effective temperature coefficient of \SI[per-mode=symbol]{-24}{ppm\per\celsius} at \SI{100}{\volt}.
 The short-term trace was taken on a PicoScope~5442B (ac-coupled, \SI{100}{\volt} output).
@@
 
-\begin{figure}[h]
+\begin{figure}[t]
 \includegraphics[width=\columnwidth]{fig/TimeDomain.pdf}
@@
 
-Finally, Figure~\ref{Fig:TransferFunc} shows the measured frequency response under different load conditions.
+Figure~\ref{Fig:TransferFunc} shows the measured frequency response under different load conditions.
 The unloaded bandwidth is as high as a few megahertz, while a \SI{1}{\micro\farad} capacitive load can still be driven at $\approx\SI{100}{\kilo\hertz}$.
-Several mechanical resonances can be seen with a \SI{700}{\nano\farad} piezoelectric load, as might be expected.
+Several mechanical resonances can be seen with a \SI{700}{\nano\farad} piezoelectric load, as expected.
 In a laboratory setting, these resonances can be mitigated by using a digital feedback controller with notch filters tuned to match the exact resonance frequencies observed in the system\cite{Ryou2016a}, thereby extending the usable bandwidth out to $\approx\SI{100}{\kilo\hertz}$.
-\begin{figure}[h]
+\begin{figure}[t]
 \includegraphics[width=\columnwidth]{fig/PiezoModulationTransfer.pdf}
-\caption{Modulation input transfer function.
-Green trace shows the response with a ThorLabs piezoelectric actuator {(PN~AE0505D08F)}; the mechanical resonances above $\approx\SI{50}{\kilo\hertz}$ are clearly visible.
-The red trace shows the response under a \SI{1}{\micro\farad} purely capacitive load.
-Loaded response bandwidth is $\approx\SI{100}{\kilo\hertz}$, while unloaded the bandwidth is $\approx\SI{1}{\mega\hertz}$.\label{Fig:TransferFunc}}
+\caption{Modulation input transfer function (color online).
+The blue line indicates the unloaded frequency response, while the dash-dotted orange trace shows the response with a ThorLabs piezoelectric actuator {(PN~AE0505D08F)}.
+Mechanical resonances above $\approx\SI{50}{\kilo\hertz}$ are clearly visible.
+The dashed green trace shows the response under a \SI{1}{\micro\farad} purely capacitive load.
+Loaded response bandwidth is $\approx\SI{100}{\kilo\hertz}$, while the unloaded bandwidth is $\approx\SI{1}{\mega\hertz}$.\label{Fig:TransferFunc}}
 \end{figure}
@@
 
-We have designed, built, and characterized a high-voltage piezoelectric circuit optimized for use in a modern atomic physics laboratory.
+We have designed, built, and characterized a high-voltage piezoelectric driver optimized for use in a modern atomic physics laboratory.
 It is based on a flyback configuration switching regulator, but is able to achieve very low noise performance by active stabilization from a high slew-rate op-amp.
@@
 The authors would like to thank Z. Smith for useful discussions.
-
-This work was partially supported by ONR, and the NSF through the PFC at the JQI.
+This work was partially supported by the Office of Naval Research, and the National Science Foundation through the Physics Frontier Center at the Joint Quantum Institute.
 
@@
 %\bibliographystyle{jabbrv_abbr}
-\bibliography{piezobib}
+\bibliography{references}
 % Run this once to generate your BBL file. Then copy the contents of your BBL file into your main latex file, commenting out "\bibliography"

### 2016-06-28 piezo.tex
Edits; about to rewrite noise analysis section

@@
 This architecture is able to achieve extremely low noise performance ($\approx\SI{100}{\micro\volt}_{\text{RMS}}$) over the entire output range, draws very little current, and fits comfortably onto a small-footprint PCB.
+Additionally, the high-voltage output is single-ended and referenced to ground, allowing it to drive piezo actuators with a grounded terminal.
+In Section~\ref{Sec:NoiseAnalysis} we present a noise analysis, and show characteristic performance data in Section~\ref{Sec:Results}.
 Complete design files, including the schematic, bill of materials, and board layout, can be found on Github\cite{DesignFiles}.
@@
 \caption{Schematic of the high voltage supply and stabilization.
-The voltage HV is generated using a Texas Instruments DRV2700 high voltage driver in flyback configuration.
-A high slew-rate op-amp senses the output voltage across $R_1$ and $R_2$, and servos it by modulating the node at ``HV floating gnd''.
+The voltage $\text{V}_\text{HV}$ is generated using a Texas Instruments DRV2700 high voltage driver in flyback configuration.
+A high slew-rate op-amp (U2) senses the output voltage across $R_1$ and $R_2$, and servos it by modulating the node at ``HV floating gnd''.
 The DC control signal for this op-amp,  $\text{V}_{\text{ctl}}$, is supplied by a digital-to-analog (DAC) converter, which is passed through a switchable low-pass filter.
@@
 The design principles discussed below show how we leverage the versatility of galvanically isolated switching regulators in a low-noise laboratory environment. 
-Our design targets a \SI{250}{\volt} output, but straightforward modifications to the schematic make it possible to tailor the gain and output range to a specific application.
+Our design targets a \SI{250}{\volt} output, but straightforward modifications to the schematic (discussed below) make it possible to tailor the gain and output range to a specific application.
 The entire electronics package fits comfortably into a 12HP eurocard rack module (with the high voltage section taking only a fraction of the PCB), and draws less than \SI{150}{\milli\ampere} at \SI{15}{\volt}.
@@
 Figure~\ref{Fig:PiezoCircuit} shows the schematic overview. 
-A digital-to-analog converter (DAC) generates a voltage setpoint, which is sent to the high-voltage flyback regulator and to the low-noise stabilization circuit.
+A digital-to-analog converter (DAC) generates a voltage setpoint, $\text{V}_\text{ctl}$, which is sent to the high-voltage flyback regulator and to the low-noise stabilization circuit.
 The flyback regulator (Sec.~\ref{Sec:DRV2700}) controls the potential between circuit nodes $\text{V}_\text{HV}$ and $\text{V}_\text{FG}$, while the low-noise stabilization circuitry (Sec.~\ref{Sec:LowNoiseStabilization}) servos the output node $\text{V}_\text{out}$ relative to the true circuit ground.
-The DAC is controlled by an integrated microcontroller, and can be programmed to output slow ($\approx\SI{10}{\hertz}$) rail-to-rail voltage ramps in addition to setting the DC operating point.
-Because $1/f$ voltage noise in the DAC contributes heavily to the output noise, a low-pass filter can be engaged during DC operation to mitigate this effect (see Sec.~\ref{Sec:NoiseAnalysis}).
-To improve the large-voltage slew rate, a MOSFET ``quench'' circuit is included to shorten the $RC$ time constant of the high voltage node $\text{V}_\text{HV}$ when needed (Figure~\ref{Fig:MOS}, described in Sec.~\ref{Sec:SlowModulationMOS}).
-Fast output modulation over $\pm\SI{10}{\volt}$ can be achieved through the input node $\text{V}_\text{mod}$.
+The DAC is controlled by an integrated microcontroller, and can be programmed to output slow ($\approx\SI{10}{\hertz}$) rail-to-rail voltage ramps in addition to setting the DC operating point (Sec.~\ref{Sec:SlowModulationMOS}).
+To improve the large-voltage slew rate, a MOSFET ``quench'' circuit (Figure~\ref{Fig:MOS}) is included to shorten the $RC$ time constant of the high voltage node $\text{V}_\text{HV}$ when needed.
+Because $1/f$ voltage noise in the DAC contributes heavily to the output noise, a low-pass filter can be engaged during DC operation to mitigate this output noise (discussed in Sec.~\ref{Sec:NoiseAnalysis}).
+Fast output modulation between $\pm\SI{10}{\volt}$ can be achieved through the input node $\text{V}_\text{mod}$.
 This node is DC-coupled to the high voltage output, and is useful for closed-loop feedback control.
-The bandwidth under various loads is shown in Figure~\ref{Fig:TransferFunc}.
 
@@
 Because the output of the flyback regulator is galvanically isolated, U2 is able to control $\text{V}_\text{FG}$. 
-At low frequencies, this amounts to changing the ``zero-volt'' reference for the flyback regulator, while at high frequencies the capacitor $\text{C}_\text{HV}$ provides a low-impedance pathway to the HV output.
+At low frequencies, this amounts to changing the floating ground reference for the flyback regulator, while at high frequencies the capacitor $\text{C}_\text{HV}$ provides a low-impedance pathway to $\text{V}_\text{out}$.
 Thus, U2 simultaneously servos residual switching noise from the flyback converter and provides a DC-coupled, high-bandwidth modulation of the output.
@@
 Because this resistive divider is responsible for accurately sensing the voltage $\text{V}_\text{out}$, noise introduced by these resistors cannot be corrected by the op-amp.
-In general, resistors are fundamentally limited by Johnson noise, in which thermal fluctuations contribute to a white noise power spectrum given by $\sqrt{4 k_B T R}$, where $T$ is the temperature and $k_B$ is Boltzmann's constant\cite{Horowitz1989a}.
+In general, resistors are fundamentally limited by Johnson noise, in which thermal fluctuations contribute to a white noise power spectrum given by $4 k_B T R$, where $T$ is the temperature and $k_B$ is Boltzmann's constant\cite{Horowitz1989a}.
 However, resistors also exhibit $1/f$ current noise caused by equilibrium fluctuations of the resistance~\cite{Clarke1974a,Voss1976a}.
@@
 The value of capacitor $\text{C}_1$ is a tradeoff between two competing design considerations.
-On the one hand, larger $\text{C}_1$ extends the bandwidth where the suppression of switching noise from the DRV2700 is maximal.
-However, large values of $\text{C}_1$ limit the bandwith of $\text{V}_\text{ctl}$ and increase the reverse transfer function from the load to the control, thereby limiting the directivity.
-We empirically settled on $\text{C}_1 = \SI{1}{\nano\farad}$.
-This value is large enough to saturate the feedback gain in the \SI{40}{\kilo\hertz}--\SI{100}{\kilo\hertz} range where switching noise dominates, but not so large that we limit the bandwidth of $\text{V}_\text{ctl}$.
-Once this value was chosen, capacitor $\text{C}_\text{mod}$ was calculated to match the impedances $R_1||\text{C}_1=R_\text{mod}||\text{C}_\text{mod}$.
+On the one hand, a larger $\text{C}_1$ extends the frequency range where switching noise from the DRV2700 is suppressed.
+However, large values of $\text{C}_1$ limit the bandwith of $\text{V}_\text{ctl}$.
+We empirically settled on $\text{C}_1 = \SI{1}{\nano\farad}$, which is large enough to saturate the feedback gain in the \SI{40}{\kilo\hertz}--\SI{100}{\kilo\hertz} range where switching noise dominates, but not so large that it limits the bandwidth of $\text{V}_\text{ctl}$ below the corner set by the switchable low-pass filter described in Section~\ref{Sec:SlowModulationMOS}.
+Once $\text{C}_1$ was chosen, capacitor $\text{C}_\text{mod}$ was calculated to match the impedances $R_1||\text{C}_1=R_\text{mod}||\text{C}_\text{mod}$.
 For our circuit, this means $\text{C}_\text{mod} = \text{C}_1$.
@@
 \caption{MOSFET ``quench'' circuit.
-When the mid-ground node $\text{V}_\text{MG}$ (see Fig.~\ref{Fig:PiezoCircuit}) goes below the threshold value set at $\text{V}_\text{th}$, the op-amp puts the HV MOSFET Q1 into conduction.
-Now, the time constant for capacitor $\text{C}_\text{out}$ in Fig.~\ref{Fig:PiezoCircuit} is given by $R_\text{MOS} C_\text{out}$, which for our circuit is set to \SI{1}{\milli\second}.
+When the mid-ground node $\text{V}_\text{MG}$ (also shown in Fig.~\ref{Fig:PiezoCircuit}) goes below the threshold value set at $\text{V}_\text{TH}$, the op-amp puts the HV MOSFET Q1 into conduction.
+When engaged, the time constant for capacitor $\text{C}_\text{out}$ in Fig.~\ref{Fig:PiezoCircuit} is given by $R_\text{MOS} C_\text{out}$, which for our circuit is set to \SI{1}{\milli\second}.
 \label{Fig:MOS}}
@@
 This has two advantages: digital control enhances setpoint repeatability, and makes it easy to integrate with a wide variety of computerized control electronics or implement more sophisticated servo loops.
-So while the modulation input $\text{V}_\text{mod}$ has a limited range of $\pm\SI{10}{\volt}$, larger voltage swings can be achieved by reprogramming the DAC.
+While the modulation input $\text{V}_\text{mod}$ has a limited range of $\pm\SI{10}{\volt}$, larger voltage swings can be achieved by reprogramming the DAC.
 
-One downside of the flyback regulator presented above is that while the switched transformer is very efficient at charging the capacitor $\text{C}_\text{HV}$, discharge of the high-voltage line is limited by the $RC$ time constant of the circuit.
+As discussed in Section~\ref{Sec:NoiseAnalysis}, without modification the DAC would dominate the noise performance of $\text{V}_\text{out}$.
+Therefore, we add a single-pole low-pass filter between $\text{V}_\text{ctl}$ and the non-inverting node of U2.
+This filter has a switchable corner frequency (between \SI{165}{\hertz} and \SI{0.8}{\hertz}) to optimize noise performance at DC while still allowing for AC modulation when needed.
+
+One downside of the flyback regulator presented above is that while the switched transformer is very efficient at charging the capacitor $\text{C}_\text{HV}$, discharge of the high-voltage line is limited by the $\approx\SI{1}{\second}$ RC time constant of the circuit.
 To get around this limitation, we have added an auxiliary MOSFET ``quench'' circuit, as suggested in the DRV2700 datasheet, to quickly shunt $\text{V}_\text{out}$ to ground (see Figure~\ref{Fig:MOS}).
-This works by monitoring the voltage at $\text{V}_\text{MG}$, the mid-ground node controlled by op-amp U2.
-If that voltage drops below the threshold set by $\text{V}_\text{th}$, the comparator op-amp in Fig.~\ref{Fig:MOS} changes the gate voltage of the MOSFET to put it into conduction.
-Now, the time constant is given by $\tau \approx R_\text{MOS}\text{C}_\text{out}$.
-For our circuit, this is about \SI{1}{\milli\second} and the threshold $\text{V}_\text{th} \approx \SI{-10}{\volt}$ but other values could be chosen depending on the design requirements.
+This circuit works by monitoring the voltage at $\text{V}_\text{MG}$, the mid-ground node controlled by op-amp U2.
+If that voltage drops below a threshold set by $\text{V}_\text{TH}$, the comparator op-amp in Figure~\ref{Fig:MOS} changes the gate voltage of the MOSFET to put it into conduction.
+The time constant for this configuration is given by $\tau \approx R_\text{MOS}\text{C}_\text{out}$.
+For our circuit, this changes $\tau$ to $\approx\SI{1}{\milli\second}$, allowing for the fast discharge of $\text{C}_\text{out}$.
+The threshold is $\text{V}_\text{TH} = \SI{-10.4}{\volt}$, but other values could be chosen depending on the design requirements.
 
@@
 
-Here, we discuss some additional features of our circuit that are independent of the high-voltage design but make it nicer to work with in the laboratory.
+Here, we discuss some additional features of our circuit that are independent of the high-voltage design but are advantageous for many applications.
 The onboard microcontroller responsible for setting the DAC control voltage, $\text{V}_\text{ctl}$, also interfaces with frontpanel controls including a switch, LCD, and rotary encoder with an integrated push button.
@@
 The entire circuit fits into a standard Eurocard rack, which supplies power at $\pm\SI{15}{\volt}$.
-While not required, the rack provides a backplane with analog lines to communicate with other modules (e.g., to implement a current feed-forward for laser diodes, see description below).
+While not required, the rack provides a backplane with analog lines to communicate with other modules (e.g., to implement a current feed-forward for laser diodes as described below).
 We are presently designing a backplane with a secondary microcontroller that can be addressed over TCP/IP.
 This vastly expands the conceivable control scenarios. 
-For example, in our lab we implement a slow-feedback lock of two external-cavity diode lasers to a wavemeter for repumping strontium.
+For example, in our lab we implement a slow-feedback lock of two external-cavity diode lasers to a wavemeter.
 LabView code on the computer attached to the wavemeter computes an error signal and corrective control voltage, which will be passed over our internal network to the piezo driver to correct for frequency drifts in the laser.
@@
 In either case, this voltage is differentially buffered to break ground loops.
-An output voltage monitor (sensed at the inverting node of U2 in Figure~\ref{Fig:PiezoCircuit}) is buffered and connected to a BNC on the frontpanel, a GPIO line on the backplane, and to the microcontroller.
-This enables the microcontroller to digitally implement an infinite integrator, driving $\text{V}_\text{mod}$ to \SI{0}{\volt} in closed-loop operation and preventing the servo controller from railing.
-In our lab, the GPIO voltage monitor is fed to a low-noise current controller (based on the design in~\cite{Erickson2008a}) to implement a laser diode current feed-forward.
-The high voltage output is interlocked with a signal on the backplane (which can optionally be bypassed by placing an onboard jumper), permitting easy integration with existing laboratory interlock schemes if desired.
-
-%While the integrated Eurocard rack and backplane are convenient, they are not necessary to use the circuit design we provide -- one can equally supply $\pm\SI{15}{\volt}$ and program the microcontroller to fit whichever enclosure is at hand.
-For more details, see the design files and documentation on Github~\cite{DesignFiles}.
+An output voltage monitor (sensed at the inverting node of U2 in Figure~\ref{Fig:PiezoCircuit}, but not shown) is buffered and connected to a BNC on the frontpanel, an analog signal line on the backplane, and to the microcontroller\footnote{One drawback of this scheme is that the contribution of $\text{V}_\text{mod}$ is not sensed by the monitor.
+Future versions will instead monitor $\text{V}_\text{out}$ through a resistive divider, allowing the microcontroller to implement an infinite integrator and drive $\text{V}_\text{mod}$ to \SI{0}{\volt} in closed-loop operation.
+This will be a very useful feature to prevent the servo controller from railing.}.
+%This enables the microcontroller to digitally implement an infinite integrator, driving $\text{V}_\text{mod}$ to \SI{0}{\volt} in closed-loop operation and preventing the servo controller from railing.
+The backplane monitor could be fed to a low-noise current controller (e.g., one based on the design in~\cite{Erickson2008a}) to implement a laser diode current feed-forward.
+The high voltage output is interlocked with another signal on the backplane, which can optionally be bypassed by placing an onboard jumper, permitting easy integration with existing laboratory interlock schemes if desired.
+Further details on the design features discussed in this section, including sample software, can be found on Github~\cite{DesignFiles}.
 
@@
 The element labeled $Z_\text{LP}$ is comprised of a \SI{47}{\nano\farad} capacitor in parallel with a \SI{10}{\micro\farad} capacitor connected to ground through a switch, such that the corner frequency of the filter can be changed depending on the mode of operation.
-The on-resistance of the switch introduces a zero in the transfer function at $\approx\SI{23}{\kilo\hertz}$, which has negligible effect on the computed RMS noise.
+%The on-resistance of the switch introduces a zero in the transfer function at $\approx\SI{23}{\kilo\hertz}$, which has negligible effect on the computed RMS noise.
 \label{Fig:NoiseModel}}
@@
 \hline
-\rule{0pt}{2ex}$e_n$ (op-amp)  & \SI{26}{\micro\volt} & \SI{31}{\micro\volt}      \\
-$i_n$ (op-amp)  &            \SI{51}{\micro\volt}     & \SI{73}{\micro\volt}      \\
+\rule{0pt}{2ex}$e_n$ (op-amp U2)  & \SI{26}{\micro\volt} & \SI{31}{\micro\volt}      \\
+$i_n$ (op-amp U2)  &            \SI{51}{\micro\volt}     & \SI{73}{\micro\volt}      \\
 DAC             &             \SI{28}{\micro\volt}    & \SI{8}{\micro\volt}       \\
@@
 We analyze the noise performance of the circuit according to the model shown in Fig.~\ref{Fig:NoiseModel}, where noise spectral densities are calculated at the node $\text{V}_\text{out}$.
-A summary of each noise contribution (op-amp, DAC, Johnson-Nyquist) is shown in Fig.~\ref{Fig:NoisePlot}, along with the cumulative root-mean-square (RMS) nose estimates in different frequency bands.
-% We also discuss, given our choice of op-amp, the noise rejection ratio from the DRV2700 flyback regulator.
-% -- not sure about how to do this... could just report the measured value.
+A summary of each noise contribution (op-amp, DAC, Johnson-Nyquist, residual DRV2700) is shown in Fig.~\ref{Fig:NoisePlot}, along with the cumulative root-mean-square (RMS) nose estimates in different frequency bands.
 
-To treat the intrinsic op-amp noise contributions, we first compute the noise gain ($NG$) for this amplifier configuration according to
+To treat the intrinsic op-amp noise contributions, we first compute the noise gain $G_n$ for this amplifier configuration according to
 \begin{align}
 \label{Eq:NG}
-NG(s) &= 1 + Z_1\left(\frac{1}{R_2} + \frac{1}{Z_\text{mod}}\right)\,,
+G_n(s) &= 1 + Z_1\left(\frac{1}{R_2} + \frac{1}{Z_\text{mod}}\right)\,,
 \end{align}
-where we've defined the equivalent impedances $Z_1 = R_1/(1+R_1 C_1 s)$ and $Z_{\text{mod}} = R_{\text{mod}}/(1+R_{\text{mod}} C_{\text{mod}} s)$, and $s = i\omega$ is the frequency in the Laplace domain.
+with equivalent impedances $Z_1 = R_1/(1+R_1 C_1 s)$ and $Z_{\text{mod}} = R_{\text{mod}}/(1+R_{\text{mod}} C_{\text{mod}} s)$, and where $s$ is the Laplace variable.
 By design, we've chosen $Z_1 \equiv Z_{\text{mod}}$ such that the signal gain from the node $\text{V}_{\text{mod}}$ is unity.
@@
 \label{Eq:RedNG}
-NG(s) &= 2 + \frac{Z_1}{R_2}\,.
+G_n(s) &= 2 + \frac{Z_1}{R_2}\,.
 \end{align}
@@
 The voltage noise is summed in at the non-inverting input, while the current noise is present at both inputs.
-To convert $i_n$ to an equivalent voltage noise $e_n$, we multiply by the impedances $Z_n$, $Z_p$ seen by the inverting and non-inverting nodes, respectively.
+To convert $i_n$ to an equivalent voltage noise $e_n$, we multiply by the impedances $Z_n$ and $Z_p$ seen by the inverting and non-inverting nodes, respectively.
 These are calculated as
@@
 The impedance $Z_\text{LP}$ is determined by the corner frequency of a switchable low-pass filter between the DAC and the non-inverting node of U2 (discussed below).
-
-The total noise contribution of the op-amp (referenced to the output) is
+The total noise contribution of the op-amp U2 (referenced to the output) is
 \begin{align}
 \label{Eq:OpAmpNoise}
-e_{n,\text{op-amp}} &= NG(s)\sqrt{e_n^2 + (Z_n i_n)^2 + (Z_p i_n)^2}
+e_{n,\text{U2}} &= G_n(s)\sqrt{e_n^2 + (Z_n i_n)^2 + (Z_p i_n)^2}\,.
 \end{align}
 
-We now calculate the noise contribution of the DAC.
+Next, we calculate the noise contribution from the DAC.
 The noise signal gain from the node $\text{V}_{\text{ctl}}$ is given by
@@
 \label{Eq:Gdc}
-G_{\text{ctl}} &= \left(\frac{Z_\text{LP}}{R_\text{LP} + Z_\text{LP}}\right)NG(s)\,,
+G_{\text{ctl}} &= \left(\frac{Z_\text{LP}}{R_\text{LP} + Z_\text{LP}}\right)G_n(s)\,,
 \end{align}
@@
 Without the addition of this low-pass filter, the voltage noise of the DAC would dominate both the low- and high-frequency noise performance of the circuit.
-But if we were to simply place a fixed-corner filter at this node, we would severely restrict the AC performance of $\text{V}_\text{ctl}$.
-Thus, the switchable low-pass filter is necessary to achieve low-noise performance during ``DC'' operation, while still permitting the DAC to modulate $\text{V}_\text{ctl}$ more quickly when needed.
+A simple solution would be to place a fixed-corner filter at this node, but this would severely restrict the AC performance of $\text{V}_\text{ctl}$.
+Thus, we use a switchable low-pass filter (as described in Sec.~\ref{Sec:SlowModulationMOS}) to achieve low-noise performance during DC operation, while still permitting the DAC to modulate $\text{V}_\text{ctl}$ more quickly when needed.
 In our circuit, the high-corner filter is comprised of a \SI{20.5}{\kilo\ohm} resistor and \SI{47}{\nano\farad} capacitor, with $f_c \approx \SI{165}{\hertz}$.
-In ``DC'' mode, a secondary \SI{10}{\micro\farad} capacitor in parallel with the \SI{47}{\nano\farad} capacitor mentioned above can be shorted to ground through a low resistance digital switch.
+In DC mode, a secondary \SI{10}{\micro\farad} capacitor in parallel with the \SI{47}{\nano\farad} capacitor mentioned above can be connected to ground through a low resistance digital switch.
 This changes the corner frequency to \SI{0.8}{\hertz}.
-The non-zero resistance of the digital switch contributes a zero to the transfer function at high frequencies, but has negligible effect on the performance.
+The non-zero resistance of the switch contributes a zero to the transfer function at $\approx\SI{23}{\kilo\hertz}$, but has negligible effect on the performance.
 The DAC voltage noise contribution can now be calculated as $e_{n,\text{DAC}} = G_{\text{ctl}} v_{n,\text{DAC}}$, where $v_{n,\text{DAC}}$ is the frequency dependent output voltage noise of the DAC. 
-In subsequent calculations, we take the ``DC mode'' operation for the switchable low-pass filter.
+In subsequent calculations, we take the DC mode operation for the switchable low-pass filter.
 %The DAC used in our design (Analog devices, AD5663R) has a white noise floor of \SI[per-mode=symbol]{100}{\nano\volt\per\sqrthz} with an $\approx\SI{1}{\kilo\hertz}$ corner frequency.
 
-The low-noise stabilization circuit is limited in its ability to reject residual switching noise $v_{n,\text{DRV}}$ from the DRV2700 regulator by the total loop gain analyzed from node $\text{V}_\text{out}$.
-The LM7171 has an open-loop gain of \SI{85}{\decibel}, with a dominant pole at $\approx\SI{10}{\kilo\hertz}$.
-We model the open loop gain, $A_\text{OL}$, as
+The low-noise stabilization circuit is limited in its ability to reject residual switching noise from the DRV2700 regulator and passive filtering by the total loop gain analyzed from node $\text{V}_\text{out}$.
+The LM7171 has an open-loop gain of \SI{85}{\decibel} ($\approx 1.8\times 10^4$), with a dominant pole at $\approx\SI{10}{\kilo\hertz}$\cite{LM7171Datasheet}.
+We model the open loop gain, $G_\text{OL}$, as
 \begin{align}
-A_\text{OL} &= \frac{10^{85/20}}{1+s/(2\pi\cdot\SI{10}{\kilo\hertz})}
+G_\text{OL} &= \frac{1.8\times10^4}{1+s/(2\pi\cdot\SI{10}{\kilo\hertz})}\,.
 \end{align}
-Thus, noise appearing at $\text{V}_\text{out}$ is attenuated by a factor
+The contribution of this residual switching noise, $v_{n,\text{DRV}}$, to the output is given by
 \begin{align}
-\frac{1}{1+A_\text{OL}\left(\frac{R_2||Z_\text{mod}}{Z_1 + R_2||Z_\text{mod}}\right)}
+e_{n,\text{DRV}} &= \frac{v_{n,\text{DRV}}}{1+G_\text{OL}\left(\frac{R_2||Z_\text{mod}}{Z_1 + R_2||Z_\text{mod}}\right)}\,.
 \end{align}
 For $R_1=\SI{1}{\mega\ohm}$ and $\text{C}_1 = \SI{1}{\nano\farad}$, $v_{n,\text{DRV}}$ is attenuated by as much as \SI{76}{\decibel} at \SI{6.3}{\kilo\hertz}, with a rolloff of \SI[per-mode=symbol]{10}{\decibel\per\text{decade}} at higher frequencies.
-(INCLUDE DRV NOISE MODEL IN CALCULATION??)
+(INCLUDE DRV NOISE MODEL IN CALCULATION?? -- EG, WHAT ORDER DO THEY CONTRIBUTE?)
 
@@
 Given the noise model discussed above, our circuit is dominated by Johnson noise at intermediate to high frequencies, and the op-amp's intrinsic current noise at lower frequencies.
-Both of these contributions could be suppressed by using lower resistances $R_1, R_\text{mod}$, however one must be careful about power and current limitations when dealing with such high voltages.
+Both of these contributions could be suppressed by using lower resistances $R_1$ and $R_\text{mod}$, however one must be careful about power and current limitations when dealing with such high voltages.
 Each noise source is tabulated and plotted in Fig.~\ref{Fig:NoisePlot}, and the total voltage noise  is calculated to be $\SI{107}{\micro\volt}$ ($\SI{1}{\hertz} - \SI{100}{\kilo\hertz}$).
+Frequency-dependent input noise parameters in this model were extracted from datasheet spectral density curves\cite{SHEETS}.
 
@@
 \caption{Voltage power spectral density at various output voltages.
-The integrated RMS voltage noise ($\SI{1}{\hertz} - \SI{100}{\kilo\hertz}$) is $\{138, 80, 101\}~\si{\micro\volt}$ measured at  $\{50, 100, 200\}~\si{\volt}$.
+The integrated RMS voltage noise ($\SI{1}{\hertz} - \SI{100}{\kilo\hertz}$) is $\{138, 80, 101\}~\si{\micro\volt}$ measured at  $\{50, 100, 200\}~\si{\volt}$, with no output load.
 \label{Fig:PSD}}
@@
 
-In this section, we show the measured performance of the high-voltage piezo driver.
-In Fig.~\ref{Fig:PSD}, we plot the noise power spectral density measured at several different output voltages.
-These traces were taken on a Stanford Research Systems SR780 spectrum analyzer, with the piezo output coupled through a \SI{0.5}{\hertz} high-pass filter. 
-At \SI{100}{\volt}, the integrated noise ($\SI{1}{\hertz} - \SI{100}{\kilo\hertz}$) was measured to be $\SI{80}{\micro\volt}_\text{RMS}$ ($\SI{138}{\micro\volt}_\text{RMS}$, $\SI{101}{\micro\volt}_\text{RMS}$ for \SI{50}{\volt}, \SI{200}{\volt} outputs).
+The measured performance of the high-voltage piezo driver is shown in Fig.~\ref{Fig:PSD}, where we plot the noise power spectral density measured at several different output voltages.
+These traces were taken on a Stanford Research Systems SR780 spectrum analyzer, with the high-voltage output coupled through a \SI{0.5}{\hertz} high-pass filter and without any capacitive load.
+This represents a worst-case scenario, as larger capacitances at the output will reduce the noise.
+The integrated noise ($\SI{1}{\hertz} - \SI{100}{\kilo\hertz}$) was measured to be $\{\SI{138}{\micro\volt}_\text{RMS},~\SI{80}{\micro\volt}_\text{RMS},~\SI{101}{\micro\volt}_\text{RMS}\}$ for \{\SI{50}{\volt}, \SI{100}{\volt}, \SI{200}{\volt}\} outputs.
 This matches well with the expected total RMS noise calculated in Section~\ref{Sec:NoiseAnalysis}.
+DISCUSS WHY 50V IS WORSE
 
@@
 \caption{Time-domain traces of the high voltage output (\SI{100}{\volt}).
-Top: short-time scatterplot  (AC coupled).
+(a) Short-time scatterplot  (AC coupled).
 Points are colored based on the Gaussian spread in acquired voltages, thus indicating the RMS width of the trace.
-Bottom: long-term trace, measured on a Keithly~2010 digital multimeter.
+(b) Long-term trace, measured on a Keithly~2010 digital multimeter.
 A~\SI{100}{\volt} DC offset is subtracted from the plotted values.
-The top trace shows the lab temperature during the same time period.\label{Fig:TimeDomain}}
+The top panel shows the lab temperature during the same time period.\label{Fig:TimeDomain}}
 \end{figure}

### 2016-07-28 piezo.tex
Rewrote noise analysis, about to input final edits

@@
 The architecture uses a flyback switching regulator to generate up to 250V in our current design, with an output of \SI{1}{\kilo\volt} or more possible with small modifications. 
-A high slew-rate op-amp suppresses the switching noise by XX dB (MEASURE), yielding a total RMS noise of $\approx\SI{100}{\micro\volt}$ (\SI{1}{\hertz}--\SI{100}{\kilo\hertz}).
-A low-voltage (\SI{\pm 10}{\volt}), high bandwidth signal can be summed directly onto the output, making the driver well-suited for closed-loop feedback applications.
+%A high slew-rate op-amp suppresses the switching noise by XX dB (MEASURE), yielding a total RMS noise of $\approx\SI{100}{\micro\volt}$ (\SI{1}{\hertz}--\SI{100}{\kilo\hertz}).
+A high slew-rate op-amp suppresses the residual switching noise, yielding a total RMS noise of $\approx\SI{100}{\micro\volt}$ (\SI{1}{\hertz}--\SI{100}{\kilo\hertz}).
+A low-voltage (\SI{\pm 10}{\volt}), high bandwidth signal can be summed with unity gain directly onto the output, making the driver well-suited for closed-loop feedback applications.
 Digital control enables repeatable setpoints or sophisticated control logic, and the circuit consumes less than \SI{150}{\milli\ampere} at $\pm\SI{15}{\volt}$.
@@
 We present a circuit with a hybrid architecture.
-The high voltage is generated by a galvanically isolated DC-DC converter (described in Sec.~\ref{Sec:DRV2700}), while a low-noise, high slew-rate op-amp removes noise at the output  (see Sec.~\ref{Sec:LowNoiseStabilization}).
-The op-amp additionally provides a low-gain, high-bandwidth modulation input for closed-loop feedback applications.
+The high voltage is generated by a galvanically isolated DC-DC converter (described in Sec.~\ref{Sec:DRV2700}), while a low-noise, high slew-rate op-amp simulatneously removes noise at the output and provides a low-gain, high-bandwidth modulation input for closed-loop feedback applications  (see Sec.~\ref{Sec:LowNoiseStabilization}).
 This architecture is able to achieve extremely low noise performance ($\approx\SI{100}{\micro\volt}_{\text{RMS}}$) over the entire output range, draws very little current, and fits comfortably onto a small-footprint PCB.
-Additionally, the high-voltage output is single-ended and referenced to ground, allowing it to drive piezo actuators with a grounded terminal.
-In Section~\ref{Sec:NoiseAnalysis} we present a noise analysis, and show characteristic performance data in Section~\ref{Sec:Results}.
+Additionally, the high-voltage output remains single-ended and referenced to ground, allowing it to drive piezo actuators with a grounded terminal.
+%Additionally, the high-voltage output is single-ended and referenced to ground, allowing it to drive piezo actuators with a grounded terminal.
+In Sec.~\ref{Sec:NoiseAnalysis} we present a noise analysis, and show characteristic performance data in Sec.~\ref{Sec:Results}.
 Complete design files, including the schematic, bill of materials, and board layout, can be found on Github\cite{DesignFiles}.
@@
 
-Figure~\ref{Fig:PiezoCircuit} shows the schematic overview. 
+Fig.~\ref{Fig:PiezoCircuit} shows the schematic overview. 
 A digital-to-analog converter (DAC) generates a voltage setpoint, $\text{V}_\text{ctl}$, which is sent to the high-voltage flyback regulator and to the low-noise stabilization circuit.
@@
 The DAC is controlled by an integrated microcontroller, and can be programmed to output slow ($\approx\SI{10}{\hertz}$) rail-to-rail voltage ramps in addition to setting the DC operating point (Sec.~\ref{Sec:SlowModulationMOS}).
-To improve the large-voltage slew rate, a MOSFET ``quench'' circuit (Figure~\ref{Fig:MOS}) is included to shorten the $RC$ time constant of the high voltage node $\text{V}_\text{HV}$ when needed.
-Because $1/f$ voltage noise in the DAC contributes heavily to the output noise, a low-pass filter can be engaged during DC operation to mitigate this output noise (discussed in Sec.~\ref{Sec:NoiseAnalysis}).
-Fast output modulation between $\pm\SI{10}{\volt}$ can be achieved through the input node $\text{V}_\text{mod}$.
+To improve the large-voltage slew rate, a MOSFET ``quench'' circuit (Fig.~\ref{Fig:MOS}) is included to shorten the $RC$ time constant of the high voltage node $\text{V}_\text{HV}$ when needed.
+A switchable corner low-pass filter can be engaged during DC operation to reduce $1/f$ noise from the DAC (discussed in Sec.~\ref{Sec:NoiseAnalysis}), and
+%Because $1/f$ voltage noise in the DAC contributes heavily to the output noise, a low-pass filter can be engaged during DC operation to mitigate this output noise (discussed in Sec.~\ref{Sec:NoiseAnalysis}).
+fast output modulation between $\pm\SI{10}{\volt}$ can be achieved through the input node $\text{V}_\text{mod}$.
 This node is DC-coupled to the high voltage output, and is useful for closed-loop feedback control.
@@
 \end{align}
-as suggested by the DRV2700 datasheet\cite{DRV2700Datasheet}, where $R_6 = R_7 = R_8$, and $R_i||R_j \equiv R_i R_j/(R_i + R_j)$.
+as suggested by the DRV2700 datasheet\cite{DRV2700Datasheet}, where $R_6 = R_7 = R_8$, and $R_i~||~R_j \equiv R_i R_j/(R_i + R_j)$.
 In our lab, we implement a gain $G\approx 50$ ($R_3 = R_5 = \SI{499}{\kilo\ohm}$; $R_4 = R_{6,7,8} = \SI{10}{\kilo\ohm}$), allowing a \SI{5}{\volt} control signal $\text{V}_\text{ctl}$ to span \SI{250}{\volt} at the output.
@@
 Because this resistive divider is responsible for accurately sensing the voltage $\text{V}_\text{out}$, noise introduced by these resistors cannot be corrected by the op-amp.
-In general, resistors are fundamentally limited by Johnson noise, in which thermal fluctuations contribute to a white noise power spectrum given by $4 k_B T R$, where $T$ is the temperature and $k_B$ is Boltzmann's constant\cite{Horowitz1989a}.
+Resistors are fundamentally limited by Johnson noise, in which thermal fluctuations contribute to a white noise power spectrum given by $4 k_B T R$, where $T$ is the temperature and $k_B$ is Boltzmann's constant\cite{Horowitz2015a:JN}.
 However, resistors also exhibit $1/f$ current noise caused by equilibrium fluctuations of the resistance~\cite{Clarke1974a,Voss1976a}.
@@
 However, large values of $\text{C}_1$ limit the bandwith of $\text{V}_\text{ctl}$.
-We empirically settled on $\text{C}_1 = \SI{1}{\nano\farad}$, which is large enough to saturate the feedback gain in the \SI{40}{\kilo\hertz}--\SI{100}{\kilo\hertz} range where switching noise dominates, but not so large that it limits the bandwidth of $\text{V}_\text{ctl}$ below the corner set by the switchable low-pass filter described in Section~\ref{Sec:SlowModulationMOS}.
-Once $\text{C}_1$ was chosen, capacitor $\text{C}_\text{mod}$ was calculated to match the impedances $R_1||\text{C}_1=R_\text{mod}||\text{C}_\text{mod}$.
+We empirically settled on $\text{C}_1 = \SI{1}{\nano\farad}$, which is large enough to saturate the feedback gain in the \SI{40}{\kilo\hertz}--\SI{100}{\kilo\hertz} range where switching noise dominates, but not so large that it limits the bandwidth of $\text{V}_\text{ctl}$ below the corner set by the switchable low-pass filter described in Sec.~\ref{Sec:SlowModulationMOS}.
+Once $\text{C}_1$ was chosen, capacitor $\text{C}_\text{mod}$ was calculated to match the impedances $R_1~||~\text{C}_1 = R_\text{mod}~||~\text{C}_\text{mod}$.
 For our circuit, this means $\text{C}_\text{mod} = \text{C}_1$.
@@
 
-\begin{figure}[b!]
+\begin{figure}[t!]
 \includegraphics[width=\columnwidth]{fig/MOS.ai}
@@
 
-As discussed in Section~\ref{Sec:NoiseAnalysis}, without modification the DAC would dominate the noise performance of $\text{V}_\text{out}$.
+As discussed below in Sec.~\ref{Sec:NoiseAnalysis}, without modification the DAC would dominate the noise performance of $\text{V}_\text{out}$.
 Therefore, we add a single-pole low-pass filter between $\text{V}_\text{ctl}$ and the non-inverting node of U2.
-This filter has a switchable corner frequency (between \SI{165}{\hertz} and \SI{0.8}{\hertz}) to optimize noise performance at DC while still allowing for AC modulation when needed.
+This filter has a switchable corner frequency (between \SI{165}{\hertz} and \SI{0.8}{\hertz}) to optimize noise performance at DC while still permitting AC modulation when needed.
 
 One downside of the flyback regulator presented above is that while the switched transformer is very efficient at charging the capacitor $\text{C}_\text{HV}$, discharge of the high-voltage line is limited by the $\approx\SI{1}{\second}$ RC time constant of the circuit.
-To get around this limitation, we have added an auxiliary MOSFET ``quench'' circuit, as suggested in the DRV2700 datasheet, to quickly shunt $\text{V}_\text{out}$ to ground (see Figure~\ref{Fig:MOS}).
+To get around this limitation, we have added an auxiliary MOSFET ``quench'' circuit, as suggested in the DRV2700 datasheet, to quickly shunt $\text{V}_\text{out}$ to ground (see Fig.~\ref{Fig:MOS}).
 This circuit works by monitoring the voltage at $\text{V}_\text{MG}$, the mid-ground node controlled by op-amp U2.
-If that voltage drops below a threshold set by $\text{V}_\text{TH}$, the comparator op-amp in Figure~\ref{Fig:MOS} changes the gate voltage of the MOSFET to put it into conduction.
+If that voltage drops below a threshold set by $\text{V}_\text{TH}$, the comparator op-amp in Fig.~\ref{Fig:MOS} changes the gate voltage of the MOSFET to put it into conduction.
 The time constant for this configuration is given by $\tau \approx R_\text{MOS}\text{C}_\text{out}$.
-For our circuit, this changes $\tau$ to $\approx\SI{1}{\milli\second}$, allowing for the fast discharge of $\text{C}_\text{out}$.
+For our circuit, this changes $\tau$ to $\approx\SI{1}{\milli\second}$, allowing $\text{C}_\text{out}$ to be quickly discharged.
 The threshold is $\text{V}_\text{TH} = \SI{-10.4}{\volt}$, but other values could be chosen depending on the design requirements.
@@
 
-The modulation voltage $\text{V}_\text{mod}$ can be supplied either from a BNC on the frontpanel, or from the backplane.
+The modulation voltage $\text{V}_\text{mod}$ can be supplied either from a BNC on the frontpanel or from the backplane.
 This may be useful, e.g., with servo controllers that reside in the same rack as the other control electronics.
 In either case, this voltage is differentially buffered to break ground loops.
-An output voltage monitor (sensed at the inverting node of U2 in Figure~\ref{Fig:PiezoCircuit}, but not shown) is buffered and connected to a BNC on the frontpanel, an analog signal line on the backplane, and to the microcontroller\footnote{One drawback of this scheme is that the contribution of $\text{V}_\text{mod}$ is not sensed by the monitor.
+An output voltage monitor (sensed at the inverting node of U2 in Fig.~\ref{Fig:PiezoCircuit}, but not shown) is buffered and connected to a BNC on the frontpanel, an analog signal line on the backplane, and to the microcontroller\footnote{One drawback of this scheme is that the contribution of $\text{V}_\text{mod}$ is not sensed by the monitor.
 Future versions will instead monitor $\text{V}_\text{out}$ through a resistive divider, allowing the microcontroller to implement an infinite integrator and drive $\text{V}_\text{mod}$ to \SI{0}{\volt} in closed-loop operation.
 This will be a very useful feature to prevent the servo controller from railing.}.
-%This enables the microcontroller to digitally implement an infinite integrator, driving $\text{V}_\text{mod}$ to \SI{0}{\volt} in closed-loop operation and preventing the servo controller from railing.
 The backplane monitor could be fed to a low-noise current controller (e.g., one based on the design in~\cite{Erickson2008a}) to implement a laser diode current feed-forward.
@@
 \includegraphics[width=\columnwidth]{fig/NoiseModel.ai}
-\caption{Noise model (see text).
-The element labeled $Z_\text{LP}$ is comprised of a \SI{47}{\nano\farad} capacitor in parallel with a \SI{10}{\micro\farad} capacitor connected to ground through a switch, such that the corner frequency of the filter can be changed depending on the mode of operation.
+\caption{Noise model.
+The element labeled $\text{C}_\text{LP}$ is comprised of a \SI{47}{\nano\farad} capacitor in parallel with a \SI{10}{\micro\farad} capacitor connected to ground through a switch, such that the corner frequency of the filter can be changed depending on the mode of operation  (see text).
 %The on-resistance of the switch introduces a zero in the transfer function at $\approx\SI{23}{\kilo\hertz}$, which has negligible effect on the computed RMS noise.
@@
 \end{figure}
+
+We analyze the noise performance of the circuit according to the model shown in Fig.~\ref{Fig:NoiseModel}, where noise spectral densities are calculated at the node $\text{V}_\text{out}$.
+A summary of each noise contribution (op-amp, DAC, Johnson-Nyquist, and residual ripple from the DRV2700) is shown in Fig.~\ref{Fig:NoisePlot}, along with the cumulative root-mean-square (RMS) nose estimates in different frequency bands.
+We will neglect the ``modulation noise'' appearing at node $\text{V}_\text{mod}$, because its exact character depends on the external drive.
+
+To facilitate the noise analysis, we first calculate the voltage and current (transimpedance) gains from the input nodes of U2 to the output, $\text{V}_\text{out}$.
+Starting with the non-inverting node, we find the voltage gain to be
+\begin{align}
+G_{+}^{(v)} = 1 + Z_1\left(\frac{1}{R_2} + \frac{1}{Z_\text{mod}}\right)\,,
+\end{align}
+where $Z_1$ and $Z_\text{mod}$ are the equivalent impedances of $R_1~||~\text{C}_1$ and $R_\text{mod}~||~\text{C}_\text{mod}$, respectively.
+The transimpedance gain, $G^{(i)}_{+}$, follows by multiplying $G_+^{(v)}$ by the impedance, $Z_+$, seen from that node. % $Z_+ = R_\text{LP}~||~\text{C}_\text{LP}$ seen from that node.
+Thus,
+\begin{align}
+G_{+}^{(i)} = G_{+}^{(v)}\left[\frac{R_\text{LP}}{1+2\pi i f R_\text{LP} C_\text{LP}}\right]\,,
+\end{align}
+where the bracketed term is $Z_+$, and $f$ is the Fourier frequency.
 
@@
 DAC             &             \SI{28}{\micro\volt}    & \SI{8}{\micro\volt}       \\
-Johnson-Nyquist &             \SI{3}{\micro\volt}    & \SI{31}{\micro\volt}        \\ 
+Johnson-Nyquist &             \SI{3}{\micro\volt}    & \SI{14}{\micro\volt}        \\ 
+Residual switching &        \SI{3}{\micro\volt}   & \SI{8}{\micro\volt} \\
 \hline
-\rule{0pt}{2ex}\textbf{total (calculated)} & \SI{64}{\micro\volt} & \SI{86}{\micro\volt}  \\
+\rule{0pt}{2ex}\textbf{total (calculated)} & \SI{64}{\micro\volt} & \SI{82}{\micro\volt}  \\
 \hline\hline
@@
 Power spectral density (PSD) is referred to the high voltage output, and the table shows the integrated RMS noise due to each noise source in different frequency bands.
-The total RMS noise (summed in quadrature) over the entire \SI{1}{\hertz}~--~\SI{100}{\kilo\hertz} range is calculated to be \SI{107}{\micro\volt}.
+The total RMS noise (summed in quadrature) over the entire \SI{1}{\hertz}~--~\SI{100}{\kilo\hertz} range is calculated to be \SI{104}{\micro\volt}, with the residual switching noise measured at \SI{200}{\volt}.
+Frequency-dependent noise spectra for the DAC and op-amp were extracted from the datasheets.
 \label{Fig:NoisePlot}}
@@
 
-We analyze the noise performance of the circuit according to the model shown in Fig.~\ref{Fig:NoiseModel}, where noise spectral densities are calculated at the node $\text{V}_\text{out}$.
-A summary of each noise contribution (op-amp, DAC, Johnson-Nyquist, residual DRV2700) is shown in Fig.~\ref{Fig:NoisePlot}, along with the cumulative root-mean-square (RMS) nose estimates in different frequency bands.
+We now calculate gains from the inverting node of U2.
+Because any currents appearing at this node will be cancelled by the feedback of U2, the transimpedance gain $G_{-}^{(i)}$ is simply the impedance $Z_1$, given by
+\begin{align}
+G_{-}^{(i)} = Z_1 \equiv \frac{R_1}{1+2\pi i f R_1 C_1}\,.
+\end{align}
+The voltage gain from this node is similarly given by
+\begin{align}
+G_{-}^{(v)} = -Z_1 \left(\frac{1}{R_2} + \frac{1}{Z_\text{mod}}\right)\,.
+\end{align}
+With these in hand, we can calculate the output noise contribution from each source in our model.
 
-To treat the intrinsic op-amp noise contributions, we first compute the noise gain $G_n$ for this amplifier configuration according to
-\begin{align}
-\label{Eq:NG}
-G_n(s) &= 1 + Z_1\left(\frac{1}{R_2} + \frac{1}{Z_\text{mod}}\right)\,,
-\end{align}
-with equivalent impedances $Z_1 = R_1/(1+R_1 C_1 s)$ and $Z_{\text{mod}} = R_{\text{mod}}/(1+R_{\text{mod}} C_{\text{mod}} s)$, and where $s$ is the Laplace variable.
-By design, we've chosen $Z_1 \equiv Z_{\text{mod}}$ such that the signal gain from the node $\text{V}_{\text{mod}}$ is unity.
-This reduces Eq.~(\ref{Eq:NG}) to
-\begin{align}
-\label{Eq:RedNG}
-G_n(s) &= 2 + \frac{Z_1}{R_2}\,.
-\end{align}
-
-The op-amp noise is parametrized by two noise contributions: $e_n$, the input voltage noise power spectral density (PSD), and $i_n$, the input current noise PSD.
+As shown in Fig.~\ref{Fig:NoiseModel}, the op-amp noise is parametrized by two noise contributions: $e_n$, the input voltage noise spectral density, and $i_n$, the input current noise spectral density.
 For the LM7171, $e_n = \SI[per-mode=symbol]{14}{\nano\volt\per\sqrthz}$ and $i_n = \SI[per-mode=symbol]{1.5}{\pico\ampere\per\sqrthz}$ at $\SI{10}{\kilo\hertz}$, with a $1/f$ noise character below this frequency~\cite{LM7171Datasheet}.
-The voltage noise is summed in at the non-inverting input, while the current noise is present at both inputs.
-To convert $i_n$ to an equivalent voltage noise $e_n$, we multiply by the impedances $Z_n$ and $Z_p$ seen by the inverting and non-inverting nodes, respectively.
-These are calculated as
+The voltage noise appears at the non-inverting input, while the current noise is present at both inputs.
+By multiplying each source by the appropriate gain, we obtain the equivalent output noise power spectral densities (PSD),
 \begin{align}
 \begin{split}
-\label{Eq:ZnZp}
-Z_n &\equiv \left(\frac{1}{Z_1} + \frac{1}{Z_\text{mod}} +  \frac{1}{R_2}\right)^{-1}   = \frac{Z_1 R_2}{2R_2 + Z_1} \\
-Z_p &\equiv \left(\frac{1}{R_\text{LP}} + \frac{1}{Z_\text{LP}}\right)^{-1}\,.
+e^2_{v,\text{U2}} &= \big|G_{+}^{(v)}\big|^2 e^2_n \\
+e^2_{i,\text{U2}} &= \big|G_{-}^{(i)}\big|^2 i^2_n + \big|G_{+}^{(i)}\big|^2 i^2_n\,,
 \end{split}
 \end{align}
-The impedance $Z_\text{LP}$ is determined by the corner frequency of a switchable low-pass filter between the DAC and the non-inverting node of U2 (discussed below).
-The total noise contribution of the op-amp U2 (referenced to the output) is
-\begin{align}
-\label{Eq:OpAmpNoise}
-e_{n,\text{U2}} &= G_n(s)\sqrt{e_n^2 + (Z_n i_n)^2 + (Z_p i_n)^2}\,.
-\end{align}
+where  $e^2_{v,\text{U2}}$, $e^2_{i,\text{U2}}$ are the output-referred voltage and current noise PSD, respectively.
 
-Next, we calculate the noise contribution from the DAC.
-The noise signal gain from the node $\text{V}_{\text{ctl}}$ is given by
+%To convert the current noise into an equivalent voltage noise referred to the output (RTO), we multiply by the transimpedance gain, $G_\pm$, seen from the relevant node.
+%For $i_n$ at the inverting node of U2, $G_-$ is simply the impedance $Z_1$ formed by $R_1$ in parallel with $C_1$,
+%\begin{align}
+%G_- = \frac{R_1}{1+2\pi i f R_1 C_1}
+%\end{align}
+%where $f$ is the frequency.
+%For current noise at the non-inverting node, we find
+%\begin{align}
+%%G_+ &= Z_\text{LP}\left(1+\frac{Z_1}{R_2~||~Z_\text{mod}}\right)
+%G_+ &= Z_\text{LP}\left[1+Z_1\left(\frac{1}{R_2} + \frac{1}{Z_\text{mod}}\right)\right]\,,
+%\end{align}
+%where $Z_\text{LP} = R_\text{LP}/(1+2\pi i f R_\text{LP} C_\text{LP})$ is the impedance of the switchable low-pass filter (discussed below) as seen from the non-inverting node of U2, and the term in brackets is the non-inverting voltage gain, $G_\text{pos}$.
+%With these values, we calculate the total op-amp noise contribution as
+%\begin{align}
+%e^2_{n,\text{U2}} &= e_n^2 \left|G_\text{pos}\right|^2 + i_n^2\left( \left|G_-\right|^2 + \left|G_+\right|^2\right)
+%\end{align}
+
+\begin{figure}[t]
+\includegraphics[width=\columnwidth]{fig/VoltagePSD.png}
+\caption{Voltage power spectral density at various output voltages.
+The integrated RMS voltage noise ($\SI{1}{\hertz} - \SI{100}{\kilo\hertz}$) is $\{138, 80, 101\}~\si{\micro\volt}$ measured at  $\{50, 100, 200\}~\si{\volt}$, with no output load.
+\label{Fig:PSD}}
+\end{figure}
+
+Next, we calculate the DAC noise contribution.
+The voltage gain from the node $\text{V}_{\text{ctl}}$ is given by
 \begin{align}
 \label{Eq:Gdc}
-G_{\text{ctl}} &= \left(\frac{Z_\text{LP}}{R_\text{LP} + Z_\text{LP}}\right)G_n(s)\,,
+G^{(v)}_{\text{ctl}} &= \left(\frac{1}{1+2\pi i f R_\text{LP} C_\text{LP}}\right)G_{+}^{(v)}\,,
 \end{align}
@@
 The non-zero resistance of the switch contributes a zero to the transfer function at $\approx\SI{23}{\kilo\hertz}$, but has negligible effect on the performance.
-The DAC voltage noise contribution can now be calculated as $e_{n,\text{DAC}} = G_{\text{ctl}} v_{n,\text{DAC}}$, where $v_{n,\text{DAC}}$ is the frequency dependent output voltage noise of the DAC. 
-In subsequent calculations, we take the DC mode operation for the switchable low-pass filter.
-%The DAC used in our design (Analog devices, AD5663R) has a white noise floor of \SI[per-mode=symbol]{100}{\nano\volt\per\sqrthz} with an $\approx\SI{1}{\kilo\hertz}$ corner frequency.
+The DAC voltage noise contribution can now be calculated as 
+\begin{align}
+e^2_{n,\text{DAC}} = \big|G^{(v)}_{\text{ctl}}\big|^2 v^2_{n,\text{DAC}}\,,
+\end{align}
+where $v_{n,\text{DAC}}$ is the frequency dependent output voltage noise of the DAC\cite{AD56XXRDatasheet}. 
+In subsequent calculations, we take the DC-mode operation for the switchable low-pass filter.
 
-The low-noise stabilization circuit is limited in its ability to reject residual switching noise from the DRV2700 regulator and passive filtering by the total loop gain analyzed from node $\text{V}_\text{out}$.
-The LM7171 has an open-loop gain of \SI{85}{\decibel} ($\approx 1.8\times 10^4$), with a dominant pole at $\approx\SI{10}{\kilo\hertz}$\cite{LM7171Datasheet}.
-We model the open loop gain, $G_\text{OL}$, as
-\begin{align}
-G_\text{OL} &= \frac{1.8\times10^4}{1+s/(2\pi\cdot\SI{10}{\kilo\hertz})}\,.
-\end{align}
-The contribution of this residual switching noise, $v_{n,\text{DRV}}$, to the output is given by
-\begin{align}
-e_{n,\text{DRV}} &= \frac{v_{n,\text{DRV}}}{1+G_\text{OL}\left(\frac{R_2||Z_\text{mod}}{Z_1 + R_2||Z_\text{mod}}\right)}\,.
-\end{align}
-For $R_1=\SI{1}{\mega\ohm}$ and $\text{C}_1 = \SI{1}{\nano\farad}$, $v_{n,\text{DRV}}$ is attenuated by as much as \SI{76}{\decibel} at \SI{6.3}{\kilo\hertz}, with a rolloff of \SI[per-mode=symbol]{10}{\decibel\per\text{decade}} at higher frequencies.
-(INCLUDE DRV NOISE MODEL IN CALCULATION?? -- EG, WHAT ORDER DO THEY CONTRIBUTE?)
-
-% such that the closed-loop gain for noise contributed by the flyback regulator at node $\text{V}_\text{out}$ is minimized in the \SIrange{40}{100}{\kilo\hertz} switching noise band.
-%For $R_1=\SI{1}{\mega\ohm}$, we choose $\text{C}_1=\SI{1}{\nano\farad}$.
-%The noise gain
-
-Given the noise model discussed above, our circuit is dominated by Johnson noise at intermediate to high frequencies, and the op-amp's intrinsic current noise at lower frequencies.
-Both of these contributions could be suppressed by using lower resistances $R_1$ and $R_\text{mod}$, however one must be careful about power and current limitations when dealing with such high voltages.
-Each noise source is tabulated and plotted in Fig.~\ref{Fig:NoisePlot}, and the total voltage noise  is calculated to be $\SI{107}{\micro\volt}$ ($\SI{1}{\hertz} - \SI{100}{\kilo\hertz}$).
-Frequency-dependent input noise parameters in this model were extracted from datasheet spectral density curves\cite{SHEETS}.
-
-\section{Results}
-\label{Sec:Results}
-\begin{figure}[t]
-\includegraphics[width=\columnwidth]{fig/VoltagePSD.pdf}
-\caption{Voltage power spectral density at various output voltages.
-The integrated RMS voltage noise ($\SI{1}{\hertz} - \SI{100}{\kilo\hertz}$) is $\{138, 80, 101\}~\si{\micro\volt}$ measured at  $\{50, 100, 200\}~\si{\volt}$, with no output load.
-\label{Fig:PSD}}
-\end{figure}
-
-The measured performance of the high-voltage piezo driver is shown in Fig.~\ref{Fig:PSD}, where we plot the noise power spectral density measured at several different output voltages.
-These traces were taken on a Stanford Research Systems SR780 spectrum analyzer, with the high-voltage output coupled through a \SI{0.5}{\hertz} high-pass filter and without any capacitive load.
-This represents a worst-case scenario, as larger capacitances at the output will reduce the noise.
-The integrated noise ($\SI{1}{\hertz} - \SI{100}{\kilo\hertz}$) was measured to be $\{\SI{138}{\micro\volt}_\text{RMS},~\SI{80}{\micro\volt}_\text{RMS},~\SI{101}{\micro\volt}_\text{RMS}\}$ for \{\SI{50}{\volt}, \SI{100}{\volt}, \SI{200}{\volt}\} outputs.
-This matches well with the expected total RMS noise calculated in Section~\ref{Sec:NoiseAnalysis}.
-DISCUSS WHY 50V IS WORSE
-
-Figure~\ref{Fig:TimeDomain} shows the performance at both short- and long-time scales.
-At long times, voltage fluctuations on the order of a few \si{\milli\volt} can be observed.
-This is due generically to $1/f$ noise, but also correlates with the external temperature.
-A cross-correlation between measured temperature and output voltage (trace not shown) yields an effective temperature coefficient of \SI[per-mode=symbol]{-24}{ppm\per\celsius} at \SI{100}{\volt}.
-The short-term trace was taken on a PicoScope~5442B (ac-coupled, \SI{100}{\volt} output).
-Points are colored based on their normally distributed statistical probability, and thus give a visual estimation of the RMS width.
-
-\begin{figure}[t]
-\includegraphics[width=\columnwidth]{fig/TimeDomain.pdf}
+\begin{figure}[b]
+\includegraphics[width=\columnwidth]{fig/TimeDomain.png}
 \caption{Time-domain traces of the high voltage output (\SI{100}{\volt}).
@@
 
-Figure~\ref{Fig:TransferFunc} shows the measured frequency response under different load conditions.
-The unloaded bandwidth is as high as a few megahertz, while a \SI{1}{\micro\farad} capacitive load can still be driven at $\approx\SI{100}{\kilo\hertz}$.
-Several mechanical resonances can be seen with a \SI{700}{\nano\farad} piezoelectric load, as expected.
-In a laboratory setting, these resonances can be mitigated by using a digital feedback controller with notch filters tuned to match the exact resonance frequencies observed in the system\cite{Ryou2016a}, thereby extending the usable bandwidth out to $\approx\SI{100}{\kilo\hertz}$.
+The Johnson noise contribution can be calculated by modeling each resistor with a parallel current noise given by $i_\text{R}^2 = 4k_B T/R$.
+Resistors $R_1$, $R_2$, and $R_\text{mod}$ all contribute current noise at the inverting node of U2, which as discussed previously has a transimpedance gain to the output given by $G_{-}^{(i)}$.
+The resistor $R_\text{LP}$ contributes current noise at the non-inverting node, which sees a transimpedance gain $G_{+}^{(i)}$.
+Thus, the total Johnson noise is
+\begin{align}
+\begin{split}
+e^2_{n,\text{JN}} &= 4 k_B T \times \\
+&\left[ \big|G_{-}^{(i)}\big|^2 \left(\frac{1}{R_1} + \frac{1}{R_2} + \frac{1}{R_\text{mod}} \right) + 
+\frac{\big|G_{+}^{(i)}\big|^2}{R_\text{LP}} \right]
+\end{split}
+\end{align}
+
+The low-noise stabilization circuit is limited in its ability to reject residual switching noise from the DRV2700 regulator (after the passive filtering network) by the total loop gain analyzed from node $\text{V}_\text{out}$.
+The LM7171 has a reported open-loop gain of \SI{85}{\decibel} ($\approx 1.8\times 10^4$), with a dominant pole at $\approx\SI{10}{\kilo\hertz}$\cite{LM7171Datasheet}.
+We can model the open loop gain, $G_\text{OL}$, as
+\begin{align}
+G_\text{OL} &= \frac{1.8\times10^4}{1 + i (f/\SI{10}{\kilo\hertz})}\,.
+\end{align}
+The feedback network contributes a gain
+\begin{align}
+G_\text{FB} = \frac{R_2~||~Z_\text{mod}}{Z_1 + R_2~||~Z_\text{mod}}\,,
+\end{align}
+arising from the voltage partition between $\text{V}_\text{out}$ and the inverting node of U2.
+From these, we write down the closed-loop gain seen from $\text{V}_\text{U2}$,
+\begin{align}
+G^{(\text{DRV})} = \frac{1}{1+G_\text{OL} G_\text{FB}}\,.
+\end{align}
+The contribution to the output from residual switching noise, $v_{n,\text{DRV}}$, is then
+\begin{align}
+e^2_{n,\text{DRV}} = v^2_{n,\text{DRV}}\big|G^{(\text{DRV})}\big|^2\,.
+\end{align}
+For $R_1=\SI{1}{\mega\ohm}$ and $\text{C}_1 = \SI{1}{\nano\farad}$, $v_{n,\text{DRV}}$ is attenuated by as much as \SI{76}{\decibel} at \SI{6.3}{\kilo\hertz}.
+
+A good estimate of the noise spectral density $v_{n,\text{DRV}}$ can be obtained by measuring the voltage power spectrum at node $\text{V}_\text{U2}$ in Fig.~\ref{Fig:NoiseModel}, since the output of this op-amp represents the control signal required to cancel voltage fluctuations at $\text{V}_\text{out}$.
+The trace plotted in Fig.~\ref{Fig:NoisePlot} assumes $v_{n,\text{DRV}}$ given by this measurement. 
+Because the noise floor of our instrument crosses the measurement trace at $\approx\SI{10}{\kilo\hertz}$, we only plot out to that frequency.
+
+% such that the closed-loop gain for noise contributed by the flyback regulator at node $\text{V}_\text{out}$ is minimized in the \SIrange{40}{100}{\kilo\hertz} switching noise band.
+%For $R_1=\SI{1}{\mega\ohm}$, we choose $\text{C}_1=\SI{1}{\nano\farad}$.
+%The noise gain
+
+Given the noise model discussed above, our circuit is dominated by the op-amp's intrinsic current noise at lower frequencies, and voltage noise at higher frequencies.
+The op-amp current noise contribution could be suppressed by using lower resistances $R_1$ and $R_\text{mod}$, however one must be careful about power and current limitations when dealing with such high voltages.
+Each noise source is tabulated and plotted in Fig.~\ref{Fig:NoisePlot}, and the total voltage noise  is calculated to be $\SI{104}{\micro\volt}$ ($\SI{1}{\hertz} - \SI{100}{\kilo\hertz}$, $\text{V}_\text{out} = \SI{200}{\volt}$).
+Frequency-dependent input noise parameters in this model were extracted from datasheet spectral density curves\cite{LM7171Datasheet,AD56XXRDatasheet}, and measured for the residual DRV2700 noise $v_{n,\text{DRV}}$ as discussed above.
+At lower voltages, the residual ripple from the DRV2700 begins to dominate the noise performance.
+This can be seen in Fig.~\ref{Fig:NoisePerformance}, as the characteristic shape changes between \SI{100}{\volt} and \SI{50}{\volt}.
+%say more here??
+
+\section{Results}
+\label{Sec:Results}
+
 \begin{figure}[t]
-\includegraphics[width=\columnwidth]{fig/PiezoModulationTransfer.pdf}
+\includegraphics[width=\columnwidth]{fig/PiezoModulationTransfer.png}
 \caption{Modulation input transfer function (color online).
@@
 
+The measured performance of the high-voltage piezo driver is shown in Fig.~\ref{Fig:PSD}, where we plot the noise power spectral density measured at several different output voltages.
+These traces were taken on a Stanford Research Systems SR780 spectrum analyzer, with the high-voltage output coupled through a \SI{0.5}{\hertz} high-pass filter and without any capacitive load.
+This represents a worst-case scenario, as larger capacitances at the output will reduce the noise.
+The integrated noise ($\SI{1}{\hertz} - \SI{100}{\kilo\hertz}$) was measured to be $\{\SI{138}{\micro\volt}_\text{RMS},~\SI{80}{\micro\volt}_\text{RMS},~\SI{101}{\micro\volt}_\text{RMS}\}$ for \{\SI{50}{\volt}, \SI{100}{\volt}, \SI{200}{\volt}\} outputs.
+This matches well with the expected total RMS noise calculated in Sec.~\ref{Sec:NoiseAnalysis}.
+The difference in noise performance at different output voltages can be traced back to the residual ripple of the DRV2700, which counterintuitively is larger for lower output voltages.
+
+Fig.~\ref{Fig:TimeDomain} shows the performance at both short- and long-time scales.
+At long times, voltage fluctuations on the order of a few \si{\milli\volt} can be observed.
+This is due generically to $1/f$ noise, but also correlates with the external temperature.
+A cross-correlation between measured temperature and output voltage (trace not shown) yields an effective temperature coefficient of \SI[per-mode=symbol]{-24}{ppm\per\celsius} at \SI{100}{\volt}.
+The short-term trace was taken on a PicoScope~5442B (AC-coupled, \SI{100}{\volt} output).
+Points are colored based on their normally distributed statistical probability, and thus give a visual estimation of the RMS width.
+
+Fig.~\ref{Fig:TransferFunc} shows the measured frequency response under different load conditions.
+The unloaded bandwidth is as high as a few megahertz, while a \SI{1}{\micro\farad} capacitive load can still be driven at $\approx\SI{100}{\kilo\hertz}$.
+Several mechanical resonances can be seen with a \SI{700}{\nano\farad} piezoelectric load, as expected.
+In a laboratory setting, these resonances can be mitigated by using a digital feedback controller with notch filters tuned to match the exact resonance frequencies observed in the system\cite{Ryou2016a}, thereby extending the usable bandwidth out to $\approx\SI{100}{\kilo\hertz}$.
+
 \section{Conclusion}
@@
 It is based on a flyback configuration switching regulator, but is able to achieve very low noise performance by active stabilization from a high slew-rate op-amp.
-This hybrid architecture makes it small and easy to deploy in a variety of situations, without requiring an external, bulky high-voltage power supply.
+This hybrid architecture makes it small and easy to deploy in a variety of situations, without requiring an external high-voltage power supply.
 The design principles discussed here can be adapted to fit the exact application, and all design files are freely available on GitHub for others to use and modify.
@@
 % Create the reference section using BibTeX:
-%\bibliographystyle{jabbrv_abbr}
+%\bibliographystyle{plain}
 \bibliography{references}

### 2016-07-31 piezo.tex
Added all calculations; hopefully final draft
* Cleaned up calculation/figure scripts, added raw data, etc.
* updated .gitignore for temp files
* exported references.bib such that it only contains relevant entries

@@
 
-%\usepackage[warnundef]{jabbrv}
-
 \usepackage{siunitx}
@@
 \usepackage{multirow}
-%\usepackage{caption}
-%\usepackage{subcaption}
-
-% \usepackage{aastex}
-%\usepackage{natbib}
 \usepackage{hyperref}
@@
 
-% Use the \preprint command to place your local institutional report number
-% on the title page in preprint mode.
-% Multiple \preprint commands are allowed.
-%\preprint{}
-
 \title{An ultra-low noise, high-voltage piezo driver}
-
-% repeat the \author .. \affiliation  etc. as needed
-% \email, \thanks, \homepage, \altaffiliation all apply to the current author.
-% Explanatory text should go in the []'s,
-% actual e-mail address or url should go in the {}'s for \email and \homepage.
-% Please use the appropriate macro for the type of information
-
-% \affiliation command applies to all authors since the last \affiliation command.
-% The \affiliation command should follow the other information.
 
@@
 \author{G.K. Campbell}
-%\homepage[]{Your web page}
-%\thanks{}
-%\altaffiliation{}
 \affiliation{Joint Quantum Institute, University of Maryland and National Institute of Standards and Technology}
-
-% Collaboration name, if desired (requires use of superscriptaddress option in \documentclass).
-% \noaffiliation is required (may also be used with the \author command).
-%\collaboration{}
-%\noaffiliation
 
@@
 The architecture uses a flyback switching regulator to generate up to 250V in our current design, with an output of \SI{1}{\kilo\volt} or more possible with small modifications. 
-%A high slew-rate op-amp suppresses the switching noise by XX dB (MEASURE), yielding a total RMS noise of $\approx\SI{100}{\micro\volt}$ (\SI{1}{\hertz}--\SI{100}{\kilo\hertz}).
 A high slew-rate op-amp suppresses the residual switching noise, yielding a total RMS noise of $\approx\SI{100}{\micro\volt}$ (\SI{1}{\hertz}--\SI{100}{\kilo\hertz}).
@@
 
-% Body of paper goes here. Use proper sectioning commands.
-% References should be done using the \cite and \label commands
 \section{Introduction}
@@
 For example, piezo-actuated mirrors and diffraction gratings play an important role in atomic physics experiments (used, e.g., in Fabry-Per{\`o}t cavities\cite{Riedle1994a,Bohlouli-Zanjani2006a} and extended-cavity diode lasers\cite{Wieman1991a}), while avalanche photodiodes and photomultiplier tubes require large bias voltages for proper operation.
-% Huber2014a -- Ba+ paper with micro-positioning mirror??
 In the realm of biophysics, electrokinetic separation methods such as free-flow or capillary electrophoresis\cite{Kohlheyer2008a} require large electric field gradients, and the recent push to develop lab-on-a-chip devices could benefit from miniaturized high voltage sources\cite{Temiz2015a}.
@@
 Additionally, the high-voltage output remains single-ended and referenced to ground, allowing it to drive piezo actuators with a grounded terminal.
-%Additionally, the high-voltage output is single-ended and referenced to ground, allowing it to drive piezo actuators with a grounded terminal.
-In Sec.~\ref{Sec:NoiseAnalysis} we present a noise analysis, and show characteristic performance data in Sec.~\ref{Sec:Results}.
-Complete design files, including the schematic, bill of materials, and board layout, can be found on Github\cite{DesignFiles}.
+We present a noise analysis of our circuit in Sec.~\ref{Sec:NoiseAnalysis}, and show characteristic performance data in Sec.~\ref{Sec:Results}.
+Complete design files, including the schematic, bill of materials, and board layout, can be found on Github\cite{PiezoDesignFiles}.
 The board manufacture and component cost is less than \SI{200}[\$]{}, making it a cost-effective alternative to commercial options.
-% Mention other features?
-
-%The high voltage setpoint is digitally controlled, and can be swept over \SI{200}{\volt} at \approx\SI{10}{\hertz}.
 
@@
 The voltage $\text{V}_\text{HV}$ is generated using a Texas Instruments DRV2700 high voltage driver in flyback configuration.
-A high slew-rate op-amp (U2) senses the output voltage across $R_1$ and $R_2$, and servos it by modulating the node at ``HV floating gnd''.
+A high slew-rate op-amp (U2) senses the output voltage across $R_1$ and $R_2$, and servos it by modulating the mid-ground node $\text{V}_\text{MG}$.
 The DC control signal for this op-amp,  $\text{V}_{\text{ctl}}$, is supplied by a digital-to-analog (DAC) converter, which is passed through a switchable low-pass filter.
 This allows for very heavy filtering of the DAC $1/f$ noise during steady-state operation, but the corner frequency can be increased if the output needs to be scanned more quickly.
-The $\text{V}_{\text{ctl}}$ gain is set by $\left(1+R_1/R_2\right)$, while the modulation gain is set by $-R_{\text{mod}}/R_1$.
+The $\text{V}_{\text{ctl}}$ gain is set by $\left(1+R_1/R_2\right)$, while the modulation gain is set by $-R_1/R_\text{mod}$.
 The capacitor linking the floating ground node to the output allows the op-amp to remove residual switching noise and stabilize the DC output according to the transfer function given in Eq.~(\ref{Eq:FullTransferFunc}).
@@
 To improve the large-voltage slew rate, a MOSFET ``quench'' circuit (Fig.~\ref{Fig:MOS}) is included to shorten the $RC$ time constant of the high voltage node $\text{V}_\text{HV}$ when needed.
-A switchable corner low-pass filter can be engaged during DC operation to reduce $1/f$ noise from the DAC (discussed in Sec.~\ref{Sec:NoiseAnalysis}), and
+A switchable-corner, low-pass filter can be engaged during DC operation to reduce $1/f$ noise from the DAC (discussed in Sec.~\ref{Sec:NoiseAnalysis}), and
 %Because $1/f$ voltage noise in the DAC contributes heavily to the output noise, a low-pass filter can be engaged during DC operation to mitigate this output noise (discussed in Sec.~\ref{Sec:NoiseAnalysis}).
@@
 The high voltage DC-DC converter used here is based on the Texas Instruments DRV2700 piezo driver\footnote{The identification of commercial products in this paper is for information only and does not imply recommendation or endorsement by the National Institute of Standards and Technology.}.
-This single-chip integrated circuit (IC) can be operated as a boost converter to drive an on-chip differential amplifier up to \SI{100}{\volt}, or as a flyback converter up to \SI{1}{\kilo\volt} or more.
+This single-chip integrated circuit can be operated as a boost converter to drive an on-chip differential amplifier up to \SI{100}{\volt}, or as a flyback converter up to \SI{1}{\kilo\volt} or more.
 In flyback configuration, the internal-boost switch of the DRV2700 (pin SW in Fig.~\ref{Fig:PiezoCircuit}) drives a step-up transformer.
@@
 \text{V}_\text{out} &= \left(1 + \frac{R_1}{R_2~||~R_\text{mod}}\right) \text{V}_\text{ctl} -
-\left(\frac{R_\text{mod}}{R_1}\right) \text{V}_\text{mod}\,.
+\left(\frac{R_1}{R_\text{mod}}\right) \text{V}_\text{mod}\,.
 \label{Eq:FullTransferFunc}
@@
 al.~\cite{Seifert2009a} characterized $1/f$ noise in a variety of resistors, and found that the Vishay TNPW \SI{0.1}{\percent}-series resistors showed a noise spectrum almost consistent with Johnson noise down to \SI{1}{\hertz}.
-Our current design uses this series in a 1206 package, but we noticed substantial low-frequency noise correlated with varying strain on the PCB, potentially due to the relatively large footprint of this package.
+Our current design uses this series in a 1206 package, but we noticed low-frequency noise correlated with varying strain on the PCB, potentially due to the relatively large footprint of this package.
 Future boards will instead use three TNPW \SI{0.1}{\percent} 0603 resistors in series for both R1 and R2 to minimize strain-induced output noise.
-%A previous iteration of this design used Panasonic ERJ-8ENF resistors (1206, \SI{1}{\percent}), and we noticed substantial low-frequency noise correlated with varying strain on the PCB.
-%This is consistent with the findings in Seifert, which showed this Panasonic series to exhibit voltage noise two orders of magnitude larger than the TNPW series at \SI{1}{\hertz}.
 
@@
 For our circuit, this means $\text{C}_\text{mod} = \text{C}_1$.
-
-%
-%The LM7171 has an open-loop gain of \SI{85}{\decibel}, with a dominant pole at $\approx\SI{10}{\kilo\hertz}$.
-%We thus model the open loop gain, $A_\text{OL}$, as
-%\begin{align}
-%A_\text{OL} &= \frac{10^{85/20}}{1+s/(2\pi\cdot\SI{10}{\kilo\hertz})}
-%\end{align}
-%Thus, noise appearing at $\text{V}_\text{out}$ is attenuated by a factor
-%\begin{align}
-%\frac{1}{1+A_\text{OL}\left(\frac{R_2||Z_\text{mod}}{Z_1 + R_2||Z_\text{mod}}\right)}
-%\end{align}
-%where $Z_1, Z_\text{mod}$ are the equivalent impedances of $R_1||\text{C}_1$ and $R_\text{mod}||\text{C}_\text{mod}$, respectively.
-%For $R_1=\SI{1}{\mega\ohm}$, choosing $\text{C}_1 = \SI{1}{\nano\farad}$ 
-%
-% such that the closed-loop gain for noise contributed by the flyback regulator at node $\text{V}_\text{out}$ is minimized in the \SIrange{40}{100}{\kilo\hertz} switching noise band.
-%For $R_1=\SI{1}{\mega\ohm}$, we choose $\text{C}_1=\SI{1}{\nano\farad}$.
-%The noise gain
 
@@
 This will be a very useful feature to prevent the servo controller from railing.}.
-The backplane monitor could be fed to a low-noise current controller (e.g., one based on the design in~\cite{Erickson2008a}) to implement a laser diode current feed-forward.
+The backplane monitor could be fed to a low-noise current controller (e.g., one based on the design in Erickson, et. al.~\cite{Erickson2008a}) to implement a laser diode current feed-forward.
 The high voltage output is interlocked with another signal on the backplane, which can optionally be bypassed by placing an onboard jumper, permitting easy integration with existing laboratory interlock schemes if desired.
-Further details on the design features discussed in this section, including sample software, can be found on Github~\cite{DesignFiles}.
+Further details on the design features discussed in this section, including sample software, can be found on Github~\cite{PiezoDesignFiles}.
 
@@
 \subfloat{
-\includegraphics[width=\columnwidth]{fig/NoiseContrib.pdf}
+\includegraphics[width=\columnwidth]{fig/NoiseContrib.png}
 }
@@
 Johnson-Nyquist &             \SI{3}{\micro\volt}    & \SI{14}{\micro\volt}        \\ 
-Residual switching &        \SI{3}{\micro\volt}   & \SI{8}{\micro\volt} \\
+Residual switching &        \SI{15}{\micro\volt}   & \SI{43}{\micro\volt} \\
 \hline
-\rule{0pt}{2ex}\textbf{total (calculated)} & \SI{64}{\micro\volt} & \SI{82}{\micro\volt}  \\
+\rule{0pt}{2ex}\textbf{total (calculated)} & \SI{66}{\micro\volt} & \SI{92}{\micro\volt}  \\
 \hline\hline
@@
 Power spectral density (PSD) is referred to the high voltage output, and the table shows the integrated RMS noise due to each noise source in different frequency bands.
-The total RMS noise (summed in quadrature) over the entire \SI{1}{\hertz}~--~\SI{100}{\kilo\hertz} range is calculated to be \SI{104}{\micro\volt}, with the residual switching noise measured at \SI{200}{\volt}.
+The total RMS noise (summed in quadrature) over the entire \SI{1}{\hertz}~--~\SI{100}{\kilo\hertz} range is calculated to be \SI{113}{\micro\volt}, with the residual switching noise measured at \SI{100}{\volt}.
 Frequency-dependent noise spectra for the DAC and op-amp were extracted from the datasheets.
@@
 where  $e^2_{v,\text{U2}}$, $e^2_{i,\text{U2}}$ are the output-referred voltage and current noise PSD, respectively.
-
-%To convert the current noise into an equivalent voltage noise referred to the output (RTO), we multiply by the transimpedance gain, $G_\pm$, seen from the relevant node.
-%For $i_n$ at the inverting node of U2, $G_-$ is simply the impedance $Z_1$ formed by $R_1$ in parallel with $C_1$,
-%\begin{align}
-%G_- = \frac{R_1}{1+2\pi i f R_1 C_1}
-%\end{align}
-%where $f$ is the frequency.
-%For current noise at the non-inverting node, we find
-%\begin{align}
-%%G_+ &= Z_\text{LP}\left(1+\frac{Z_1}{R_2~||~Z_\text{mod}}\right)
-%G_+ &= Z_\text{LP}\left[1+Z_1\left(\frac{1}{R_2} + \frac{1}{Z_\text{mod}}\right)\right]\,,
-%\end{align}
-%where $Z_\text{LP} = R_\text{LP}/(1+2\pi i f R_\text{LP} C_\text{LP})$ is the impedance of the switchable low-pass filter (discussed below) as seen from the non-inverting node of U2, and the term in brackets is the non-inverting voltage gain, $G_\text{pos}$.
-%With these values, we calculate the total op-amp noise contribution as
-%\begin{align}
-%e^2_{n,\text{U2}} &= e_n^2 \left|G_\text{pos}\right|^2 + i_n^2\left( \left|G_-\right|^2 + \left|G_+\right|^2\right)
-%\end{align}
 
@@
 arising from the voltage partition between $\text{V}_\text{out}$ and the inverting node of U2.
-From these, we write down the closed-loop gain seen from $\text{V}_\text{U2}$,
+From these, we write down the closed-loop gain seen from $\text{V}_\text{out}$,
 \begin{align}
@@
 The op-amp current noise contribution could be suppressed by using lower resistances $R_1$ and $R_\text{mod}$, however one must be careful about power and current limitations when dealing with such high voltages.
-Each noise source is tabulated and plotted in Fig.~\ref{Fig:NoisePlot}, and the total voltage noise  is calculated to be $\SI{104}{\micro\volt}$ ($\SI{1}{\hertz} - \SI{100}{\kilo\hertz}$, $\text{V}_\text{out} = \SI{200}{\volt}$).
+Each noise source is tabulated and plotted in Fig.~\ref{Fig:NoisePlot}, and the total voltage noise  is calculated to be $\SI{113}{\micro\volt}$ ($\SI{1}{\hertz} - \SI{100}{\kilo\hertz}$, $\text{V}_\text{out} = \SI{100}{\volt}$).
 Frequency-dependent input noise parameters in this model were extracted from datasheet spectral density curves\cite{LM7171Datasheet,AD56XXRDatasheet}, and measured for the residual DRV2700 noise $v_{n,\text{DRV}}$ as discussed above.
 At lower voltages, the residual ripple from the DRV2700 begins to dominate the noise performance.
-This can be seen in Fig.~\ref{Fig:NoisePerformance}, as the characteristic shape changes between \SI{100}{\volt} and \SI{50}{\volt}.
-%say more here??
+This can be seen in Fig.~\ref{Fig:PSD}, as the characteristic shape changes between \SI{100}{\volt} and \SI{50}{\volt}.
 
@@
 The integrated noise ($\SI{1}{\hertz} - \SI{100}{\kilo\hertz}$) was measured to be $\{\SI{138}{\micro\volt}_\text{RMS},~\SI{80}{\micro\volt}_\text{RMS},~\SI{101}{\micro\volt}_\text{RMS}\}$ for \{\SI{50}{\volt}, \SI{100}{\volt}, \SI{200}{\volt}\} outputs.
-This matches well with the expected total RMS noise calculated in Sec.~\ref{Sec:NoiseAnalysis}.
+This matches roughly with the expected total RMS noise calculated in Sec.~\ref{Sec:NoiseAnalysis}.
 The difference in noise performance at different output voltages can be traced back to the residual ripple of the DRV2700, which counterintuitively is larger for lower output voltages.
+The additional low-frequency $1/f$ noise present at \SI{200}{\volt} we suspect is due to some voltage-dependent noise source not considered in our model.
 

### 2016-08-02 piezo.tex
Finished latest round of paper torture comments, sending back for one final review

@@
 \newcommand{\prb}{Phys. Rev. B}
+\newcommand{\iu}{\mathrm{i}\mkern1mu}
 
@@
 \begin{abstract}
-We present an ultra-low noise, high voltage driver suited for use with piezoelectric actuators and other low-current applications. 
+We present an ultra-low noise, high-voltage driver suited for use with piezoelectric actuators and other low-current applications. 
 The architecture uses a flyback switching regulator to generate up to 250V in our current design, with an output of \SI{1}{\kilo\volt} or more possible with small modifications. 
@@
 A low-voltage (\SI{\pm 10}{\volt}), high bandwidth signal can be summed with unity gain directly onto the output, making the driver well-suited for closed-loop feedback applications.
-Digital control enables repeatable setpoints or sophisticated control logic, and the circuit consumes less than \SI{150}{\milli\ampere} at $\pm\SI{15}{\volt}$.
+Digital control enables both repeatable setpoints and sophisticated control logic. 
+The circuit consumes less than \SI{150}{\milli\ampere} at $\pm\SI{15}{\volt}$.
 \end{abstract}
@@
 Many instrumentation applications in the modern laboratory require agile, low-noise voltage sources capable of supplying hundreds of volts or more.
-For example, piezo-actuated mirrors and diffraction gratings play an important role in atomic physics experiments (used, e.g., in Fabry-Per{\`o}t cavities\cite{Riedle1994a,Bohlouli-Zanjani2006a} and extended-cavity diode lasers\cite{Wieman1991a}), while avalanche photodiodes and photomultiplier tubes require large bias voltages for proper operation.
-In the realm of biophysics, electrokinetic separation methods such as free-flow or capillary electrophoresis\cite{Kohlheyer2008a} require large electric field gradients, and the recent push to develop lab-on-a-chip devices could benefit from miniaturized high voltage sources\cite{Temiz2015a}.
+For example, piezo-actuated mirrors and diffraction gratings play an important role in atomic physics experiments (used, e.g., in Fabry-Per{\`o}t cavities\cite{Riedle1994a,Bohlouli-Zanjani2006a} and external-cavity diode lasers\cite{Wieman1991a}), while avalanche photodiodes and photomultiplier tubes require large bias voltages for proper operation.
+In the realm of biophysics, electrokinetic separation methods such as free-flow or capillary electrophoresis\cite{Kohlheyer2008a} require large electric field gradients.
+In addition, the recent push to develop lab-on-a-chip devices could benefit from miniaturized high-voltage sources.\cite{Temiz2015a}
 
@@
 For example, the frequency of an extended-cavity diode laser can be locked by feeding back to a piezo-actuated diffraction grating or mirror, which in turn supplies optical feedback to the diode.
-Commercially available piezoelectric drivers typically provide a modulation input for  such closed-loop applications, but the input voltage is gained such that it spans the entire output range of the device.
-While this has certain advantages, many applications would benefit from an architecture that provides a unity gain, DC-coupled feedback path to the high voltage output. 
+Commercially available piezoelectric drivers typically provide a modulation input for  such closed-loop applications, but  the input voltage is often gained such that it spans the entire output range of the device.
+While this has certain advantages, many applications would benefit from an architecture that provides a unity gain, DC-coupled feedback path to the high-voltage output. 
 Such a device could make closed-loop systems less susceptible to noise contributions from the servo controller, which we often find in our laboratory to be the limiting factor in laser lock stability.
@@
 While DC-DC converters are efficient and can work at very high voltages, they suffer from switching noise and limited control bandwidths.
-Linear-type devices are typically constructed from a high-voltage operational amplifier (op-amp), powered either from a high voltage linear regulator or more typically from a secondary switching converter.
+Linear-type devices are typically constructed from a high-voltage operational amplifier (op-amp), powered either from a high-voltage linear regulator or more typically from a secondary switching converter.
 While the op-amp provides \SI{100}{\decibel} or more of power-supply noise rejection, high-voltage op-amps require substantially more power than an equivalent switching circuit and are more cumbersome to deploy in the laboratory.
@@
 We present a noise analysis of our circuit in Sec.~\ref{Sec:NoiseAnalysis}, and show characteristic performance data in Sec.~\ref{Sec:Results}.
-Complete design files, including the schematic, bill of materials, and board layout, can be found on Github\cite{PiezoDesignFiles}.
+Complete design files, including the schematic, bill of materials, and board layout, can be found on Github.\cite{PiezoDesignFiles}
 The board manufacture and component cost is less than \SI{200}[\$]{}, making it a cost-effective alternative to commercial options.
@@
 \begin{figure*}[t]
-\includegraphics[width=\textwidth]{fig/DRV2700.ai}
+\includegraphics[width=\textwidth]{fig/Schematic.ai}
 \caption{Schematic of the high voltage supply and stabilization.
 The voltage $\text{V}_\text{HV}$ is generated using a Texas Instruments DRV2700 high voltage driver in flyback configuration.
-A high slew-rate op-amp (U2) senses the output voltage across $R_1$ and $R_2$, and servos it by modulating the mid-ground node $\text{V}_\text{MG}$.
+A high slew-rate op-amp (U2) senses the output voltage across $R_1$ and $R_2$, and controls it by modulating the mid-ground node $\text{V}_\text{MG}$.
 The DC control signal for this op-amp,  $\text{V}_{\text{ctl}}$, is supplied by a digital-to-analog (DAC) converter, which is passed through a switchable low-pass filter. 
-This allows for very heavy filtering of the DAC $1/f$ noise during steady-state operation, but the corner frequency can be increased if the output needs to be scanned more quickly.
+This design allows for very heavy filtering of the DAC $1/f$ noise during steady-state operation, but the corner frequency can be increased if the output needs to be scanned more quickly.
 The $\text{V}_{\text{ctl}}$ gain is set by $\left(1+R_1/R_2\right)$, while the modulation gain is set by $-R_1/R_\text{mod}$.
-The capacitor linking the floating ground node to the output allows the op-amp to remove residual switching noise and stabilize the DC output according to the transfer function given in Eq.~(\ref{Eq:FullTransferFunc}).
-Op-amps U1 and U2 are powered at $\pm\SI{15}{\volt}$ (not shown).
+The op-amp U2 removes residual switching noise and stabilizes the DC output according to the transfer function given in Eq.~(\ref{Eq:FullTransferFunc}).
+A MOSFET quench circuit, shown in Fig.~\ref{Fig:MOS}, connects at nodes $\text{V}_\text{out}$ and $\text{V}_\text{MG}$.
+%Op-amps U1 and U2 are powered at $\pm\SI{15}{\volt}$ (not shown).
 \label{Fig:PiezoCircuit}}
@@
 
-The design principles discussed below show how we leverage the versatility of galvanically isolated switching regulators in a low-noise laboratory environment. 
-Our design targets a \SI{250}{\volt} output, but straightforward modifications to the schematic (discussed below) make it possible to tailor the gain and output range to a specific application.
-The entire electronics package fits comfortably into a 12HP eurocard rack module (with the high voltage section taking only a fraction of the PCB), and draws less than \SI{150}{\milli\ampere} at \SI{15}{\volt}.
+The design principles discussed below show how we leverage the characteristics of a galvanically-isolated switching regulator without sacrificing the low-noise requirements of many laboratory applications.
+Our design targets a \SI{250}{\volt} output, but we discuss straightforward modifications to the schematic that make it possible to tailor the gain and output range to a specific application.
+The entire electronics package fits comfortably into a compact eurocard rack module (with the high-voltage section taking only a fraction of the PCB), and draws less than \SI{150}{\milli\ampere} at \SI{15}{\volt}.
 %The full schematic, including Gerbers, a bill of materials, and layout design files, can be found on GitHub.~\footnote{\protect\url{https://github.com/JQIamo/hv-piezo-driver}}
 
-Fig.~\ref{Fig:PiezoCircuit} shows the schematic overview. 
+Fig.~\ref{Fig:PiezoCircuit} shows an overview of the circuit schematic. 
 A digital-to-analog converter (DAC) generates a voltage setpoint, $\text{V}_\text{ctl}$, which is sent to the high-voltage flyback regulator and to the low-noise stabilization circuit.
-The flyback regulator (Sec.~\ref{Sec:DRV2700}) controls the potential between circuit nodes $\text{V}_\text{HV}$ and $\text{V}_\text{FG}$, while the low-noise stabilization circuitry (Sec.~\ref{Sec:LowNoiseStabilization}) servos the output node $\text{V}_\text{out}$ relative to the true circuit ground.
+The flyback regulator (Sec.~\ref{Sec:DRV2700}) controls the potential between circuit nodes $\text{V}_\text{HV}$ and $\text{V}_\text{FG}$, while the low-noise stabilization circuitry (Sec.~\ref{Sec:LowNoiseStabilization}) controls the output node $\text{V}_\text{out}$ relative to the true circuit ground.
 The DAC is controlled by an integrated microcontroller, and can be programmed to output slow ($\approx\SI{10}{\hertz}$) rail-to-rail voltage ramps in addition to setting the DC operating point (Sec.~\ref{Sec:SlowModulationMOS}).
-To improve the large-voltage slew rate, a MOSFET ``quench'' circuit (Fig.~\ref{Fig:MOS}) is included to shorten the $RC$ time constant of the high voltage node $\text{V}_\text{HV}$ when needed.
-A switchable-corner, low-pass filter can be engaged during DC operation to reduce $1/f$ noise from the DAC (discussed in Sec.~\ref{Sec:NoiseAnalysis}), and
-%Because $1/f$ voltage noise in the DAC contributes heavily to the output noise, a low-pass filter can be engaged during DC operation to mitigate this output noise (discussed in Sec.~\ref{Sec:NoiseAnalysis}).
-fast output modulation between $\pm\SI{10}{\volt}$ can be achieved through the input node $\text{V}_\text{mod}$.
-This node is DC-coupled to the high voltage output, and is useful for closed-loop feedback control.
+To improve the large-amplitude slew rate, a MOSFET ``quench'' circuit (Fig.~\ref{Fig:MOS}) is included to reduce the $RC$ time constant of the high-voltage node $\text{V}_\text{out}$ when needed.
+A low-pass filter with a switchable corner frequency can be engaged during DC operation to reduce $1/f$ noise from the DAC (discussed in Sec.~\ref{Sec:NoiseAnalysis}).
+Fast output modulation between $\pm\SI{10}{\volt}$ can be achieved through the input node $\text{V}_\text{mod}$.
+This node is DC-coupled to the high-voltage output, and is useful for closed-loop feedback control.
 
@@
 
-The high voltage DC-DC converter used here is based on the Texas Instruments DRV2700 piezo driver\footnote{The identification of commercial products in this paper is for information only and does not imply recommendation or endorsement by the National Institute of Standards and Technology.}.
-This single-chip integrated circuit can be operated as a boost converter to drive an on-chip differential amplifier up to \SI{100}{\volt}, or as a flyback converter up to \SI{1}{\kilo\volt} or more.
+The high-voltage DC-DC converter used here is based on the Texas Instruments DRV2700 piezo driver.\footnote{The identification of commercial products in this paper is for information only and does not imply recommendation or endorsement by the National Institute of Standards and Technology.}
+This integrated circuit can be operated as a boost converter to drive an on-chip differential amplifier up to \SI{100}{\volt}, or as a flyback converter up to \SI{1}{\kilo\volt} or more.
 In flyback configuration, the internal-boost switch of the DRV2700 (pin SW in Fig.~\ref{Fig:PiezoCircuit}) drives a step-up transformer.
-When the switch closes, current begins to flow through the primary coil of the transformer and induces a corresponding voltage across the secondary coil.
-In this state, the output diode is reverse-biased, and the capacitor ($\text{C}_{\text{HV}}$ in Fig.~\ref{Fig:PiezoCircuit}) holds its charge.
+When the switch closes to ground, current begins to flow through the primary coil of the transformer and induces a corresponding voltage across the secondary coil.
+In this state, the output diode D1 is reverse-biased, and the capacitor ($\text{C}_{\text{HV}}$ in Fig.~\ref{Fig:PiezoCircuit}) holds its charge.
 When the switch opens, the voltage across the secondary coil is inverted, putting the diode into conduction and charging the capacitor.
@@
 In our lab, we implement a gain $G\approx 50$ ($R_3 = R_5 = \SI{499}{\kilo\ohm}$; $R_4 = R_{6,7,8} = \SI{10}{\kilo\ohm}$), allowing a \SI{5}{\volt} control signal $\text{V}_\text{ctl}$ to span \SI{250}{\volt} at the output.
-A different DAC and/or a different gain factor could be chosen to adjust the maximum output voltage\footnote{Note that the passive components must be rated for the chosen output voltage.}.
-The transformer (ATB3225, 1:10 step-up winding), diode, and RC feedback network are all based on values suggested in the DRV2700 datasheet~\cite{DRV2700Datasheet,DRV2700EVMUserGuide}.
+A different DAC and/or a different gain factor could be chosen to adjust the maximum output voltage.\footnote{Note that the passive components must be rated for the chosen output voltage.}
+The transformer (ATB3225, 1:10 step-up winding), diode, and RC feedback network are all based on values suggested in the DRV2700 datasheet.\cite{DRV2700Datasheet,DRV2700EVMUserGuide}
 
 The output of the flyback regulator is passed through a four-pole, low-pass RC filter.
-The corner frequency $f_c \approx \SI{3}{\kilo\hertz}$ is chosen to be high enough that a slow ($\approx \SI{10}{\hertz}$) rail-to-rail triangle ramp can be applied by the DAC at $\text{V}_\text{ctl}$ (for, e.g., sweeping over a spectroscopy resonance), but low enough that the $\approx \SI{100}{\kilo\hertz}$ switching noise is substantially attenuated.
+The corner frequency $f_c \approx \SI{3}{\kilo\hertz}$ is chosen to be high enough that a slow ($\approx \SI{10}{\hertz}$) rail-to-rail triangle ramp can be applied by the DAC at $\text{V}_\text{ctl}$ (for, e.g., sweeping over a resonance in spectroscopy), but low enough that the $\approx \SI{100}{\kilo\hertz}$ switching noise is substantially attenuated.
 Additional capacitors on both the $\text{V}_\text{HV}$ and $\text{V}_\text{FG}$ resistor networks shunt high frequency noise to ground.
@@
 
+%Rework this paragraph re: dan's comment; stabilization vs 
+%
+%The electronics that control the galvanically isolated output of the DRV2700 works in two ways: keep Cout constant, U2 drives Vmg in order to supress the noise; 
+%
+%emphasize: sensing Vout relative to the true ground, and servoing Vmg to stabilize (remove noise, DC value...) -- explain high level first, then drill down into specifics?
+%
+%Note that the modulation gain is negative, so the voltage Vmod is inverted before being summed onto the output.
+
 The low-noise stabilization circuit is crucial to the performance of the design, as it is responsible for removing noise at the output of the flyback converter.
-To accomplish this, a high slew-rate op-amp (Texas Instruments LM7171, \SI[per-mode=symbol]{4100}{\volt\per\micro\second}) drives the galvanically isolated ground node of the flyback converter (see U2 in Fig.~\ref{Fig:PiezoCircuit}).
-This op-amp enforces the HV output voltage
+To accomplish this, a high slew-rate op-amp (Texas Instruments LM7171, \SI[per-mode=symbol]{4100}{\volt\per\micro\second}) drives the galvanically isolated floating ground of the flyback converter; see U2 in Fig.~\ref{Fig:PiezoCircuit}.
+This op-amp senses the voltage $\text{V}_\text{out}$ referenced to true circuit ground, and adjusts its output such that
 \begin{align}
@@
 \end{align}
-Here, $\text{V}_\text{mod}$ is the applied modulation, which can vary between $\pm\SI{10}{\volt}$.
+Here, $\text{V}_\text{mod}$ is the applied modulation, which can vary between $\pm\SI{10}{\volt}$ and is inverted before being summed onto the output.
 We choose $R_1 = R_\text{mod} = \SI{1}{\mega\ohm}$ and $R_2 = \SI{20.5}{\kilo\ohm}$ such that the DC gain is $\approx 50$ and the modulation gain $\Delta\text{V}_\text{out}/\Delta\text{V}_\text{mod}$ is unity.
 Depending on the application, other gain configurations could work equally well provided the non-inverting gain of U2 closely matches the gain of the flyback regulator (since they both derive from $\text{V}_\text{ctl}$).
-Ultimately, the op-amp U2 sets the operating voltage of the output (referenced to true circuit ground) while the flyback converter regulates the high voltage relative to $\text{V}_\text{FG}$.
-Because the output of the flyback regulator is galvanically isolated, U2 is able to control $\text{V}_\text{FG}$. 
-At low frequencies, this amounts to changing the floating ground reference for the flyback regulator, while at high frequencies the capacitor $\text{C}_\text{HV}$ provides a low-impedance pathway to $\text{V}_\text{out}$.
-Thus, U2 simultaneously servos residual switching noise from the flyback converter and provides a DC-coupled, high-bandwidth modulation of the output.
+
+The output of U2 can be viewed in two ways.
+At low frequencies, it modifies the floating ground reference $\text{V}_\text{FG}$ for the flyback converter, which regulates the voltage between $\text{V}_\text{HV}$ and $\text{V}_\text{FG}$.
+At higher frequencies, U2 is decoupled from $\text{V}_\text{FG}$ by the passive filtering network.
+Instead, $\text{C}_\text{out}$ provides a low-impedance path directly to the output, such that high-frequency switching noise can be directly compensated for by the op-amp.
+A small resistance $R_{11} = \SI{50}{\ohm}$ is inserted between U2 and $\text{C}_\text{out}$ to ensure stable operation, although smaller values might also work and provide better performance.
+%
+%
+%
+%Ultimately, the op-amp U2 sets the operating voltage of the output (referenced to true circuit ground) while the flyback converter regulates the high voltage relative to $\text{V}_\text{FG}$.
+%Because the output of the flyback regulator is galvanically isolated, U2 is able to control $\text{V}_\text{FG}$. 
+%At low frequencies, this amounts to changing the floating ground reference for the flyback regulator, while at high frequencies the capacitor $\text{C}_\text{out}$ provides a low-impedance pathway to $\text{V}_\text{out}$.
+%Thus, U2 simultaneously suppresses residual switching noise from the flyback converter and provides a DC-coupled, high-bandwidth modulation of the output.
 
@@
 Because this resistive divider is responsible for accurately sensing the voltage $\text{V}_\text{out}$, noise introduced by these resistors cannot be corrected by the op-amp.
-Resistors are fundamentally limited by Johnson noise, in which thermal fluctuations contribute to a white noise power spectrum given by $4 k_B T R$, where $T$ is the temperature and $k_B$ is Boltzmann's constant\cite{Horowitz2015a:JN}.
-However, resistors also exhibit $1/f$ current noise caused by equilibrium fluctuations of the resistance~\cite{Clarke1974a,Voss1976a}.
+In general, resistors are fundamentally limited by Johnson noise, in which thermal fluctuations contribute to a white noise power spectrum given by $4 k_B T R$, where $T$ is the temperature and $k_B$ is Boltzmann's constant.\cite{Horowitz2015a:JN}
+However, resistors also exhibit $1/f$ current noise caused by equilibrium fluctuations of the resistance.\cite{Clarke1974a,Voss1976a}
 This excess noise depends on the applied voltage, and therefore is an important consideration in a high-voltage circuit.
@@
 When the mid-ground node $\text{V}_\text{MG}$ (also shown in Fig.~\ref{Fig:PiezoCircuit}) goes below the threshold value set at $\text{V}_\text{TH}$, the op-amp puts the HV MOSFET Q1 into conduction.
-When engaged, the time constant for capacitor $\text{C}_\text{out}$ in Fig.~\ref{Fig:PiezoCircuit} is given by $R_\text{MOS} C_\text{out}$, which for our circuit is set to \SI{1}{\milli\second}.
+When engaged, the quench time constant is given by $\tau \approx R_\text{MOS} \text{C}_\text{out}$, which for our circuit is set to \SI{1}{\milli\second}.
+Capacitor $\text{C}_\text{out}=\SI{1}{\micro\farad}$ is shown in Fig.~\ref{Fig:PiezoCircuit}.
 \label{Fig:MOS}}
@@
 The high-voltage setpoint (absent voltages summed in at $\text{V}_\text{mod}$) is controlled by a low-noise DAC.
-This has two advantages: digital control enhances setpoint repeatability, and makes it easy to integrate with a wide variety of computerized control electronics or implement more sophisticated servo loops.
+This has two advantages: digital control enhances setpoint repeatability, and simplifies integration with a wide variety of computerized control electronics or more sophisticated servo loops.
 While the modulation input $\text{V}_\text{mod}$ has a limited range of $\pm\SI{10}{\volt}$, larger voltage swings can be achieved by reprogramming the DAC.
@@
 This filter has a switchable corner frequency (between \SI{165}{\hertz} and \SI{0.8}{\hertz}) to optimize noise performance at DC while still permitting AC modulation when needed.
+It consists of a \SI{20.5}{\kilo\ohm} resistor and \SI{47}{\nano\farad} capacitor, with a secondary \SI{10}{\micro\farad} capacitor that can be switched in to operate with the lower corner frequency.
 
-One downside of the flyback regulator presented above is that while the switched transformer is very efficient at charging the capacitor $\text{C}_\text{HV}$, discharge of the high-voltage line is limited by the $\approx\SI{1}{\second}$ RC time constant of the circuit.
+One downside of the flyback regulator presented above is that while the switched transformer can quickly charge the output capacitors, the discharge time $\tau$ is limited to {$\approx~\SI{1}{\second}$} by the RC time constant of the circuit.
 To get around this limitation, we have added an auxiliary MOSFET ``quench'' circuit, as suggested in the DRV2700 datasheet, to quickly shunt $\text{V}_\text{out}$ to ground (see Fig.~\ref{Fig:MOS}).
@@
 However, other user interfaces can easily be designed to work with the existing hardware.
-Arduino-based code written in \CC defines the entire software interaction, and can be modified depending on the needs of the researcher.
+Arduino-based code\cite{Arduino} written in \CC defines the entire software interaction, and can be modified depending on the needs of the researcher.
 
-The entire circuit fits into a standard Eurocard rack, which supplies power at $\pm\SI{15}{\volt}$.
+The circuit fits into a standard Eurocard module (3U by 12HP by \SI{160}{\milli\meter}), and is mounted in a Eurocard rack to supply power at $\pm\SI{15}{\volt}$.
 While not required, the rack provides a backplane with analog lines to communicate with other modules (e.g., to implement a current feed-forward for laser diodes as described below).
@@
 This vastly expands the conceivable control scenarios. 
-For example, in our lab we implement a slow-feedback lock of two external-cavity diode lasers to a wavemeter.
-LabView code on the computer attached to the wavemeter computes an error signal and corrective control voltage, which will be passed over our internal network to the piezo driver to correct for frequency drifts in the laser.
+For example, in our lab we implement a slow-feedback lock of external-cavity diode lasers to a wavemeter.
+Software on the computer attached to the wavemeter computes an error signal and corrective control voltage, which will be passed over our internal network to the piezo driver to correct for frequency drifts in the laser.
 Other similar schemes are possible, enabling complete remote control of the laser electronics.
@@
 In either case, this voltage is differentially buffered to break ground loops.
-An output voltage monitor (sensed at the inverting node of U2 in Fig.~\ref{Fig:PiezoCircuit}, but not shown) is buffered and connected to a BNC on the frontpanel, an analog signal line on the backplane, and to the microcontroller\footnote{One drawback of this scheme is that the contribution of $\text{V}_\text{mod}$ is not sensed by the monitor.
+An output voltage monitor (sensed at the inverting node of U2 in Fig.~\ref{Fig:PiezoCircuit}, but not shown) is buffered and connected to a BNC on the frontpanel, an analog signal line on the backplane, and to the microcontroller.\footnote{One drawback of this scheme is that the contribution of $\text{V}_\text{mod}$ is not sensed by the monitor.
 Future versions will instead monitor $\text{V}_\text{out}$ through a resistive divider, allowing the microcontroller to implement an infinite integrator and drive $\text{V}_\text{mod}$ to \SI{0}{\volt} in closed-loop operation.
-This will be a very useful feature to prevent the servo controller from railing.}.
+This will be a very useful feature to prevent the servo controller from railing.}
 The backplane monitor could be fed to a low-noise current controller (e.g., one based on the design in Erickson, et. al.~\cite{Erickson2008a}) to implement a laser diode current feed-forward.
-The high voltage output is interlocked with another signal on the backplane, which can optionally be bypassed by placing an onboard jumper, permitting easy integration with existing laboratory interlock schemes if desired.
-Further details on the design features discussed in this section, including sample software, can be found on Github~\cite{PiezoDesignFiles}.
+The high-voltage output is interlocked with another signal on the backplane, which can optionally be bypassed by placing an onboard jumper, permitting easy integration with existing laboratory interlock schemes if desired.
+Further details on the design features discussed in this section, including sample software, can be found on Github.\cite{PiezoDesignFiles}
 
@@
 \includegraphics[width=\columnwidth]{fig/NoiseModel.ai}
-\caption{Noise model.
-The element labeled $\text{C}_\text{LP}$ is comprised of a \SI{47}{\nano\farad} capacitor in parallel with a \SI{10}{\micro\farad} capacitor connected to ground through a switch, such that the corner frequency of the filter can be changed depending on the mode of operation  (see text).
-%The on-resistance of the switch introduces a zero in the transfer function at $\approx\SI{23}{\kilo\hertz}$, which has negligible effect on the computed RMS noise.
+\caption{Noise model, including contributions from the op-amp, DAC, DRV2700, and modulation input.
+The element labeled $\text{C}_\text{LP}$ consists of a \SI{47}{\nano\farad} capacitor in parallel with a \SI{10}{\micro\farad} capacitor connected to ground through a switch, such that the corner frequency of the filter can be changed depending on the mode of operation  (see text).
+Though not drawn in the figure, we also consider the Johnson noise contributions from all resistors.
 \label{Fig:NoiseModel}}
@@
 We analyze the noise performance of the circuit according to the model shown in Fig.~\ref{Fig:NoiseModel}, where noise spectral densities are calculated at the node $\text{V}_\text{out}$.
-A summary of each noise contribution (op-amp, DAC, Johnson-Nyquist, and residual ripple from the DRV2700) is shown in Fig.~\ref{Fig:NoisePlot}, along with the cumulative root-mean-square (RMS) nose estimates in different frequency bands.
-We will neglect the ``modulation noise'' appearing at node $\text{V}_\text{mod}$, because its exact character depends on the external drive.
+A summary of each noise contribution (op-amp, DAC, Johnson-Nyquist, and residual ripple from the DRV2700) is shown in Fig.~\ref{Fig:NoisePlot}, along with the cumulative root-mean-square (RMS) noise estimates in different frequency bands.
+We will neglect noise appearing at node $\text{V}_\text{mod}$ due to the external modulation because its exact character depends on the external drive.
 
@@
 \begin{align}
-G_{+}^{(i)} = G_{+}^{(v)}\left[\frac{R_\text{LP}}{1+2\pi i f R_\text{LP} C_\text{LP}}\right]\,,
+G_{+}^{(i)} = G_{+}^{(v)}\left[\frac{R_\text{LP}}{1+2\pi \iu f R_\text{LP} C_\text{LP}}\right]\,,
 \end{align}
-where the bracketed term is $Z_+$, and $f$ is the Fourier frequency.
+where the bracketed term is $Z_+$, $f$ is the Fourier frequency, and $\iu$ is the imaginary unit.
 
@@
 \centering
-\begin{tabular*}{0.95\columnwidth}{@{\extracolsep{\fill}} lcc}
+\begin{tabular*}{\columnwidth}{@{\extracolsep{\fill}} llcc}
 \hline\hline
-\rule{0pt}{2.5ex}\multirow{2}{*}{Noise source} & RMS Voltage & RMS Voltage \\
-& (\SI{1}{\hertz}~--~\SI{10}{\hertz})\rule[-1ex]{0pt}{1ex} & (\SI{10}{\hertz}~--~\SI{100}{\kilo\hertz})\rule[-1ex]{0pt}{1ex} \\
+\rule{0pt}{2.5ex}\multirow{2}{*}{Noise source} & & RMS Voltage & RMS Voltage \\
+& & (\SI{1}{\hertz}~--~\SI{10}{\hertz})\rule[-1ex]{0pt}{1ex} & (\SI{10}{\hertz}~--~\SI{100}{\kilo\hertz})\rule[-1ex]{0pt}{1ex} \\
 \hline
-\rule{0pt}{2ex}$e_n$ (op-amp U2)  & \SI{26}{\micro\volt} & \SI{31}{\micro\volt}      \\
-$i_n$ (op-amp U2)  &            \SI{51}{\micro\volt}     & \SI{73}{\micro\volt}      \\
-DAC             &             \SI{28}{\micro\volt}    & \SI{8}{\micro\volt}       \\
-Johnson-Nyquist &             \SI{3}{\micro\volt}    & \SI{14}{\micro\volt}        \\ 
-Residual switching &        \SI{15}{\micro\volt}   & \SI{43}{\micro\volt} \\
+\rule{0pt}{2ex}op-amp voltage & ($e_{v,\text{U2}}$)  & \SI{26}{\micro\volt} & \SI{31}{\micro\volt}      \\
+op-amp voltage &  ($e_{i,\text{U2}}$)  &            \SI{51}{\micro\volt}     & \SI{73}{\micro\volt}      \\
+DAC             &  ($e_{n,\text{DAC}}$)  &          \SI{28}{\micro\volt}    & \SI{8}{\micro\volt}       \\
+Johnson-Nyquist &   ($e_{n,\text{JN}}$)  &         \SI{3}{\micro\volt}    & \SI{14}{\micro\volt}        \\ 
+DRV2700 & ($e_{n,\text{DRV}}$) &        \SI{15}{\micro\volt}   & \SI{43}{\micro\volt} \\
 \hline
-\rule{0pt}{2ex}\textbf{total (calculated)} & \SI{66}{\micro\volt} & \SI{92}{\micro\volt}  \\
+\rule{0pt}{2ex}\textbf{total (calculated)} & & \SI{66}{\micro\volt} & \SI{92}{\micro\volt}  \\
 \hline\hline
@@
 Plotted are the noise contributions from each source in our model, along with the total calculated noise.
-Power spectral density (PSD) is referred to the high voltage output, and the table shows the integrated RMS noise due to each noise source in different frequency bands.
-The total RMS noise (summed in quadrature) over the entire \SI{1}{\hertz}~--~\SI{100}{\kilo\hertz} range is calculated to be \SI{113}{\micro\volt}, with the residual switching noise measured at \SI{100}{\volt}.
-Frequency-dependent noise spectra for the DAC and op-amp were extracted from the datasheets.
-\label{Fig:NoisePlot}}
+Power spectral density (PSD) is referred to the high-voltage output, and the table shows the integrated RMS noise due to each noise source in different frequency bands.
+The total RMS noise (summed in quadrature) over the entire \SI{1}{\hertz}~--~\SI{100}{\kilo\hertz} range is calculated to be \SI{113}{\micro\volt}, with the residual DRV2700 switching noise measured at \SI{100}{\volt} as described in the text.
+Frequency-dependent noise spectra for the DAC and op-amp were extracted from the datasheets.\label{Fig:NoisePlot}}
 \end{figure}
@@
 \begin{align}
-G_{-}^{(i)} = Z_1 \equiv \frac{R_1}{1+2\pi i f R_1 C_1}\,.
+G_{-}^{(i)} = Z_1 \equiv \frac{R_1}{1+2\pi \iu f R_1 C_1}\,.
 \end{align}
-The voltage gain from this node is similarly given by
-\begin{align}
-G_{-}^{(v)} = -Z_1 \left(\frac{1}{R_2} + \frac{1}{Z_\text{mod}}\right)\,.
-\end{align}
-With these in hand, we can calculate the output noise contribution from each source in our model.
+%The voltage gain from this node is similarly given by
+%\begin{align}
+%G_{-}^{(v)} = -Z_1 \left(\frac{1}{R_2} + \frac{1}{Z_\text{mod}}\right)\,.
+%\end{align}
+With these expressions in hand, we can calculate the output noise contribution from each source in our model.
 
 As shown in Fig.~\ref{Fig:NoiseModel}, the op-amp noise is parametrized by two noise contributions: $e_n$, the input voltage noise spectral density, and $i_n$, the input current noise spectral density.
-For the LM7171, $e_n = \SI[per-mode=symbol]{14}{\nano\volt\per\sqrthz}$ and $i_n = \SI[per-mode=symbol]{1.5}{\pico\ampere\per\sqrthz}$ at $\SI{10}{\kilo\hertz}$, with a $1/f$ noise character below this frequency~\cite{LM7171Datasheet}.
+For the LM7171, $e_n = \SI[per-mode=symbol]{14}{\nano\volt\per\sqrthz}$ and $i_n = \SI[per-mode=symbol]{1.5}{\pico\ampere\per\sqrthz}$ at $\SI{10}{\kilo\hertz}$ with a $1/f$ noise character below this frequency.\cite{LM7171Datasheet}
 The voltage noise appears at the non-inverting input, while the current noise is present at both inputs.
-By multiplying each source by the appropriate gain, we obtain the equivalent output noise power spectral densities (PSD),
+By multiplying each source by the appropriate gain, we obtain the equivalent output-noise power spectral densities (PSD),
 \begin{align}
@@
 \end{align}
-where  $e^2_{v,\text{U2}}$, $e^2_{i,\text{U2}}$ are the output-referred voltage and current noise PSD, respectively.
+where  $e^2_{v,\text{U2}}$, $e^2_{i,\text{U2}}$ are the output-referred voltage and current noise PSD, respectively (plotted in Fig.~\ref{Fig:NoisePlot}).
 
@@
 \includegraphics[width=\columnwidth]{fig/VoltagePSD.png}
-\caption{Voltage power spectral density at various output voltages.
-The integrated RMS voltage noise ($\SI{1}{\hertz} - \SI{100}{\kilo\hertz}$) is $\{138, 80, 101\}~\si{\micro\volt}$ measured at  $\{50, 100, 200\}~\si{\volt}$, with no output load.
-\label{Fig:PSD}}
+\caption{Voltage noise power spectral density at various output voltages (color online).
+The integrated RMS noise ($\SI{1}{\hertz} - \SI{100}{\kilo\hertz}$) is $\{138, 80, 101\}~\si{\micro\volt}$ measured at  $\{50, 100, 200\}~\si{\volt}$, with no output load.
+The dashed black line indicates the noise estimate from our model (see Fig.~\ref{Fig:NoisePlot}).\label{Fig:PSD}}
 \end{figure}
@@
 \label{Eq:Gdc}
-G^{(v)}_{\text{ctl}} &= \left(\frac{1}{1+2\pi i f R_\text{LP} C_\text{LP}}\right)G_{+}^{(v)}\,,
+G^{(v)}_{\text{ctl}} &= \left[\frac{1}{1+2\pi \iu f R_\text{LP} C_\text{LP}}\right]G_{+}^{(v)}\,,
 \end{align}
-where the first term represents the contribution to the transfer function from the switchable low-pass filter.
+where the bracketed term represents the contribution to the transfer function from the switchable low-pass filter.
 Without the addition of this low-pass filter, the voltage noise of the DAC would dominate both the low- and high-frequency noise performance of the circuit.
@@
 Thus, we use a switchable low-pass filter (as described in Sec.~\ref{Sec:SlowModulationMOS}) to achieve low-noise performance during DC operation, while still permitting the DAC to modulate $\text{V}_\text{ctl}$ more quickly when needed.
-In our circuit, the high-corner filter is comprised of a \SI{20.5}{\kilo\ohm} resistor and \SI{47}{\nano\farad} capacitor, with $f_c \approx \SI{165}{\hertz}$.
-In DC mode, a secondary \SI{10}{\micro\farad} capacitor in parallel with the \SI{47}{\nano\farad} capacitor mentioned above can be connected to ground through a low resistance digital switch.
-This changes the corner frequency to \SI{0.8}{\hertz}.
+%In our circuit, the high-corner filter is comprised of a \SI{20.5}{\kilo\ohm} resistor and \SI{47}{\nano\farad} capacitor, with $f_c \approx \SI{165}{\hertz}$.
+%In DC mode, a secondary \SI{10}{\micro\farad} capacitor in parallel with the \SI{47}{\nano\farad} capacitor mentioned above can be connected to ground through a low resistance digital switch.
+%This changes the corner frequency to \SI{0.8}{\hertz}.
 The non-zero resistance of the switch contributes a zero to the transfer function at $\approx\SI{23}{\kilo\hertz}$, but has negligible effect on the performance.
@@
 \end{align}
-where $v_{n,\text{DAC}}$ is the frequency dependent output voltage noise of the DAC\cite{AD56XXRDatasheet}. 
-In subsequent calculations, we take the DC-mode operation for the switchable low-pass filter.
+where $v_{n,\text{DAC}}$ is the frequency dependent output voltage noise of the DAC as reported in the datasheet.\cite{AD56XXRDatasheet} 
+In subsequent calculations, we take the DC-mode operation ($f_c = \SI{0.8}{\hertz}$) for the switchable low-pass filter.
 
@@
 \includegraphics[width=\columnwidth]{fig/TimeDomain.png}
-\caption{Time-domain traces of the high voltage output (\SI{100}{\volt}).
-(a) Short-time scatterplot  (AC coupled).
-Points are colored based on the Gaussian spread in acquired voltages, thus indicating the RMS width of the trace.
+\caption{Time-domain traces of the high-voltage output (\SI{100}{\volt}). (a) Short-time scatterplot  (AC coupled). 
+%Points are colored based on the Gaussian spread in acquired voltages, thus indicating the RMS width of the trace.
+The points have been down-sampled and colored based on their probability of occurence, thus providing a visual estimation of the RMS width.
 (b) Long-term trace, measured on a Keithly~2010 digital multimeter.
@@
 The low-noise stabilization circuit is limited in its ability to reject residual switching noise from the DRV2700 regulator (after the passive filtering network) by the total loop gain analyzed from node $\text{V}_\text{out}$.
-The LM7171 has a reported open-loop gain of \SI{85}{\decibel} ($\approx 1.8\times 10^4$), with a dominant pole at $\approx\SI{10}{\kilo\hertz}$\cite{LM7171Datasheet}.
+The LM7171 has a reported open-loop gain of \SI{85}{\decibel} ($\approx 1.8\times 10^4$), with a dominant pole at $\approx\SI{10}{\kilo\hertz}$.\cite{LM7171Datasheet}
 We can model the open loop gain, $G_\text{OL}$, as
 \begin{align}
-G_\text{OL} &= \frac{1.8\times10^4}{1 + i (f/\SI{10}{\kilo\hertz})}\,.
+G_\text{OL} &= \frac{1.8\times10^4}{1 + \iu (f/\SI{10}{\kilo\hertz})}\,.
 \end{align}
@@
 
-A good estimate of the noise spectral density $v_{n,\text{DRV}}$ can be obtained by measuring the voltage power spectrum at node $\text{V}_\text{U2}$ in Fig.~\ref{Fig:NoiseModel}, since the output of this op-amp represents the control signal required to cancel voltage fluctuations at $\text{V}_\text{out}$.
-The trace plotted in Fig.~\ref{Fig:NoisePlot} assumes $v_{n,\text{DRV}}$ given by this measurement. 
-Because the noise floor of our instrument crosses the measurement trace at $\approx\SI{10}{\kilo\hertz}$, we only plot out to that frequency.
+We estimate the noise spectral density $v_{n,\text{DRV}}$ by measuring it at node $\text{V}_\text{U2}$ in Fig.~\ref{Fig:NoiseModel}, since the output of this op-amp represents the control signal required to cancel voltage fluctuations at $\text{V}_\text{out}$.
+The trace for $e_{n,\text{DRV}}$ plotted in Fig.~\ref{Fig:NoisePlot} is derived from the results of this measurement.
+Because the measured $v_{n,\text{DRV}}$ drops below the noise floor of our spectrum analyzer at $\approx \SI{10}{\kilo\hertz}$, we only plot the trace out to this frequency.
+%%% Comment about the total RMS noise from DRV2700, cancellation by op amp
 
@@
 The op-amp current noise contribution could be suppressed by using lower resistances $R_1$ and $R_\text{mod}$, however one must be careful about power and current limitations when dealing with such high voltages.
-Each noise source is tabulated and plotted in Fig.~\ref{Fig:NoisePlot}, and the total voltage noise  is calculated to be $\SI{113}{\micro\volt}$ ($\SI{1}{\hertz} - \SI{100}{\kilo\hertz}$, $\text{V}_\text{out} = \SI{100}{\volt}$).
-Frequency-dependent input noise parameters in this model were extracted from datasheet spectral density curves\cite{LM7171Datasheet,AD56XXRDatasheet}, and measured for the residual DRV2700 noise $v_{n,\text{DRV}}$ as discussed above.
-At lower voltages, the residual ripple from the DRV2700 begins to dominate the noise performance.
-This can be seen in Fig.~\ref{Fig:PSD}, as the characteristic shape changes between \SI{100}{\volt} and \SI{50}{\volt}.
+Each noise source is tabulated and plotted in Fig.~\ref{Fig:NoisePlot}, and the total voltage noise ($\SI{1}{\hertz} - \SI{100}{\kilo\hertz}$, $\text{V}_\text{out} = \SI{100}{\volt}$) is calculated to be $\SI{113}{\micro\volt}$ .
+%Frequency-dependent input noise parameters in this model were extracted from datasheet spectral density curves\cite{LM7171Datasheet,AD56XXRDatasheet}, and measured for the residual DRV2700 noise $v_{n,\text{DRV}}$ as discussed above.
+%At lower voltages, the residual ripple from the DRV2700 begins to dominate the noise performance.
+%This can be seen in Fig.~\ref{Fig:PSD}, as the characteristic shape changes between \SI{100}{\volt} and \SI{50}{\volt}.
 
@@
 \caption{Modulation input transfer function (color online).
-The blue line indicates the unloaded frequency response, while the dash-dotted orange trace shows the response with a ThorLabs piezoelectric actuator {(PN~AE0505D08F)}.
+The solid blue line indicates the unloaded frequency response, while the dash-dotted orange trace shows the response with a \SI{700}{\nano\farad} piezoelectric actuator~{(Thorlabs PN~AE0505D08F)}.
 Mechanical resonances above $\approx\SI{50}{\kilo\hertz}$ are clearly visible.
 The dashed green trace shows the response under a \SI{1}{\micro\farad} purely capacitive load.
-Loaded response bandwidth is $\approx\SI{100}{\kilo\hertz}$, while the unloaded bandwidth is $\approx\SI{1}{\mega\hertz}$.\label{Fig:TransferFunc}}
+Loaded response bandwidth is $\approx~\SI{100}{\kilo\hertz}$, while the unloaded bandwidth is $\approx~\SI{1}{\mega\hertz}$.\label{Fig:TransferFunc}}
 \end{figure}
@@
 This matches roughly with the expected total RMS noise calculated in Sec.~\ref{Sec:NoiseAnalysis}.
-The difference in noise performance at different output voltages can be traced back to the residual ripple of the DRV2700, which counterintuitively is larger for lower output voltages.
-The additional low-frequency $1/f$ noise present at \SI{200}{\volt} we suspect is due to some voltage-dependent noise source not considered in our model.
+The difference in noise performance at different output voltages can be traced back to the residual ripple of the DRV2700, which is larger for lower output voltages.
+Indeed, one can see the characteristic shape change between \SI{100}{\volt} and \SI{50}{\volt} in Fig.~\ref{Fig:PSD} as the residual ripple $e_{n,\text{DRV}}$ begins to dominate at low frequencies.
 
@@
 This is due generically to $1/f$ noise, but also correlates with the external temperature.
-A cross-correlation between measured temperature and output voltage (trace not shown) yields an effective temperature coefficient of \SI[per-mode=symbol]{-24}{ppm\per\celsius} at \SI{100}{\volt}.
+A cross-correlation between the measured temperature and output voltage (trace not shown) yields an effective temperature coefficient of \SI[per-mode=symbol]{-24}{ppm\per\celsius} at \SI{100}{\volt}.
 The short-term trace was taken on a PicoScope~5442B (AC-coupled, \SI{100}{\volt} output).
-Points are colored based on their normally distributed statistical probability, and thus give a visual estimation of the RMS width.
+For clarity, the trace has been down-sampled and the points colored based on their probability of occurrence.
+Thus, the color gives a visual estimation of the RMS width.
+% are colored based on their normally distributed statistical probability, and thus give a visual estimation of the RMS width.
 

### 2016-09-04 piezo.tex
(hopefully) final round of edits.

@@
 
+\usepackage{natbib}
+
 \begin{document}
@@
 \author{G.K. Campbell}
-\affiliation{Joint Quantum Institute, University of Maryland and National Institute of Standards and Technology}
+\affiliation{Joint Quantum Institute, University of Maryland and National Institute of Standards and Technology \\ College Park, MD 20742, USA}
 
@@
 A low-voltage (\SI{\pm 10}{\volt}), high bandwidth signal can be summed with unity gain directly onto the output, making the driver well-suited for closed-loop feedback applications.
-Digital control enables both repeatable setpoints and sophisticated control logic. 
-The circuit consumes less than \SI{150}{\milli\ampere} at $\pm\SI{15}{\volt}$.
+Digital control enables both repeatable setpoints and sophisticated control logic, and the circuit consumes less than \SI{150}{\milli\ampere} at $\pm\SI{15}{\volt}$.
 \end{abstract}
@@
 For example, piezo-actuated mirrors and diffraction gratings play an important role in atomic physics experiments (used, e.g., in Fabry-Per{\`o}t cavities\cite{Riedle1994a,Bohlouli-Zanjani2006a} and external-cavity diode lasers\cite{Wieman1991a}), while avalanche photodiodes and photomultiplier tubes require large bias voltages for proper operation.
-In the realm of biophysics, electrokinetic separation methods such as free-flow or capillary electrophoresis\cite{Kohlheyer2008a} require large electric field gradients.
-In addition, the recent push to develop lab-on-a-chip devices could benefit from miniaturized high-voltage sources.\cite{Temiz2015a}
+In the realm of biophysics, electrokinetic separation methods such as free-flow or capillary electrophoresis\cite{Kohlheyer2008a} require large electric field gradients, and the recent push to develop lab-on-a-chip devices could benefit from miniaturized high-voltage sources.\cite{Temiz2015a}
 
@@
 Commercially available piezoelectric drivers typically provide a modulation input for  such closed-loop applications, but  the input voltage is often gained such that it spans the entire output range of the device.
-While this has certain advantages, many applications would benefit from an architecture that provides a unity gain, DC-coupled feedback path to the high-voltage output. 
+While this has certain advantages, many applications would benefit from an architecture that provides a unity-gain, DC-coupled feedback path to the high-voltage output. 
 Such a device could make closed-loop systems less susceptible to noise contributions from the servo controller, which we often find in our laboratory to be the limiting factor in laser lock stability.
@@
 Linear-type devices are typically constructed from a high-voltage operational amplifier (op-amp), powered either from a high-voltage linear regulator or more typically from a secondary switching converter.
-While the op-amp provides \SI{100}{\decibel} or more of power-supply noise rejection, high-voltage op-amps require substantially more power than an equivalent switching circuit and are more cumbersome to deploy in the laboratory.
+While the op-amp can provide \SI{100}{\decibel} or more of power-supply noise rejection\cite{PA84Datasheet}, high-voltage op-amps require substantially more power than an equivalent switching circuit and are more cumbersome to deploy in the laboratory.
 
 We present a circuit with a hybrid architecture.
-The high voltage is generated by a galvanically isolated DC-DC converter (described in Sec.~\ref{Sec:DRV2700}), while a low-noise, high slew-rate op-amp simulatneously removes noise at the output and provides a low-gain, high-bandwidth modulation input for closed-loop feedback applications  (see Sec.~\ref{Sec:LowNoiseStabilization}).
-This architecture is able to achieve extremely low noise performance ($\approx\SI{100}{\micro\volt}_{\text{RMS}}$) over the entire output range, draws very little current, and fits comfortably onto a small-footprint PCB.
+The high voltage is generated by a galvanically isolated DC-DC converter, while a low-noise, high-slew-rate op-amp simulatneously removes noise at the output and provides a low-gain, high-bandwidth modulation input for closed-loop feedback applications.
+This architecture is able to achieve extremely low noise ($\approx\SI{100}{\micro\volt}_{\text{RMS}}$) over the entire output range, draws very little current, and fits comfortably onto a small-footprint PCB.
 Additionally, the high-voltage output remains single-ended and referenced to ground, allowing it to drive piezo actuators with a grounded terminal.
-We present a noise analysis of our circuit in Sec.~\ref{Sec:NoiseAnalysis}, and show characteristic performance data in Sec.~\ref{Sec:Results}.
-Complete design files, including the schematic, bill of materials, and board layout, can be found on Github.\cite{PiezoDesignFiles}
+The schematic is presented in Sec.~\ref{Sec:Circuit}, with a noise analysis in Sec.~\ref{Sec:NoiseAnalysis} and characteristic performance data in Sec.~\ref{Sec:Results}.
+Complete design files, including the schematic, bill of materials, and board layout, can be found on GitHub.\cite{PiezoDesignFiles}
 The board manufacture and component cost is less than \SI{200}[\$]{}, making it a cost-effective alternative to commercial options.
@@
 Our design targets a \SI{250}{\volt} output, but we discuss straightforward modifications to the schematic that make it possible to tailor the gain and output range to a specific application.
-The entire electronics package fits comfortably into a compact eurocard rack module (with the high-voltage section taking only a fraction of the PCB), and draws less than \SI{150}{\milli\ampere} at \SI{15}{\volt}.
-%The full schematic, including Gerbers, a bill of materials, and layout design files, can be found on GitHub.~\footnote{\protect\url{https://github.com/JQIamo/hv-piezo-driver}}
+The entire electronics package fits into a compact Eurocard rack module (with the high-voltage section taking only a fraction of the PCB), and draws less than \SI{150}{\milli\ampere} at \SI{15}{\volt}.
 
@@
 A digital-to-analog converter (DAC) generates a voltage setpoint, $\text{V}_\text{ctl}$, which is sent to the high-voltage flyback regulator and to the low-noise stabilization circuit.
-The flyback regulator (Sec.~\ref{Sec:DRV2700}) controls the potential between circuit nodes $\text{V}_\text{HV}$ and $\text{V}_\text{FG}$, while the low-noise stabilization circuitry (Sec.~\ref{Sec:LowNoiseStabilization}) controls the output node $\text{V}_\text{out}$ relative to the true circuit ground.
+The flyback regulator (Sec.~\ref{Sec:DRV2700}) controls the potential between the high-voltage ($\text{V}_\text{HV}$) and floating-ground ($\text{V}_\text{FG}$) circuit nodes, while the low-noise stabilization circuitry (Sec.~\ref{Sec:LowNoiseStabilization}) controls the output node $\text{V}_\text{out}$ relative to the true circuit ground.
 The DAC is controlled by an integrated microcontroller, and can be programmed to output slow ($\approx\SI{10}{\hertz}$) rail-to-rail voltage ramps in addition to setting the DC operating point (Sec.~\ref{Sec:SlowModulationMOS}).
@@
 In flyback configuration, the internal-boost switch of the DRV2700 (pin SW in Fig.~\ref{Fig:PiezoCircuit}) drives a step-up transformer.
-When the switch closes to ground, current begins to flow through the primary coil of the transformer and induces a corresponding voltage across the secondary coil.
+When the switch closes, current begins to flow through the primary coil of the transformer and induces a corresponding voltage across the secondary coil.
 In this state, the output diode D1 is reverse-biased, and the capacitor ($\text{C}_{\text{HV}}$ in Fig.~\ref{Fig:PiezoCircuit}) holds its charge.
@@
 as suggested by the DRV2700 datasheet\cite{DRV2700Datasheet}, where $R_6 = R_7 = R_8$, and $R_i~||~R_j \equiv R_i R_j/(R_i + R_j)$.
-In our lab, we implement a gain $G\approx 50$ ($R_3 = R_5 = \SI{499}{\kilo\ohm}$; $R_4 = R_{6,7,8} = \SI{10}{\kilo\ohm}$), allowing a \SI{5}{\volt} control signal $\text{V}_\text{ctl}$ to span \SI{250}{\volt} at the output.
+In our implementation, we choose a gain $G\approx 50$ ($R_3 = R_5 = \SI{499}{\kilo\ohm}$; $R_4 = R_{6,7,8} = \SI{10}{\kilo\ohm}$), allowing a \SI{5}{\volt} control signal $\text{V}_\text{ctl}$ to span \SI{250}{\volt} at the output.
 A different DAC and/or a different gain factor could be chosen to adjust the maximum output voltage.\footnote{Note that the passive components must be rated for the chosen output voltage.}
@@
 The output of the flyback regulator is passed through a four-pole, low-pass RC filter.
-The corner frequency $f_c \approx \SI{3}{\kilo\hertz}$ is chosen to be high enough that a slow ($\approx \SI{10}{\hertz}$) rail-to-rail triangle ramp can be applied by the DAC at $\text{V}_\text{ctl}$ (for, e.g., sweeping over a resonance in spectroscopy), but low enough that the $\approx \SI{100}{\kilo\hertz}$ switching noise is substantially attenuated.
+The corner frequency $f_c \approx \SI{30}{\hertz}$ is chosen to be high enough that a slow ($\approx \SI{10}{\hertz}$) rail-to-rail triangle ramp can be applied by the DAC at $\text{V}_\text{ctl}$ (for, e.g., sweeping over a resonance in spectroscopy), but low enough that the $\approx \SI{100}{\kilo\hertz}$ switching noise is substantially attenuated.
 Additional capacitors on both the $\text{V}_\text{HV}$ and $\text{V}_\text{FG}$ resistor networks shunt high frequency noise to ground.
@@
 The low-noise stabilization circuit is crucial to the performance of the design, as it is responsible for removing noise at the output of the flyback converter.
-To accomplish this, a high slew-rate op-amp (Texas Instruments LM7171, \SI[per-mode=symbol]{4100}{\volt\per\micro\second}) drives the galvanically isolated floating ground of the flyback converter; see U2 in Fig.~\ref{Fig:PiezoCircuit}.
+To accomplish this, a high slew-rate op-amp (Texas Instruments LM7171, \SI[per-mode=symbol]{4100}{\volt\per\micro\second}; see U2 in Fig.~\ref{Fig:PiezoCircuit}) drives the galvanically isolated floating ground of the flyback converter.
 This op-amp senses the voltage $\text{V}_\text{out}$ referenced to true circuit ground, and adjusts its output such that
@@
 Here, $\text{V}_\text{mod}$ is the applied modulation, which can vary between $\pm\SI{10}{\volt}$ and is inverted before being summed onto the output.
-We choose $R_1 = R_\text{mod} = \SI{1}{\mega\ohm}$ and $R_2 = \SI{20.5}{\kilo\ohm}$ such that the DC gain is $\approx 50$ and the modulation gain $\Delta\text{V}_\text{out}/\Delta\text{V}_\text{mod}$ is unity.
+We choose $R_1 = R_\text{mod} = \SI{1}{\mega\ohm}$ and $R_2 = \SI{20.5}{\kilo\ohm}$ such that the DC gain $\Delta\text{V}_\text{out}/\Delta\text{V}_\text{ctl}$ is $\approx 50$ and the modulation gain $\Delta\text{V}_\text{out}/\Delta\text{V}_\text{mod}$ is unity.
 Depending on the application, other gain configurations could work equally well provided the non-inverting gain of U2 closely matches the gain of the flyback regulator (since they both derive from $\text{V}_\text{ctl}$).
 
-The output of U2 can be viewed in two ways.
-At low frequencies, it modifies the floating ground reference $\text{V}_\text{FG}$ for the flyback converter, which regulates the voltage between $\text{V}_\text{HV}$ and $\text{V}_\text{FG}$.
+The op-amp U2 controls $\text{V}_\text{out}$ via two different feedback pathways.
+At low frequencies, it modifies the floating ground reference $\text{V}_\text{FG}$ of the flyback converter, and the DRV2700 in turn modifies $\text{V}_\text{HV}$ to maintain a constant voltage between $\text{V}_\text{FG}$ and $V_\text{HV}$.
 At higher frequencies, U2 is decoupled from $\text{V}_\text{FG}$ by the passive filtering network.
-Instead, $\text{C}_\text{out}$ provides a low-impedance path directly to the output, such that high-frequency switching noise can be directly compensated for by the op-amp.
-A small resistance $R_{11} = \SI{50}{\ohm}$ is inserted between U2 and $\text{C}_\text{out}$ to ensure stable operation, although smaller values might also work and provide better performance.
-%
-%
-%
-%Ultimately, the op-amp U2 sets the operating voltage of the output (referenced to true circuit ground) while the flyback converter regulates the high voltage relative to $\text{V}_\text{FG}$.
-%Because the output of the flyback regulator is galvanically isolated, U2 is able to control $\text{V}_\text{FG}$. 
-%At low frequencies, this amounts to changing the floating ground reference for the flyback regulator, while at high frequencies the capacitor $\text{C}_\text{out}$ provides a low-impedance pathway to $\text{V}_\text{out}$.
-%Thus, U2 simultaneously suppresses residual switching noise from the flyback converter and provides a DC-coupled, high-bandwidth modulation of the output.
+In this regime, $\text{C}_\text{out}$ provides a low-impedance path between U2 and the output, such that high-frequency switching noise can be directly compensated for by the op-amp.
+We settled on a value $\text{C}_\text{out}=\SI{1}{\micro\farad}$, which is a compromise between component size and the desire for a large capacitance.
+In addition, a small resistance $R_{11} = \SI{50}{\ohm}$ is inserted between U2 and $\text{C}_\text{out}$ to ensure stable operation.
+Smaller $R_{11}$ and/or larger $\text{C}_\text{out}$ might provide better performance, but this has not been tested.
 
@@
 The high-voltage setpoint (absent voltages summed in at $\text{V}_\text{mod}$) is controlled by a low-noise DAC.
-This has two advantages: digital control enhances setpoint repeatability, and simplifies integration with a wide variety of computerized control electronics or more sophisticated servo loops.
+This has two advantages: digital control enhances setpoint repeatability, and simplifies the integration with computerized control electronics or sophisticated servo loops.
 While the modulation input $\text{V}_\text{mod}$ has a limited range of $\pm\SI{10}{\volt}$, larger voltage swings can be achieved by reprogramming the DAC.
@@
 As discussed below in Sec.~\ref{Sec:NoiseAnalysis}, without modification the DAC would dominate the noise performance of $\text{V}_\text{out}$.
-Therefore, we add a single-pole low-pass filter between $\text{V}_\text{ctl}$ and the non-inverting node of U2.
+Therefore, we add a single-pole low-pass filter between $\text{V}_\text{ctl}$ and the non-inverting node of U2 to bring the DAC noise contribution below other noise sources in the circuit.
 This filter has a switchable corner frequency (between \SI{165}{\hertz} and \SI{0.8}{\hertz}) to optimize noise performance at DC while still permitting AC modulation when needed.
@@
 One downside of the flyback regulator presented above is that while the switched transformer can quickly charge the output capacitors, the discharge time $\tau$ is limited to {$\approx~\SI{1}{\second}$} by the RC time constant of the circuit.
-To get around this limitation, we have added an auxiliary MOSFET ``quench'' circuit, as suggested in the DRV2700 datasheet, to quickly shunt $\text{V}_\text{out}$ to ground (see Fig.~\ref{Fig:MOS}).
+To get around this limitation, we have added an auxiliary MOSFET ``quench'' circuit, as suggested in the DRV2700 datasheet\cite{DRV2700Datasheet}, to quickly shunt $\text{V}_\text{out}$ to ground (see Fig.~\ref{Fig:MOS}).
 This circuit works by monitoring the voltage at $\text{V}_\text{MG}$, the mid-ground node controlled by op-amp U2.
-If that voltage drops below a threshold set by $\text{V}_\text{TH}$, the comparator op-amp in Fig.~\ref{Fig:MOS} changes the gate voltage of the MOSFET to put it into conduction.
+If $\text{V}_\text{MG}$ drops below a threshold set by $\text{V}_\text{TH}$, the comparator op-amp in Fig.~\ref{Fig:MOS} changes the gate voltage of the MOSFET to put it into conduction.
 The time constant for this configuration is given by $\tau \approx R_\text{MOS}\text{C}_\text{out}$.
@@
 Here, we discuss some additional features of our circuit that are independent of the high-voltage design but are advantageous for many applications.
-The onboard microcontroller responsible for setting the DAC control voltage, $\text{V}_\text{ctl}$, also interfaces with frontpanel controls including a switch, LCD, and rotary encoder with an integrated push button.
-The encoder/push button provide menu navigation, and the switch toggles between DC and scanning operation.
+The onboard microcontroller responsible for setting the DAC control voltage, $\text{V}_\text{ctl}$, also interfaces with frontpanel controls including a switch, LCD, and rotary encoder with an integrated pushbutton.
+The encoder/pushbutton provide menu navigation, and the switch toggles between DC and scanning operation.
 However, other user interfaces can easily be designed to work with the existing hardware.
@@
 
-The circuit fits into a standard Eurocard module (3U by 12HP by \SI{160}{\milli\meter}), and is mounted in a Eurocard rack to supply power at $\pm\SI{15}{\volt}$.
+The circuit fits into a standard Eurocard module\footnote{Module size is 3U by 12HP by \SI{160}{\milli\meter}, see IEEE~Std~1101.11 for details.}, and is mounted in a Eurocard rack which supplies power at $\pm\SI{15}{\volt}$.
 While not required, the rack provides a backplane with analog lines to communicate with other modules (e.g., to implement a current feed-forward for laser diodes as described below).
@@
 The backplane monitor could be fed to a low-noise current controller (e.g., one based on the design in Erickson, et. al.~\cite{Erickson2008a}) to implement a laser diode current feed-forward.
-The high-voltage output is interlocked with another signal on the backplane, which can optionally be bypassed by placing an onboard jumper, permitting easy integration with existing laboratory interlock schemes if desired.
-Further details on the design features discussed in this section, including sample software, can be found on Github.\cite{PiezoDesignFiles}
+The high-voltage output can be interlocked with another signal on the backplane, permitting easy integration with existing laboratory interlock schemes if desired.
+Further details on the design features discussed in this section, including sample software, can be found on GitHub.\cite{PiezoDesignFiles}
 
@@
 
-To facilitate the noise analysis, we first calculate the voltage and current (transimpedance) gains from the input nodes of U2 to the output, $\text{V}_\text{out}$.
+To facilitate the noise analysis, we calculate the voltage and current (transimpedance) gains from the input nodes of U2 to the output, $\text{V}_\text{out}$.
 Starting with the non-inverting node, we find the voltage gain to be
@@
 As shown in Fig.~\ref{Fig:NoiseModel}, the op-amp noise is parametrized by two noise contributions: $e_n$, the input voltage noise spectral density, and $i_n$, the input current noise spectral density.
-For the LM7171, $e_n = \SI[per-mode=symbol]{14}{\nano\volt\per\sqrthz}$ and $i_n = \SI[per-mode=symbol]{1.5}{\pico\ampere\per\sqrthz}$ at $\SI{10}{\kilo\hertz}$ with a $1/f$ noise character below this frequency.\cite{LM7171Datasheet}
+For the LM7171 at $\SI{10}{\kilo\hertz}$, $e_n = \SI[per-mode=symbol]{14}{\nano\volt\per\sqrthz}$ and $i_n = \SI[per-mode=symbol]{1.5}{\pico\ampere\per\sqrthz}$ with a $1/f$ noise character below this frequency.\cite{LM7171Datasheet}
 The voltage noise appears at the non-inverting input, while the current noise is present at both inputs.
@@
 The integrated RMS noise ($\SI{1}{\hertz} - \SI{100}{\kilo\hertz}$) is $\{138, 80, 101\}~\si{\micro\volt}$ measured at  $\{50, 100, 200\}~\si{\volt}$, with no output load.
-The dashed black line indicates the noise estimate from our model (see Fig.~\ref{Fig:NoisePlot}).\label{Fig:PSD}}
+The dashed black line indicates the total noise estimate from our model, calculated at \SI{100}{\volt} (see Fig.~\ref{Fig:NoisePlot}).\label{Fig:PSD}}
 \end{figure}
@@
 \end{align}
-where $v_{n,\text{DAC}}$ is the frequency dependent output voltage noise of the DAC as reported in the datasheet.\cite{AD56XXRDatasheet} 
+where $v_{n,\text{DAC}}$ is the frequency-dependent output voltage noise of the DAC as reported in the datasheet.\cite{AD56XXRDatasheet} 
 In subsequent calculations, we take the DC-mode operation ($f_c = \SI{0.8}{\hertz}$) for the switchable low-pass filter.
@@
 \includegraphics[width=\columnwidth]{fig/TimeDomain.png}
-\caption{Time-domain traces of the high-voltage output (\SI{100}{\volt}). (a) Short-time scatterplot  (AC coupled). 
+\caption{Time-domain traces of the high-voltage output (\SI{100}{\volt}, color online). (a) Short-time scatterplot  (AC coupled). 
 %Points are colored based on the Gaussian spread in acquired voltages, thus indicating the RMS width of the trace.
-The points have been down-sampled and colored based on their probability of occurence, thus providing a visual estimation of the RMS width.
+%The points have been down-sampled and colored based on their probability of occurence, thus providing a visual estimation of the RMS width.
+The points have been down-sampled for clarity, and colored based on a normally-distributed probability of occurence in each 100-\si{\micro\second} timeslice (scaled to the most probable voltage).
+The color thus provides a visual estimation of the RMS width.
+%At each time bin, the points have been colored based on a normally-distributed probability of occurrence, scaled to the most probable voltage for that bin.
+%The points have been binned down-sampled and colored based on their probability of occurence, normalized to the most probable voltage in each time bin, thus providing a visual estimation of the RMS width.
 (b) Long-term trace, measured on a Keithly~2010 digital multimeter.
@@
 &\left[ \big|G_{-}^{(i)}\big|^2 \left(\frac{1}{R_1} + \frac{1}{R_2} + \frac{1}{R_\text{mod}} \right) + 
-\frac{\big|G_{+}^{(i)}\big|^2}{R_\text{LP}} \right]
+\frac{\big|G_{+}^{(i)}\big|^2}{R_\text{LP}} \right]\,.
 \end{split}
@@
 
-We estimate the noise spectral density $v_{n,\text{DRV}}$ by measuring it at node $\text{V}_\text{U2}$ in Fig.~\ref{Fig:NoiseModel}, since the output of this op-amp represents the control signal required to cancel voltage fluctuations at $\text{V}_\text{out}$.
+We estimate the noise spectral density $v_{n,\text{DRV}}$ by monitoring the node $\text{V}_\text{U2}$ in Fig.~\ref{Fig:NoiseModel}, since the output of this op-amp represents the control signal required to cancel voltage fluctuations at $\text{V}_\text{out}$.
 The trace for $e_{n,\text{DRV}}$ plotted in Fig.~\ref{Fig:NoisePlot} is derived from the results of this measurement.
 Because the measured $v_{n,\text{DRV}}$ drops below the noise floor of our spectrum analyzer at $\approx \SI{10}{\kilo\hertz}$, we only plot the trace out to this frequency.
-%%% Comment about the total RMS noise from DRV2700, cancellation by op amp
-
-% such that the closed-loop gain for noise contributed by the flyback regulator at node $\text{V}_\text{out}$ is minimized in the \SIrange{40}{100}{\kilo\hertz} switching noise band.
-%For $R_1=\SI{1}{\mega\ohm}$, we choose $\text{C}_1=\SI{1}{\nano\farad}$.
-%The noise gain
 
@@
 The op-amp current noise contribution could be suppressed by using lower resistances $R_1$ and $R_\text{mod}$, however one must be careful about power and current limitations when dealing with such high voltages.
-Each noise source is tabulated and plotted in Fig.~\ref{Fig:NoisePlot}, and the total voltage noise ($\SI{1}{\hertz} - \SI{100}{\kilo\hertz}$, $\text{V}_\text{out} = \SI{100}{\volt}$) is calculated to be $\SI{113}{\micro\volt}$ .
-%Frequency-dependent input noise parameters in this model were extracted from datasheet spectral density curves\cite{LM7171Datasheet,AD56XXRDatasheet}, and measured for the residual DRV2700 noise $v_{n,\text{DRV}}$ as discussed above.
-%At lower voltages, the residual ripple from the DRV2700 begins to dominate the noise performance.
-%This can be seen in Fig.~\ref{Fig:PSD}, as the characteristic shape changes between \SI{100}{\volt} and \SI{50}{\volt}.
+Each noise source is tabulated and plotted in Fig.~\ref{Fig:NoisePlot}, and the total voltage noise ($\SI{1}{\hertz} - \SI{100}{\kilo\hertz}$, $\text{V}_\text{out} = \SI{100}{\volt}$) is calculated to be $\SI{113}{\micro\volt}_\text{RMS}$ .
 
@@
 The difference in noise performance at different output voltages can be traced back to the residual ripple of the DRV2700, which is larger for lower output voltages.
-Indeed, one can see the characteristic shape change between \SI{100}{\volt} and \SI{50}{\volt} in Fig.~\ref{Fig:PSD} as the residual ripple $e_{n,\text{DRV}}$ begins to dominate at low frequencies.
+Indeed, one can see the characteristic shape change in Fig.~\ref{Fig:PSD} between \SI{100}{\volt} and \SI{50}{\volt} as the residual ripple $e_{n,\text{DRV}}$ begins to dominate at low frequencies.
 
@@
 This is due generically to $1/f$ noise, but also correlates with the external temperature.
-A cross-correlation between the measured temperature and output voltage (trace not shown) yields an effective temperature coefficient of \SI[per-mode=symbol]{-24}{ppm\per\celsius} at \SI{100}{\volt}.
-The short-term trace was taken on a PicoScope~5442B (AC-coupled, \SI{100}{\volt} output).
-For clarity, the trace has been down-sampled and the points colored based on their probability of occurrence.
-Thus, the color gives a visual estimation of the RMS width.
-% are colored based on their normally distributed statistical probability, and thus give a visual estimation of the RMS width.
+A cross-correlation between the measured temperature and output voltage yields an effective temperature coefficient of \SI[per-mode=symbol]{-24}{ppm\per\celsius} at \SI{100}{\volt}.\footnote{This value was extracted from a separate long-term voltage measurement, during which the temperature of the room fluctuated by $\approx \SI{3}{\celsius}$.}
+The short-term trace was taken on a PicoScope~5442B (AC-coupled, \SI{100}{\volt} output), and downsampled for clarity.
+Points are binned into 100-\si{\micro\second} slices, and colored based on their normally-distributed probability of occurrence.
+The color scale is normalized to the most probable voltage in each bin.
 
@@
 
+\begin{acknowledgments}
 The authors would like to thank Z. Smith for useful discussions.
 This work was partially supported by the Office of Naval Research, and the National Science Foundation through the Physics Frontier Center at the Joint Quantum Institute.
+\end{acknowledgments}
 
-%
-%\section{Other...}
-%\begin{itemize}
-%\item $1/f \rightarrow$ white noise corner frequency
-%\item white noise spectral density
-%\item RMS noise (0.1 - 10 Hz; 10 Hz - 10 kHz, or something similar) -- use SRS voltage preamp?
-%\item How effective is the LM7171 at reducing switching noise? look at FFT power before final filter resistor, and at output of op amp (dBc spec)
-%\item compare noise to predicted values
-%\item longterm trace on kiethly -- across voltage divider at output? Monitor vs temperature? -- need to find low Tc resistors, at least.
-%\item see what dependence is on power source -- eg, JQI power supply vs lab supply vs very quiet voltage regulator?
-%\item current draw -- display in some ``bottom line'' specs table?
-%\item bandwidth measurements -- full scale triangle ramp, small signal bandwidth -- discuss limitations on this (eg, also versus different piezo loads)
-%\item Lock a laser, show RMS noise fluct vs. old piezo?
-%\item compare to SC100 toptica controller? even if just internally.
-%\end{itemize}
-
-% If in two-column mode, this environment will change to single-column format so that long equations can be displayed.
-% Use only when necessary.
-%\begin{widetext}
-%$$\mbox{put long equation here}$$
-%\end{widetext}
-
-% Figures should be put into the text as floats.
-% Use the graphics or graphicx packages (distributed with LaTeX2e). EPSFig is no longer fully supported.
-% See the LaTeX Graphics Companion by Michel Goosens, Sebastian Rahtz, and Frank Mittelbach for examples.
-%
-% Here is an example of the general form of a figure:
-% Fill in the caption in the braces of the \caption{} command.
-% Put the label that you will use with \ref{} command in the braces of the \label{} command.
-%
-% \begin{figure}
-% \includegraphics{}% % Important NOTE: Please make certain your figures do not include local directory paths. ex. "c:\file\sub\fig1.eps"
-% \caption{\label{}}%
-% \end{figure}
-
-% Tables may be be put in the text as floats.
-% Here is an example of the general form of a table:
-% Fill in the caption in the braces of the \caption{} command. Put the label
-% that you will use with \ref{} command in the braces of the \label{} command.
-% Insert the column specifiers (l, r, c, d, etc.) in the empty braces of the
-% \begin{tabular}{} command.
-%
-% \begin{table}
-% \caption{\label{} }
-% \begin{tabular}{}
-% \end{tabular}
-% \end{table}
-
-% If you have acknowledgments, this puts in the proper section head.
-%\begin{acknowledgments}
-% Put your acknowledgments here.
-%\end{acknowledgments}
-
-% Create the reference section using BibTeX:
-%\bibliographystyle{plain}
+% Run this once to generate your BBL file. Then copy the contents of your BBL file into your main latex file, commenting out "\bibliography"
 \bibliography{references}
-% Run this once to generate your BBL file. Then copy the contents of your BBL file into your main latex file, commenting out "\bibliography"
 
 \end{document}
-%
-% ****** End of file aiptemplate.tex ******

### 2016-09-12 piezo.tex
Streamline build process
* updated makefile
* changed \includegraphics to be more agnostic
* removed a few commented lines
WERB comments; submission version

@@
 \DeclareGraphicsRule{.ai}{pdf}{.ai}{}
+\DeclareGraphicsExtensions{.png,.tiff,.ai,.eps}
+\graphicspath{{fig/}}
 
@@
 While this has certain advantages, many applications would benefit from an architecture that provides a unity-gain, DC-coupled feedback path to the high-voltage output. 
-Such a device could make closed-loop systems less susceptible to noise contributions from the servo controller, which we often find in our laboratory to be the limiting factor in laser lock stability.
+This low-gain modulation input could make closed-loop systems less susceptible to noise contributions from the servo controller, which we often find in our laboratory to be a limiting factor in laser lock stability.
 
@@
 We present a circuit with a hybrid architecture.
-The high voltage is generated by a galvanically isolated DC-DC converter, while a low-noise, high-slew-rate op-amp simulatneously removes noise at the output and provides a low-gain, high-bandwidth modulation input for closed-loop feedback applications.
+The high voltage is generated by a galvanically isolated DC-DC converter, while a low-noise, high-slew-rate op-amp simulatneously removes noise at the output and provides a low-gain, high-bandwidth ($\gtrsim \SI{100}{\kilo\hertz}$) modulation input for closed-loop feedback applications.
 This architecture is able to achieve extremely low noise ($\approx\SI{100}{\micro\volt}_{\text{RMS}}$) over the entire output range, draws very little current, and fits comfortably onto a small-footprint PCB.
@@
 \begin{figure*}[t]
-\includegraphics[width=\textwidth]{fig/Schematic.ai}
+\includegraphics[width=\textwidth]{Schematic}
 \caption{Schematic of the high voltage supply and stabilization.
@@
 A MOSFET quench circuit, shown in Fig.~\ref{Fig:MOS}, connects at nodes $\text{V}_\text{out}$ and $\text{V}_\text{MG}$.
-%Op-amps U1 and U2 are powered at $\pm\SI{15}{\volt}$ (not shown).
 \label{Fig:PiezoCircuit}}
@@
 
-%Rework this paragraph re: dan's comment; stabilization vs 
-%
-%The electronics that control the galvanically isolated output of the DRV2700 works in two ways: keep Cout constant, U2 drives Vmg in order to supress the noise; 
-%
-%emphasize: sensing Vout relative to the true ground, and servoing Vmg to stabilize (remove noise, DC value...) -- explain high level first, then drill down into specifics?
-%
-%Note that the modulation gain is negative, so the voltage Vmod is inverted before being summed onto the output.
-
 The low-noise stabilization circuit is crucial to the performance of the design, as it is responsible for removing noise at the output of the flyback converter.
@@
 In this regime, $\text{C}_\text{out}$ provides a low-impedance path between U2 and the output, such that high-frequency switching noise can be directly compensated for by the op-amp.
-We settled on a value $\text{C}_\text{out}=\SI{1}{\micro\farad}$, which is a compromise between component size and the desire for a large capacitance.
+We chose a value $\text{C}_\text{out}=\SI{1}{\micro\farad}$, which is a compromise between component size and the desire for a large capacitance.
 In addition, a small resistance $R_{11} = \SI{50}{\ohm}$ is inserted between U2 and $\text{C}_\text{out}$ to ensure stable operation.
@@
 \begin{figure}[t!]
-\includegraphics[width=\columnwidth]{fig/MOS.ai}
+\includegraphics[width=\columnwidth]{MOS}
 \caption{MOSFET ``quench'' circuit.
@@
 
-\section{Noise Analysis}
+\section{Noise model \& analysis}
 \label{Sec:NoiseAnalysis}
@@
 \begin{figure}[t]
-\includegraphics[width=\columnwidth]{fig/NoiseModel.ai}
+\includegraphics[width=\columnwidth]{NoiseModel}
 \caption{Noise model, including contributions from the op-amp, DAC, DRV2700, and modulation input.
@@
 \subfloat{
-\includegraphics[width=\columnwidth]{fig/NoiseContrib.png}
+\includegraphics[width=\columnwidth]{NoiseContrib}
 }
@@
 }
-\caption{Noise Contributions (color online).
+\caption{Noise contributions (color online).
 Plotted are the noise contributions from each source in our model, along with the total calculated noise.
@@
 \begin{figure}[t]
-\includegraphics[width=\columnwidth]{fig/VoltagePSD.png}
+\includegraphics[width=\columnwidth]{VoltagePSD}
 \caption{Voltage noise power spectral density at various output voltages (color online).
@@
 \begin{figure}[b]
-\includegraphics[width=\columnwidth]{fig/TimeDomain.png}
+\includegraphics[width=\columnwidth]{TimeDomain}
 \caption{Time-domain traces of the high-voltage output (\SI{100}{\volt}, color online). (a) Short-time scatterplot  (AC coupled). 
@@
 \begin{figure}[t]
-\includegraphics[width=\columnwidth]{fig/PiezoModulationTransfer.png}
+\includegraphics[width=\columnwidth]{PiezoModulationTransfer}
 \caption{Modulation input transfer function (color online).
@@
 \begin{acknowledgments}
-The authors would like to thank Z. Smith for useful discussions.
+The authors would like to thank Z. Smith and D. Genkina for useful discussions.
 This work was partially supported by the Office of Naval Research, and the National Science Foundation through the Physics Frontier Center at the Joint Quantum Institute.
@@
 
-% Run this once to generate your BBL file. Then copy the contents of your BBL file into your main latex file, commenting out "\bibliography"
 \bibliography{references}

### 2016-11-06 piezo.tex
Edits responding to referees

@@
 Commercially available piezoelectric drivers typically provide a modulation input for such closed-loop applications, but the input voltage is often gained such that it spans the entire output range of the device.
-While this has certain advantages, many applications would benefit from an architecture that provides a unity-gain, DC-coupled feedback path to the high-voltage output. 
+Other designs separate high- and low-voltage control pathways, which can extend the bandwidth to $\approx\si{\mega\hertz}$, but the low-voltage control is AC-coupled to the output.\cite{Fleming2009a}
+While these designs have advantages, many applications would benefit from an architecture that provides a unity-gain, DC-coupled feedback path to the high-voltage output.
 This low-gain modulation input could make closed-loop systems less susceptible to noise contributions from the servo controller, which we often find in our laboratory to be a limiting factor in laser lock stability.
@@
 Linear-type devices are typically constructed from a high-voltage operational amplifier (op-amp), powered either from a high-voltage linear regulator or more typically from a secondary switching converter.
-While the op-amp can provide \SI{100}{\decibel} or more of power-supply noise rejection\cite{PA84Datasheet}, high-voltage op-amps require substantially more power than an equivalent switching circuit and are more cumbersome to deploy in the laboratory.
+While the op-amp can provide \SI{100}{\decibel} or more of power-supply noise rejection\cite{PA84Datasheet}, linear regulators must dissipate excess voltages as heat and so may be more cumbersome to deploy in the laboratory.
 
@@
 The entire electronics package fits into a compact Eurocard rack module (with the high-voltage section taking only a fraction of the PCB), and draws less than \SI{150}{\milli\ampere} at \SI{15}{\volt}.
+The output current will be limited by the switching regulator and by the LM7171 op-amp used for low-noise stabilization (U2 in Fig.~\ref{Fig:PiezoCircuit}, which can supply at most $\approx\SI{100}{\milli\ampere}$\cite{LM7171Datasheet}), but is sufficient for nearly all piezoelectric applications.
 
@@
 This filter topology, modeled on a lossy transmission line, is sufficient for our application, but other corner frequencies or topologies could also be used.
+
+%% place figure here for better text flow
+\begin{figure}[t!]
+\includegraphics[width=\columnwidth]{MOS}
+\caption{MOSFET ``quench'' circuit.
+When the mid-ground node $\text{V}_\text{MG}$ (also shown in Fig.~\ref{Fig:PiezoCircuit}) goes below the threshold value set at $\text{V}_\text{TH}$, the op-amp puts the HV MOSFET Q1 into conduction.
+When engaged, the quench time constant is given by $\tau \approx R_\text{MOS} \text{C}_\text{out}$, which for our circuit is set to \SI{1}{\milli\second}.
+Capacitor $\text{C}_\text{out}=\SI{1}{\micro\farad}$ is shown in Fig.~\ref{Fig:PiezoCircuit}, and details of this circuit are discussed in Sec.~\ref{Sec:SlowModulationMOS}.
+\label{Fig:MOS}}
+\end{figure}
 
@@
 
-\begin{figure}[t!]
-\includegraphics[width=\columnwidth]{MOS}
-\caption{MOSFET ``quench'' circuit.
-When the mid-ground node $\text{V}_\text{MG}$ (also shown in Fig.~\ref{Fig:PiezoCircuit}) goes below the threshold value set at $\text{V}_\text{TH}$, the op-amp puts the HV MOSFET Q1 into conduction.
-When engaged, the quench time constant is given by $\tau \approx R_\text{MOS} \text{C}_\text{out}$, which for our circuit is set to \SI{1}{\milli\second}.
-Capacitor $\text{C}_\text{out}=\SI{1}{\micro\farad}$ is shown in Fig.~\ref{Fig:PiezoCircuit}.
-\label{Fig:MOS}}
-\end{figure}
-
 The high-voltage setpoint (absent voltages summed in at $\text{V}_\text{mod}$) is controlled by a low-noise DAC.
@@
 One downside of the flyback regulator presented above is that while the switched transformer can quickly charge the output capacitors, the discharge time $\tau$ is limited to {$\approx~\SI{1}{\second}$} by the RC time constant of the circuit.
-To get around this limitation, we have added an auxiliary MOSFET ``quench'' circuit, as suggested in the DRV2700 datasheet\cite{DRV2700Datasheet}, to quickly shunt $\text{V}_\text{out}$ to ground (see Fig.~\ref{Fig:MOS}).
+To get around this limitation, we have added an auxiliary MOSFET ``quench'' circuit\footnote{The quench circuit presented here is based on the pulldown FET discussed in the DRV2700 datasheet, with some additional modifications to suit our purposes.} to quickly shunt $\text{V}_\text{out}$ to ground (see Fig.~\ref{Fig:MOS}).
 This circuit works by monitoring the voltage at $\text{V}_\text{MG}$, the mid-ground node controlled by op-amp U2.
@@
 
-\subsection{Auxiliary design features}
-\label{Sec:AuxDesign}
-
-Here, we discuss some additional features of our circuit that are independent of the high-voltage design but are advantageous for many applications.
-The onboard microcontroller responsible for setting the DAC control voltage, $\text{V}_\text{ctl}$, also interfaces with frontpanel controls including a switch, LCD, and rotary encoder with an integrated pushbutton.
-The encoder/pushbutton provide menu navigation, and the switch toggles between DC and scanning operation.
-However, other user interfaces can easily be designed to work with the existing hardware.
-Arduino-based code\cite{Arduino} written in \CC defines the entire software interaction, and can be modified depending on the needs of the researcher.
-
-The circuit fits into a standard Eurocard module\footnote{Module size is 3U by 12HP by \SI{160}{\milli\meter}, see IEEE~Std~1101.11 for details.}, and is mounted in a Eurocard rack which supplies power at $\pm\SI{15}{\volt}$.
-While not required, the rack provides a backplane with analog lines to communicate with other modules (e.g., to implement a current feed-forward for laser diodes as described below).
-We are presently designing a backplane with a secondary microcontroller that can be addressed over TCP/IP.
-This vastly expands the conceivable control scenarios. 
-For example, in our lab we implement a slow-feedback lock of external-cavity diode lasers to a wavemeter.
-Software on the computer attached to the wavemeter computes an error signal and corrective control voltage, which will be passed over our internal network to the piezo driver to correct for frequency drifts in the laser.
-Other similar schemes are possible, enabling complete remote control of the laser electronics.
-
-The modulation voltage $\text{V}_\text{mod}$ can be supplied either from a BNC on the frontpanel or from the backplane.
-This may be useful, e.g., with servo controllers that reside in the same rack as the other control electronics.
-In either case, this voltage is differentially buffered to break ground loops.
-An output voltage monitor (sensed at the inverting node of U2 in Fig.~\ref{Fig:PiezoCircuit}, but not shown) is buffered and connected to a BNC on the frontpanel, an analog signal line on the backplane, and to the microcontroller.\footnote{One drawback of this scheme is that the contribution of $\text{V}_\text{mod}$ is not sensed by the monitor.
-Future versions will instead monitor $\text{V}_\text{out}$ through a resistive divider, allowing the microcontroller to implement an infinite integrator and drive $\text{V}_\text{mod}$ to \SI{0}{\volt} in closed-loop operation.
-This will be a very useful feature to prevent the servo controller from railing.}
-The backplane monitor could be fed to a low-noise current controller (e.g., one based on the design in Erickson, et. al.~\cite{Erickson2008a}) to implement a laser diode current feed-forward.
-The high-voltage output can be interlocked with another signal on the backplane, permitting easy integration with existing laboratory interlock schemes if desired.
-Further details on the design features discussed in this section, including sample software, can be found on GitHub.\cite{PiezoDesignFiles}
+The high-voltage design presented here has the flexibility to exist as a standalone circuit or be integrated with other electronics, and we have included several auxiliary features to make this more convenient.
+For example, the analog modulation input is differentially buffered to break ground loops, and the digital portion can be interfaced with other devices in the lab to expand conceivable control scenarios.
+Secondary features include a divided-down output that can be used as a monitor or fed forward to a low-noise laser diode current controller like the one in Erickson, et. al.~\cite{Erickson2008a}
+Of course many variations are possible, and we refer the reader to GitHub for more details on our specific implementation.\cite{PiezoDesignFiles}
 
@@
 
-\begin{figure}[t]
-\includegraphics[width=\columnwidth]{NoiseModel}
-\caption{Noise model, including contributions from the op-amp, DAC, DRV2700, and modulation input.
-The element labeled $\text{C}_\text{LP}$ consists of a \SI{47}{\nano\farad} capacitor in parallel with a \SI{10}{\micro\farad} capacitor connected to ground through a switch, such that the corner frequency of the filter can be changed depending on the mode of operation  (see text).
-Though not drawn in the figure, we also consider the Johnson noise contributions from all resistors.
-\label{Fig:NoiseModel}}
-\end{figure}
-
-We analyze the noise performance of the circuit according to the model shown in Fig.~\ref{Fig:NoiseModel}, where noise spectral densities are calculated at the node $\text{V}_\text{out}$.
-A summary of each noise contribution (op-amp, DAC, Johnson-Nyquist, and residual ripple from the DRV2700) is shown in Fig.~\ref{Fig:NoisePlot}, along with the cumulative root-mean-square (RMS) noise estimates in different frequency bands.
+To better understand the circuit performance and the measured output noise reported in Sec.~\ref{Sec:Results}, we introduce the noise model shown in Fig.~\ref{Fig:NoiseModel}. 
+A summary of each noise contribution (op-amp, DAC, Johnson-Nyquist, and residual ripple from the DRV2700, all calculated at the node $\text{V}_\text{out}$) is shown in Fig.~\ref{Fig:NoisePlot}, along with the cumulative root-mean-square (RMS) noise estimates in different frequency bands.
 We will neglect noise appearing at node $\text{V}_\text{mod}$ due to the external modulation because its exact character depends on the external drive.
@@
 where the bracketed term is $Z_+$, $f$ is the Fourier frequency, and $\iu$ is the imaginary unit.
+
+\begin{figure}[t]
+\includegraphics[width=\columnwidth]{NoiseModel}
+\caption{Noise model, including contributions from the op-amp, DAC, DRV2700, and modulation input.
+The element labeled $\text{C}_\text{LP}$ consists of a \SI{47}{\nano\farad} capacitor in parallel with a \SI{10}{\micro\farad} capacitor connected to ground through a switch, such that the corner frequency of the filter can be changed depending on the mode of operation  (see text).
+Though not drawn in the figure, we also consider the Johnson noise contributions from all resistors.
+\label{Fig:NoiseModel}}
+\end{figure}
+
+We now calculate gains from the inverting node of U2.
+Because any currents appearing at this node will be cancelled by the feedback of U2, the transimpedance gain $G_{-}^{(i)}$ is simply the impedance $Z_1$, given by
+\begin{align}
+G_{-}^{(i)} = Z_1 \equiv \frac{R_1}{1+2\pi \iu f R_1 C_1}\,.
+\end{align}
+With these expressions in hand, we can calculate the output noise contribution from each source in our model.
+
+As shown in Fig.~\ref{Fig:NoiseModel}, the op-amp noise is parametrized by two noise contributions: $e_n$, the input voltage noise spectral density, and $i_n$, the input current noise spectral density.
+For the LM7171 at $\SI{10}{\kilo\hertz}$, $e_n = \SI[per-mode=symbol]{14}{\nano\volt\per\sqrthz}$ and $i_n = \SI[per-mode=symbol]{1.5}{\pico\ampere\per\sqrthz}$ with a $1/f$ noise character below this frequency.\cite{LM7171Datasheet}
+The voltage noise appears at the non-inverting input, while the current noise is present at both inputs.
+By multiplying each source by the appropriate gain, we obtain the equivalent output-noise power spectral densities (PSD),
+\begin{align}
+\begin{split}
+e^2_{v,\text{U2}} &= \big|G_{+}^{(v)}\big|^2 e^2_n \\
+e^2_{i,\text{U2}} &= \big|G_{-}^{(i)}\big|^2 i^2_n + \big|G_{+}^{(i)}\big|^2 i^2_n\,,
+\end{split}
+\end{align}
+where  $e^2_{v,\text{U2}}$, $e^2_{i,\text{U2}}$ are the output-referred voltage and current noise PSD, respectively (plotted in Fig.~\ref{Fig:NoisePlot}).
 
@@
 }
-\caption{Noise contributions (color online).
+\caption{Modeled noise contributions (color online).
 Plotted are the noise contributions from each source in our model, along with the total calculated noise.
@@
 Frequency-dependent noise spectra for the DAC and op-amp were extracted from the datasheets.\label{Fig:NoisePlot}}
-\end{figure}
-
-We now calculate gains from the inverting node of U2.
-Because any currents appearing at this node will be cancelled by the feedback of U2, the transimpedance gain $G_{-}^{(i)}$ is simply the impedance $Z_1$, given by
-\begin{align}
-G_{-}^{(i)} = Z_1 \equiv \frac{R_1}{1+2\pi \iu f R_1 C_1}\,.
-\end{align}
-%The voltage gain from this node is similarly given by
-%\begin{align}
-%G_{-}^{(v)} = -Z_1 \left(\frac{1}{R_2} + \frac{1}{Z_\text{mod}}\right)\,.
-%\end{align}
-With these expressions in hand, we can calculate the output noise contribution from each source in our model.
-
-As shown in Fig.~\ref{Fig:NoiseModel}, the op-amp noise is parametrized by two noise contributions: $e_n$, the input voltage noise spectral density, and $i_n$, the input current noise spectral density.
-For the LM7171 at $\SI{10}{\kilo\hertz}$, $e_n = \SI[per-mode=symbol]{14}{\nano\volt\per\sqrthz}$ and $i_n = \SI[per-mode=symbol]{1.5}{\pico\ampere\per\sqrthz}$ with a $1/f$ noise character below this frequency.\cite{LM7171Datasheet}
-The voltage noise appears at the non-inverting input, while the current noise is present at both inputs.
-By multiplying each source by the appropriate gain, we obtain the equivalent output-noise power spectral densities (PSD),
-\begin{align}
-\begin{split}
-e^2_{v,\text{U2}} &= \big|G_{+}^{(v)}\big|^2 e^2_n \\
-e^2_{i,\text{U2}} &= \big|G_{-}^{(i)}\big|^2 i^2_n + \big|G_{+}^{(i)}\big|^2 i^2_n\,,
-\end{split}
-\end{align}
-where  $e^2_{v,\text{U2}}$, $e^2_{i,\text{U2}}$ are the output-referred voltage and current noise PSD, respectively (plotted in Fig.~\ref{Fig:NoisePlot}).
-
-\begin{figure}[t]
-\includegraphics[width=\columnwidth]{VoltagePSD}
-\caption{Voltage noise power spectral density at various output voltages (color online).
-The integrated RMS noise ($\SI{1}{\hertz} - \SI{100}{\kilo\hertz}$) is $\{138, 80, 101\}~\si{\micro\volt}$ measured at  $\{50, 100, 200\}~\si{\volt}$, with no output load.
-The dashed black line indicates the total noise estimate from our model, calculated at \SI{100}{\volt} (see Fig.~\ref{Fig:NoisePlot}).\label{Fig:PSD}}
 \end{figure}
@@
 Thus, we use a switchable low-pass filter (as described in Sec.~\ref{Sec:SlowModulationMOS}) to achieve low-noise performance during DC operation, while still permitting the DAC to modulate $\text{V}_\text{ctl}$ more quickly when needed.
-%In our circuit, the high-corner filter is comprised of a \SI{20.5}{\kilo\ohm} resistor and \SI{47}{\nano\farad} capacitor, with $f_c \approx \SI{165}{\hertz}$.
-%In DC mode, a secondary \SI{10}{\micro\farad} capacitor in parallel with the \SI{47}{\nano\farad} capacitor mentioned above can be connected to ground through a low resistance digital switch.
-%This changes the corner frequency to \SI{0.8}{\hertz}.
 The non-zero resistance of the switch contributes a zero to the transfer function at $\approx\SI{23}{\kilo\hertz}$, but has negligible effect on the performance.
@@
 In subsequent calculations, we take the DC-mode operation ($f_c = \SI{0.8}{\hertz}$) for the switchable low-pass filter.
-
-\begin{figure}[b]
-\includegraphics[width=\columnwidth]{TimeDomain}
-\caption{Time-domain traces of the high-voltage output (\SI{100}{\volt}, color online). (a) Short-time scatterplot  (AC coupled). 
-%Points are colored based on the Gaussian spread in acquired voltages, thus indicating the RMS width of the trace.
-%The points have been down-sampled and colored based on their probability of occurence, thus providing a visual estimation of the RMS width.
-The points have been down-sampled for clarity, and colored based on a normally-distributed probability of occurence in each 100-\si{\micro\second} timeslice (scaled to the most probable voltage).
-The color thus provides a visual estimation of the RMS width.
-%At each time bin, the points have been colored based on a normally-distributed probability of occurrence, scaled to the most probable voltage for that bin.
-%The points have been binned down-sampled and colored based on their probability of occurence, normalized to the most probable voltage in each time bin, thus providing a visual estimation of the RMS width.
-(b) Long-term trace, measured on a Keithly~2010 digital multimeter.
-A~\SI{100}{\volt} DC offset is subtracted from the plotted values.
-The top panel shows the lab temperature during the same time period.\label{Fig:TimeDomain}}
-\end{figure}
 
@@
 
+\begin{figure}[b]
+\includegraphics[width=\columnwidth]{VoltagePSD}
+\caption{Voltage noise power spectral density at various output voltages, as measured on an SR780 spectrum analyzer (color online).
+The integrated RMS noise ($\SI{1}{\hertz} - \SI{100}{\kilo\hertz}$) is $\{138, 80, 101\}~\si{\micro\volt}$ measured at  $\{50, 100, 200\}~\si{\volt}$, with no output load.
+The dashed black line overlays the noise estimate from our model, calculated at \SI{100}{\volt} (see Fig.~\ref{Fig:NoisePlot}).\label{Fig:PSD}}
+\end{figure}
+
 Given the noise model discussed above, our circuit is dominated by the op-amp's intrinsic current noise at lower frequencies, and voltage noise at higher frequencies.
@@
 
-\begin{figure}[t]
-\includegraphics[width=\columnwidth]{PiezoModulationTransfer}
-\caption{Modulation input transfer function (color online).
-The solid blue line indicates the unloaded frequency response, while the dash-dotted orange trace shows the response with a \SI{700}{\nano\farad} piezoelectric actuator~{(Thorlabs PN~AE0505D08F)}.
-Mechanical resonances above $\approx\SI{50}{\kilo\hertz}$ are clearly visible.
-The dashed green trace shows the response under a \SI{1}{\micro\farad} purely capacitive load.
-Loaded response bandwidth is $\approx~\SI{100}{\kilo\hertz}$, while the unloaded bandwidth is $\approx~\SI{1}{\mega\hertz}$.\label{Fig:TransferFunc}}
+\begin{figure}[b]
+\includegraphics[width=\columnwidth]{TimeDomain}
+\caption{Time-domain traces of the high-voltage output (\SI{100}{\volt}, color online). (a) Short-time scatterplot (AC coupled).
+The points have been down-sampled for clarity, and colored based on a normally-distributed probability of occurence in each 100-\si{\micro\second} timeslice (scaled to the most probable voltage).
+The color thus provides a visual estimation of the RMS width.
+(b) Long-term trace, measured on a Keithly~2010 digital multimeter.
+A~\SI{100}{\volt} DC offset is subtracted from the plotted values.
+The top panel shows the lab temperature during the same time period.\label{Fig:TimeDomain}}
 \end{figure}
@@
 Indeed, one can see the characteristic shape change in Fig.~\ref{Fig:PSD} between \SI{100}{\volt} and \SI{50}{\volt} as the residual ripple $e_{n,\text{DRV}}$ begins to dominate at low frequencies.
+
+\begin{figure}[t]
+\includegraphics[width=\columnwidth]{PiezoModulationTransfer}
+\caption{Modulation input transfer function (color online).
+The solid blue line indicates the unloaded frequency response, with the phase plotted in the lower panel.
+The dash-dotted orange trace shows the response with a \SI{700}{\nano\farad} piezoelectric actuator~{(Thorlabs PN~AE0505D08F)}.
+Several mechanical resonances above $\approx\SI{50}{\kilo\hertz}$ are clearly visible.
+The dashed green trace shows the response under a \SI{1}{\micro\farad} capacitive load.
+Loaded response bandwidth is $\approx~\SI{100}{\kilo\hertz}$, while the unloaded bandwidth is $\approx~\SI{5}{\mega\hertz}$ as indicated by the black dashed lines marking the $\SI{45}{\degree}$ phase margin.\label{Fig:TransferFunc}}
+\end{figure}
 

### 2016-11-06 referee_response.tex
referee response letter

\documentclass[12pt, oneside]{letter}   	% use "amsart" instead of "article" for AMSLaTeX format
\usepackage{geometry}                		% See geometry.pdf to learn the layout options. There are lots.
\geometry{letterpaper}                   		% ... or a4paper or a5paper or ... 
%\geometry{landscape}                		% Activate for for rotated page geometry
%\usepackage[parfill]{parskip}    		% Activate to begin paragraphs with an empty line rather than an indent
\usepackage{graphicx}				% Use pdf, png, jpg, or eps with pdflatex; use eps in DVI mode
								% TeX will automatically convert eps --> pdf in pdflatex		
\usepackage{amssymb}
\usepackage{amsmath}

\usepackage{siunitx}
\DeclareSIUnit{\sqrthz}{\ensuremath{\sqrt{\text{\hertz}}}}

\begin{document}

Dear Editors:

We thank the referees for their review of our paper, and are pleased they found it suitable for publication.
We are also thankful for their thoughtful comments, which have allowed us to improve our manuscript considerably.
Please see below for a detailed summary of our changes and answers to the referees' comments and questions.
Italics indicate quotes from the referees.

\textbf{1.}
\textit{There is only one missing piece in the analysis of this circuit-the phase of the transfer function. 
When designing feedback circuits the shape of the transfer function is of great importance, but so is the relative phase of the feedback. 
This is especially true in circuits involving digital components. 
In this manuscript I do not see any mention or analysis of the phase of transfer function. 
To complete this study a mention of the behavior of the circuit of the demonstration of the unloaded is needed.}

We completely agree, and it was an oversight to neglect this.
We have updated Fig.~7 to include the unloaded phase response.
We have also updated the figure caption to reflect this change.

\textbf{2.}
\textit{The section on Auxiliary design features [should be] made more concise by addressing the flexibility of the circuit design without going into the exact details implemented by the author. }

We agree that this section does not add to the novel design presented in the manuscript, and is better suited as supplemental material.
We have removed section II.D. (``Auxiliary design features'') and moved a few details we believe will be interesting to the reader from that section to a new paragraph at the end of section II.C. (``Digital control and slow modulation''), which reads ``The high-voltage design presented here has the flexibility to exist as a standalone circuit or be integrated with other electronics~\ldots~Of course many variations are possible, and we refer the reader to GitHub for more details on our specific implementation.''

\textbf{3.}
\textit{[I]t would be good to address how much current your circuit can provide, and compare that to typical currents needed for the different applications suggested in the introduction.}

We agree this would be useful, and have included an estimate of the current at the end of the first paragraph in Sec~II.
That sentence reads, ``The output current will be limited by the switching regulator and by the LM7171 op-amp used for low-noise stabilization (U2 in Fig.~1, which can supply at most $\approx\SI{100}{\milli\ampere}$), but is sufficient for nearly all piezoelectric applications.''

\textbf{4.}
\textit{You state that a high-voltage op-amp in a linear supply requires significant power.
That statement might raise some eyebrows, because often in a regulated supply the transistor that burns off excess voltage is physically separate from the op-amp, such that it's not the op-amp itself that's sinking the power. 
You might try rewording this just to avoid that critique.}

We have reworded this sentence (last sentence in paragraph 3 of the introduction): ``While the op-amp can provide \SI{100}{\decibel} or more of power-supply noise rejection, linear regulators must dissipate excess voltages as heat and so may be more cumbersome to deploy in the laboratory.''

\textbf{5.}
\textit{Maybe I missed this - but was the data in figure 6 used to make figure 5? If so, that should be stated.}

Fig. 5 was generated from an SR780 spectrum analyzer, while Fig. 6 was generated from a fast sampling ADC (PicoScope).
We have modified the first sentence of the Fig. 5 caption to make this more explicit.
It now reads ``Voltage noise power spectral density at various output voltages, as measured on an SR780 spectrum analyzer (color online).''

\textbf{6.}
\textit{The term "quench" circuit is a good description. But it is not called by that name in the datasheet, which made me a little confused when I looked for it in there. Also, you might want to state that this circuit performs the same function as a similar circuit suggested by the datasheet, but that this circuit was modified to fit your design (in other words, this is not exactly the same circuit suggested in the datasheet).}

We have modified the second sentence in the second-to-last paragraph of Sec.~II.C. (``Digital control and slow modulation'') to make this clearer.
Specifically, we have moved reference to the datasheet ``FET'' circuit to a footnote.
It now reads: ``\ldots To get around this limitation, we have added an auxiliary MOSFET ``quench'' circuit [FOOTNOTE: the quench circuit presented here is based on the pulldown FET discussed in the DRV2700 datasheet, with some additional modifications to suit our purposes.] to quickly shunt $\text{V}_\text{out}$ to ground (see Fig.~2).

\textbf{7.}
\textit{The noise model was very nice - and the agreement with measurement is surprisingly good! It is, however, something that most people implementing your design will only glance at. Mainly, we want to know what the noise is, and that it made sense to you, so that we know that there's not something you overlooked that could easily be changed to improve the circuit. As such, it might be nice to place this after you discuss measured results. Also, you compare the measured results to your model in this section, and it was a bit confusing because you hadn't talked about your measurements yet.}

\textit{Overall, the paper was a bit dense. You might want to go over it and consider what would make the paper more useful for people that want to implement your design. Most of them will want a basic understanding, but will probably trust your work and not want to take the time to reproduce calculations, etc. Try to explain things more concisely. When you describe how a part of the circuit works, you might want to have a paragraph explaining what a particular section does before giving details. I like that the paper is detailed, and it should be. But you might be able to help the reader with a little more refinement and organization.}

While we understand referee \#2's concern, this would require completely rewriting the paper to maintain a coherent flow. We think some of the confusion might arise from how the figures are placed in the draft (eg, results figures appearing side-by-side with the noise analysis figures). We have taken some care to re-format the figures so this is no longer true, which hopefully improves readability. We do try to motivate each section of the circuit heuristically before providing specific design details (eg, the caption to Fig.~1, last paragraph before Sec.~II.A, and the first sentences of each lettered subsection of Sec.~II.).

In an attempt to address this concern, however, we have made the following changes:

\begin{itemize}
\item End of the caption in Fig.~2 now includes, ``\ldots and details of this circuit are discussed in Sec.~II.C.'', and the figure itself is placed on an earlier page (closer to the full schematic). This leaves more room for the subsequent figures to be placed closer to where they are discussed.
\item Changed first sentence of the caption to Fig.~4 to read ``Modeled noise contributions (color online).'' to make this figure more distinct from figure from Fig.~5, which contains measured results.
\item Results figures (\#5-7) are placed more closely to the results section.
\item We modified the first two sentences of Sec.~III in an attempt to better motivate the subsequent discussion. They now read ``To better understand the circuit performance and the measured output noise reported in Sec.~IV, we introduce the noise model shown in Fig. 3. A summary of each noise contribution (op-amp, DAC, Johnson-Nyquist, and residual ripple from the DRV2700, all calculated at the node $\text{V}_\text{out}$) is shown in Fig.4, along with the cumulative root-mean-square (RMS) noise estimates in different frequency bands.''
\end{itemize}

We believe the noise analysis makes it clear how one could modify the circuit for different applications, and although it may get deep in the weeds, is an important part of the paper.
For those who want to implement our circuit directly, this section can be neglected and the schematic/layout downloaded from GitHub.
For those who want to make changes or improvements, this section is an orientation to the design considerations we made.

\textbf{8.}
\textit{There was very little discussion of other, similar work. Are there other papers that you need to cite?}

We have added the additional reference \#6 (doi:10.1063/1.3234261), and incorporated an additional sentence in the second paragraph of the introduction which reads, ``Other designs separate high- and low-voltage control pathways, which can extend the bandwidth to $\approx\si{\mega\hertz}$, but the low-voltage control is AC-coupled to the output.''

\textbf{9.}
\textit{Finally, it would be really good if you had something to compare to your circuit. For example, if you used the DRV2700 in the standard Boost + Amplifier mode (which is a much simpler build than your circuit), how does its noise and modulation bandwidth compare with your circuit? How does it's conversion efficiency compare? (does it draw more than the 150 mA of your design?) etc. }

We agree this would be nice for comparison, however we are not set up to easily perform this measurement.
However, we would like to point out that using DRV2700 boost/amplifier requires the piezo to be driven differentially, which may not be suitable in some instances.

With these changes, we believe the paper has been greatly improved.
Points 1 \& 2 address the provisional publication recommendations of reviewer \#1, while the remaining points incorporate comments from reviewer \#2.
We once again thank the referees and respectfully resubmit this paper to Review of Scientific Instruments.

Sincerely,

Neal Pisenti and Gretchen Campbell

\end{document}

### 2016-11-13 piezo.tex
Referee comments

@@
 Linear-type devices are typically constructed from a high-voltage operational amplifier (op-amp), powered either from a high-voltage linear regulator or more typically from a secondary switching converter.
-While the op-amp can provide \SI{100}{\decibel} or more of power-supply noise rejection\cite{PA84Datasheet}, linear regulators must dissipate excess voltages as heat and so may be more cumbersome to deploy in the laboratory.
+While the op-amp can provide \SI{100}{\decibel} or more of power-supply noise rejection\cite{PA84Datasheet}, linear regulators must handle any excess voltage by dissipating heat and so may be more cumbersome to deploy in the laboratory.
 
 We present a circuit with a hybrid architecture.
-The high voltage is generated by a galvanically isolated DC-DC converter, while a low-noise, high-slew-rate op-amp simulatneously removes noise at the output and provides a low-gain, high-bandwidth ($\gtrsim \SI{100}{\kilo\hertz}$) modulation input for closed-loop feedback applications.
+The high voltage is generated by a galvanically isolated DC-DC converter, while a low-noise, high-slew-rate op-amp simultaneously removes noise at the output and provides a low-gain, high-bandwidth ($\gtrsim \SI{100}{\kilo\hertz}$) modulation input for closed-loop feedback applications.
 This architecture is able to achieve extremely low noise ($\approx\SI{100}{\micro\volt}_{\text{RMS}}$) over the entire output range, draws very little current, and fits comfortably onto a small-footprint PCB.
@@
 The entire electronics package fits into a compact Eurocard rack module (with the high-voltage section taking only a fraction of the PCB), and draws less than \SI{150}{\milli\ampere} at \SI{15}{\volt}.
-The output current will be limited by the switching regulator and by the LM7171 op-amp used for low-noise stabilization (U2 in Fig.~\ref{Fig:PiezoCircuit}, which can supply at most $\approx\SI{100}{\milli\ampere}$\cite{LM7171Datasheet}), but is sufficient for nearly all piezoelectric applications.
+The high-voltage output current will be limited by the switching regulator and by the LM7171 op-amp used for low-noise stabilization (U2 in Fig.~\ref{Fig:PiezoCircuit}, which can supply at most $\approx\SI{100}{\milli\ampere}$\cite{LM7171Datasheet}), but is sufficient for nearly all piezoelectric applications.
 
 Fig.~\ref{Fig:PiezoCircuit} shows an overview of the circuit schematic. 
+A flyback regulator (Sec.~\ref{Sec:DRV2700}) controls the potential between the high-voltage ($\text{V}_\text{HV}$) and floating-ground ($\text{V}_\text{FG}$) circuit nodes, while the low-noise stabilization circuitry (Sec.~\ref{Sec:LowNoiseStabilization}) controls the output node $\text{V}_\text{out}$ relative to the true circuit ground.
 A digital-to-analog converter (DAC) generates a voltage setpoint, $\text{V}_\text{ctl}$, which is sent to the high-voltage flyback regulator and to the low-noise stabilization circuit.
-The flyback regulator (Sec.~\ref{Sec:DRV2700}) controls the potential between the high-voltage ($\text{V}_\text{HV}$) and floating-ground ($\text{V}_\text{FG}$) circuit nodes, while the low-noise stabilization circuitry (Sec.~\ref{Sec:LowNoiseStabilization}) controls the output node $\text{V}_\text{out}$ relative to the true circuit ground.
 The DAC is controlled by an integrated microcontroller, and can be programmed to output slow ($\approx\SI{10}{\hertz}$) rail-to-rail voltage ramps in addition to setting the DC operating point (Sec.~\ref{Sec:SlowModulationMOS}).
@@
 
-The DRV2700 implements output voltage control by comparing the feedback input pin at node $\text{V}_\text{FB}$ with an internal \SI{1.3}{\volt} reference.
+The DRV2700 implements output voltage control by comparing the feedback input pin at node $\text{V}_\text{FB}$ with an internal (\SI{1.3}{\volt}) reference.
 The resistors $R_9$ and $R_{10}$ are chosen such that pin FB is at \SI{1.3}{\volt} when the output of U1 is at ground: $R_{10}/(R_9+R_{10}) = \SI{1.3}{\volt}/\SI{5}{\volt} \approx \num{0.26}$.
@@
 When engaged, the quench time constant is given by $\tau \approx R_\text{MOS} \text{C}_\text{out}$, which for our circuit is set to \SI{1}{\milli\second}.
-Capacitor $\text{C}_\text{out}=\SI{1}{\micro\farad}$ is shown in Fig.~\ref{Fig:PiezoCircuit}, and details of this circuit are discussed in Sec.~\ref{Sec:SlowModulationMOS}.
+The capacitor $\text{C}_\text{out}=\SI{1}{\micro\farad}$ is shown in Fig.~\ref{Fig:PiezoCircuit}, and details of this circuit are discussed in Sec.~\ref{Sec:SlowModulationMOS}.
 \label{Fig:MOS}}
@@
 
-The choice of component for resistors $R_1$ and $R_2$ is crucial for the low-noise performance of the system. 
+The choice of components for resistors $R_1$ and $R_2$ is crucial for the low-noise performance of the system.
 Because this resistive divider is responsible for accurately sensing the voltage $\text{V}_\text{out}$, noise introduced by these resistors cannot be corrected by the op-amp.
@@
 As discussed below in Sec.~\ref{Sec:NoiseAnalysis}, without modification the DAC would dominate the noise performance of $\text{V}_\text{out}$.
-Therefore, we add a single-pole low-pass filter between $\text{V}_\text{ctl}$ and the non-inverting node of U2 to bring the DAC noise contribution below other noise sources in the circuit.
+Therefore we add a single-pole, low-pass filter between $\text{V}_\text{ctl}$ and the non-inverting node of U2 to bring the DAC noise contribution below other noise sources in the circuit.
 This filter has a switchable corner frequency (between \SI{165}{\hertz} and \SI{0.8}{\hertz}) to optimize noise performance at DC while still permitting AC modulation when needed.
@@
 The high-voltage design presented here has the flexibility to exist as a standalone circuit or be integrated with other electronics, and we have included several auxiliary features to make this more convenient.
-For example, the analog modulation input is differentially buffered to break ground loops, and the digital portion can be interfaced with other devices in the lab to expand conceivable control scenarios.
+For example, the analog modulation input is differentially buffered to break ground loops (not shown in Fig.~\ref{Fig:PiezoCircuit}), and the digital portion can be interfaced with other devices in the lab to expand conceivable control scenarios.
 Secondary features include a divided-down output that can be used as a monitor or fed forward to a low-noise laser diode current controller like the one in Erickson, et. al.~\cite{Erickson2008a}
-Of course many variations are possible, and we refer the reader to GitHub for more details on our specific implementation.\cite{PiezoDesignFiles}
+Of course many variations are possible, and we refer the reader to our GitHub page for more details on our specific implementation.\cite{PiezoDesignFiles}
 
@@
 \includegraphics[width=\columnwidth]{TimeDomain}
-\caption{Time-domain traces of the high-voltage output (\SI{100}{\volt}, color online). (a) Short-time scatterplot (AC coupled).
+\caption{Time-domain traces of the high-voltage output (\SI{100}{\volt}, color online). (a) Short-time scatterplot, measured on a PicoScope~5442B (AC coupled).
 The points have been down-sampled for clarity, and colored based on a normally-distributed probability of occurence in each 100-\si{\micro\second} timeslice (scaled to the most probable voltage).
@@
 The dashed green trace shows the response under a \SI{1}{\micro\farad} capacitive load.
-Loaded response bandwidth is $\approx~\SI{100}{\kilo\hertz}$, while the unloaded bandwidth is $\approx~\SI{5}{\mega\hertz}$ as indicated by the black dashed lines marking the $\SI{45}{\degree}$ phase margin.\label{Fig:TransferFunc}}
+Loaded response bandwidth is $\approx~\SI{100}{\kilo\hertz}$, and the unloaded gain is flat within $\SI{0.1}{\decibel}$ out to $\SI{1}{\mega\hertz}$ where the phase is \SI{-20}{\degree}.\label{Fig:TransferFunc}}
 \end{figure}

### 2016-11-13 referee_response.tex
referee response letter

@@
 
+\textbf{Response to referee \#1}
+
 \textbf{1.}
@@
 
-\textbf{3.}
+\textbf{Response to referee \#2}
+
+\textbf{1.}
 \textit{[I]t would be good to address how much current your circuit can provide, and compare that to typical currents needed for the different applications suggested in the introduction.}
@@
 
-\textbf{4.}
+\textbf{2.}
 \textit{You state that a high-voltage op-amp in a linear supply requires significant power.
@@
 
-\textbf{5.}
+\textbf{3.}
 \textit{Maybe I missed this - but was the data in figure 6 used to make figure 5? If so, that should be stated.}
@@
 
-\textbf{6.}
+\textbf{4.}
 \textit{The term "quench" circuit is a good description.
@@
 We have modified the second sentence in the second-to-last paragraph of Sec.~II.C. (``Digital control and slow modulation'') to make this clearer.
-Specifically, we have moved reference to the datasheet ``FET'' circuit to a footnote.
+Specifically, we have moved the reference to the datasheet ``FET'' circuit to a footnote.
 It now reads: ``\ldots To get around this limitation, we have added an auxiliary MOSFET ``quench'' circuit [FOOTNOTE: the quench circuit presented here is based on the pulldown FET discussed in the DRV2700 datasheet, with some additional modifications to suit our purposes.] to quickly shunt $\text{V}_\text{out}$ to ground (see Fig.~2).
 
-\textbf{7.}
+\textbf{5.}
 \textit{The noise model was very nice - and the agreement with measurement is surprisingly good!
@@
 
-While we understand referee \#2's concern, this would require completely rewriting the paper to maintain a coherent flow.
+While we understand referee \#2's concern, we also feel including the details could be useful for those implementing or modifying our design.
+However, we have made some changes to address these concerns.
 We think some of the confusion might arise from how the figures are placed in the draft (eg, results figures appearing side-by-side with the noise analysis figures).
@@
 
-In an attempt to address this concern, however, we have made the following changes:
+In addition, we have made the following changes:
 
@@
 
-We believe the noise analysis makes it clear how one could modify the circuit for different applications, and although it may get deep in the weeds, is an important part of the paper.
+We believe the noise analysis makes it clear how one could modify the circuit for different applications, and although it may contain a lot of detail, is an important part of the paper.
 For those who want to implement our circuit directly, this section can be neglected and the schematic/layout downloaded from GitHub.
@@
 
-\textbf{8.}
+\textbf{6.}
 \textit{There was very little discussion of other, similar work. Are there other papers that you need to cite?}
@@
 With these changes, we believe the paper has been greatly improved.
-Points 1 \& 2 address the provisional publication recommendations of reviewer \#1, while the remaining points incorporate comments from reviewer \#2.
+The first two points address the provisional publication recommendations of reviewer \#1, while the remaining points incorporate comments from reviewer \#2.
 We once again thank the referees and respectfully resubmit this paper to Review of Scientific Instruments.

### 2016-11-13 referee_response.tex
updated some quotes from copyedit

@@
 (``Auxiliary design features'') and moved a few details we believe will be interesting to the reader from that section to a new paragraph at the end of section II.C.
-(``Digital control and slow modulation''), which reads ``The high-voltage design presented here has the flexibility to exist as a standalone circuit or be integrated with other electronics~\ldots~Of course many variations are possible, and we refer the reader to GitHub for more details on our specific implementation.''
+(``Digital control and slow modulation''), which reads ``The high-voltage design presented here has the flexibility to exist as a standalone circuit or be integrated with other electronics~\ldots~Of course many variations are possible, and we refer the reader to our GitHub page for more details on our specific implementation.''
 
@@
 We agree this would be useful, and have included an estimate of the current at the end of the first paragraph in Sec~II.
-That sentence reads, ``The output current will be limited by the switching regulator and by the LM7171 op-amp used for low-noise stabilization (U2 in Fig.~1, which can supply at most $\approx\SI{100}{\milli\ampere}$), but is sufficient for nearly all piezoelectric applications.''
+That sentence reads, ``The high-voltage output current will be limited by the switching regulator and by the LM7171 op-amp used for low-noise stabilization (U2 in Fig.~1, which can supply at most $\approx\SI{100}{\milli\ampere}$), but is sufficient for nearly all piezoelectric applications.''
 
@@
 
-We have reworded this sentence (last sentence in paragraph 3 of the introduction): ``While the op-amp can provide \SI{100}{\decibel} or more of power-supply noise rejection, linear regulators must dissipate excess voltages as heat and so may be more cumbersome to deploy in the laboratory.''
+We have reworded this sentence (last sentence in paragraph 3 of the introduction): ``While the op-amp can provide \SI{100}{\decibel} or more of power-supply noise rejection, linear regulators must handle any excess voltage by dissipating heat and so may be more cumbersome to deploy in the laboratory.''
 
@@
 It now reads ``Voltage noise power spectral density at various output voltages, as measured on an SR780 spectrum analyzer (color online).''
+We also modified the first sentence of the caption to Fig. 6(a) to read, ``Short-time scatterplot, measured on a PicoScope~5442B (AC coupled).''
 
@@
 
+\textbf{Additional copy-editing changes:}
+
+\textbf{1.} We swapped the order of the second and third sentences in the second paragraph of Sec. II.
+\\\\
+\hrule
+\newpage
+
 With these changes, we believe the paper has been greatly improved.

### 2016-12-11 piezo.tex
published version: minor copyedits

@@
 Many instrumentation applications in the modern laboratory require agile, low-noise voltage sources capable of supplying hundreds of volts or more.
-For example, piezo-actuated mirrors and diffraction gratings play an important role in atomic physics experiments (used, e.g., in Fabry-Per{\`o}t cavities\cite{Riedle1994a,Bohlouli-Zanjani2006a} and external-cavity diode lasers\cite{Wieman1991a}), while avalanche photodiodes and photomultiplier tubes require large bias voltages for proper operation.
+For example, piezo-actuated mirrors and diffraction gratings play an important role in atomic physics experiments (used, e.g., in Fabry-P\'{e}rot cavities\cite{Riedle1994a,Bohlouli-Zanjani2006a} and external-cavity diode lasers\cite{Wieman1991a}), while avalanche photodiodes and photomultiplier tubes require large bias voltages for proper operation.
 In the realm of biophysics, electrokinetic separation methods such as free-flow or capillary electrophoresis\cite{Kohlheyer2008a} require large electric field gradients, and the recent push to develop lab-on-a-chip devices could benefit from miniaturized high-voltage sources.\cite{Temiz2015a}
@@
 The high voltage is generated by a galvanically isolated DC-DC converter, while a low-noise, high-slew-rate op-amp simultaneously removes noise at the output and provides a low-gain, high-bandwidth ($\gtrsim \SI{100}{\kilo\hertz}$) modulation input for closed-loop feedback applications.
-This architecture is able to achieve extremely low noise ($\approx\SI{100}{\micro\volt}_{\text{RMS}}$) over the entire output range, draws very little current, and fits comfortably onto a small-footprint PCB.
+This architecture is able to achieve extremely low noise ($\approx\SI{100}{\micro\volt}_{\text{RMS}}$) over the entire output range, draws very little current, and fits comfortably onto a small-footprint printed circuit board (PCB).
 Additionally, the high-voltage output remains single-ended and referenced to ground, allowing it to drive piezo actuators with a grounded terminal.
@@
 Our current design uses this series in a 1206 package, but we noticed low-frequency noise correlated with varying strain on the PCB, potentially due to the relatively large footprint of this package.
-Future boards will instead use three TNPW \SI{0.1}{\percent} 0603 resistors in series for both R1 and R2 to minimize strain-induced output noise.
+Future boards might instead use three TNPW \SI{0.1}{\percent} 0603 resistors in series for both R1 and R2 to minimize strain-induced output noise.
 
